### 2024-11-02 paper/paper.tex
Start the paper.

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{amsmath}
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{csquotes}

\def \thetitle {Correcting supernova luminosity for redshift implies no accelerated expansion}
\title{\thetitle}

\date{\today}

\author{
  \href{https://orcid.org/0000-0001-6450-3262}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Logan P.~Evans}
  \\ \texttt{loganpevans@gmail.com}
}

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{\textit{arXiv} Template}

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={\thetitle},
pdfsubject={astro-ph.CO},
pdfauthor={Logan P.~Evans},
pdfkeywords={cosmological parameters, dark energy},
}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

\begin{document}
\maketitle

\begin{abstract}
  Existing analysis of Type Ia supernova relies on the assumption that
  luminosity is not affected by redshift. However, when luminosity is corrected
  for redshift, the relationship between luminosity distance and redshift for
  Type Ia supernova becomes linear. This implies that the expansion rate of the
  universe is not accelerating and there is no need for dark energy to explain
  observational data.
\end{abstract}

% keywords can be removed
\keywords{Cosmological Parameters \and Dark Energy \and Luminosity Distance}

\section{Introduction}

TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarizd in \citet{straumann2012}.

Summarize dark energy. Emphasize that dark energy is a popular explanation for
why distant supernova appear to be too far away.

Talk about the difficulty of curating supernova data, and summarize the work
done by \citet{betoule2014}.

\begin{displayquote}
\end{displayquote}

\section{Derivation of luminosity distance}

Luminosity distance, $D_L$, is the appearant distance of an object based on the
measured luminosity. This does not take into any movement of the observed
object between the time when the light was emitted and the light is observed.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the relative
brightness. Magnitude is defined on a logarithmic scale where magnitude 1 has
100 times the brightness of magnitude 6. To convert magnitude to relative brightness, we use:

\begin{equation}
  a
\end{equation}

\begin{equation}
\label{eq:g_def}
  G = \sqrt{ \bigg( s_i + \frac{s_j p_j}{p_i} \bigg)
             \bigg( s_j + \frac{s_i p_i}{p_j} \bigg)
           }
    = \frac{s_i p_i + s_j p_j}{\sqrt{p_i p_j}}.
\end{equation}

\section{Calibrated distance models}
\label{sec:disproof}

\section{Discussion of discrepancy}

\section{Conclusions}
What the heck?

\bibliographystyle{unsrtnat}
\bibliography{references}

\end{document}

### 2024-11-02 src/redshift/scratch.py

@@ -1,20 +1,16 @@
-from pprint import pprint
 import json
 import os
 import csv
 import numpy as np
 import scipy
 import pathlib
-
+from typing import ClassVar
 from matplotlib import pyplot as plt
 from dataclasses import dataclass, field
 
-DATA_DIR = (pathlib.Path(os.environ["VIRTUAL_ENV"]).parent / "data").resolve()
-
-# Using 2021J. Distance: 18.110 Mpsc. Redshift: 0.0024. Magnitude: 12.5
-SN2021J_distance = 18.110
-SN2021J_redshift = 0.0024
-SN2021J_magnitude = 12.5
+REPO_DIR = pathlib.Path(os.environ["VIRTUAL_ENV"]).parent.resolve()
+DATA_DIR = REPO_DIR / "data"
+GRAPHS_DIR = REPO_DIR / "graphs"
 
 
 @dataclass()
@@ -24,6 +20,8 @@ class Supernova:
     magnitude: float | None = field(default=None)
     stretch: float | None = field(default=None)
     color: float | None = field(default=None)
+
+    H0: ClassVar[float] = 70
 
     @staticmethod
     def from_wolfram():
@@ -51,77 +49,131 @@ class Supernova:
     def z(self):
         return self.redshift
 
+    @staticmethod
+    def _uncorrected_uncalibrated_distance(magnitude):
+        return 10 ** (magnitude / 5)
+
     @property
     def uncorrected_uncalibrated_distance(self):
-        return 100 ** (self.magnitude / 10)
+        return self._uncorrected_uncalibrated_distance(self.magnitude)
+
+    def uncorrected_calibrated_distance(self, slope, intercept):
+        return (self.uncorrected_uncalibrated_distance - intercept) * self.H0 / slope
+
+    @staticmethod
+    def _corrected_uncalibrated_distance(magnitude, z):
+        return (10 ** (magnitude / 5)) / np.sqrt(z + 1)
 
     @property
     def corrected_uncalibrated_distance(self):
-        return (100 ** (self.magnitude / 10)) / np.sqrt((self.z + 1))
+        return self._corrected_uncalibrated_distance(self.magnitude, self.z)
 
-    def distance_mpsc(self, slope, intercept):
-        return (
-            SN2021J_distance
-            * (slope * self.z + intercept)
-            / (slope * SN2021J_redshift + intercept)
-        )
+    def corrected_calibrated_distance(self, slope, intercept):
[…]

### 2024-11-03 src/redshift/supernova.py
Add some graphs

@@ -1,17 +1,21 @@
-import pathlib
-from dataclasses import dataclass
+from dataclasses import dataclass, field
 from datetime import date
+from matplotlib import pyplot as plt
+from matplotlib import pyplot as plt
+from pprint import pprint
+from typing import ClassVar
 import csv
 import jdcal
+import json
 import numpy as np
+import os
+import pathlib
+import random
 import scipy
 
-from redshift.scratch import Supernova as ScratchSupernova
-
-scratch = ScratchSupernova.from_wolfram()
-
-
-DATA_DIR = (pathlib.Path(__file__).parent.parent.parent / "data").resolve()
+REPO_DIR = pathlib.Path(os.environ["VIRTUAL_ENV"]).parent.resolve()
+DATA_DIR = REPO_DIR / "data"
+GRAPHS_DIR = REPO_DIR / "graphs"
 
 
 def parse_jd_date(jd: str):
@@ -21,35 +25,63 @@ def parse_jd_date(jd: str):
 
 @dataclass()
 class Supernova:
-    name: str
-    type: str
-    host: str | None
-    location_ra: str
-    location_decl: str
-    offset: str
-    discovery_date: date
-    max_mag_date: date
-    max_mag: float
-    last_mag_date: date
-    last_mag: float
-    z: float | None
-    z_host: float | None
-    reference: str
-    discoverers: str
-    aka: str
+    name: str | None
+    magnitude: float
+    redshift: float
+
+    H0: ClassVar[float] = 70
 
     @property
-    def is_suitable_Ia(self):
+    def z(self):
+        return self.redshift
+
+    def uncalibrated_distance(self, corrected):
+        d = 10 ** (self.magnitude / 5)
+        if corrected:
+            d /= np.sqrt(self.z + 1)
+        return d
+
+    def calibrated_distance(self, slope, intercept, corrected):
+        # XXX This is wrong.
         return (
-            self.type == "Ia"
-            and None not in [self.z, self.max_mag]
-            and (9.9 < self.max_mag < 99.9)
-            and self.discoverers != "Supernova Legacy Project"
-            and self.max_mag_date.year <= 2000
+            (self.uncalibrated_distance(corrected=corrected) - intercept)
+            * self.H0
+            / slope
         )
 
+    @property
+    def velocity_kms(self):
+        c = 299792.458 # km/s
+        return self.z * c
+
     @staticmethod
-    def from_csv():
+    def from_wolfram():
[…]

### 2024-11-04 src/redshift/supernova.py
Parse data from different file

@@ -1,4 +1,6 @@
-from dataclasses import dataclass, field
+from __future__ import annotations
+from dataclasses import dataclass, field, asdict
+from numpy.polynomial.polynomial import Polynomial
 from datetime import date
 from matplotlib import pyplot as plt
 from matplotlib import pyplot as plt
@@ -27,6 +29,7 @@ def parse_jd_date(jd: str):
 class Supernova:
     name: str | None
     magnitude: float
+    magnitude_error: float
     redshift: float
 
     H0: ClassVar[float] = 70
@@ -35,49 +38,71 @@ class Supernova:
     def z(self):
         return self.redshift
 
-    def uncalibrated_distance(self, corrected):
-        d = 10 ** (self.magnitude / 5)
+    @property
+    def corrected_magnitude(self):
+        return self.magnitude * (self.z + 1)
+
+    @staticmethod
+    def _uncalibrated_distance(corrected, magnitude, z):
+        d = 10 ** (magnitude / 5)
         if corrected:
-            d /= np.sqrt(self.z + 1)
+            d /= np.sqrt(z + 1)
         return d
 
-    def calibrated_distance(self, slope, intercept, corrected):
-        # XXX This is wrong.
-        return (
-            (self.uncalibrated_distance(corrected=corrected) - intercept)
-            * self.H0
-            / slope
+    def uncalibrated_distance(self, corrected):
+        return self._uncalibrated_distance(corrected, self.magnitude, self.z)
+
+    def calibrated_distance(self, calibration: Calibration):
+        return calibration.correction * self.uncalibrated_distance(
+            corrected=calibration.corrected
         )
 
     @property
     def velocity_kms(self):
-        c = 299792.458 # km/s
+        c = 299792.458  # km/s
         return self.z * c
 
     @staticmethod
-    def from_wolfram():
-        """https://datarepository.wolframcloud.com/resources/Type-Ia-Supernova-Data/"""
-        # https://arxiv.org/pdf/1401.4064
-
+    def from_perlmutter():
+        # https://iopscience.iop.org/article/10.1086/307221/pdf
         data = []
 
-        with open(DATA_DIR / "type-Ia-supernova-data.json", "r") as json_file:
-            raw = json.load(json_file)[1]
-            for item in raw[1:]:
-                fields = {}
[…]

### 2024-11-05 paper/paper.tex
Paper draft

@@
 Luminosity distance, $D_L$, is the appearant distance of an object based on the
-measured luminosity. This does not take into any movement of the observed
-object between the time when the light was emitted and the light is observed.
+measured luminosity. This does not take into account any movement of the
+observed object between the time when the light was emitted and the light is
+observed.
 
@@
 luminosity distance from these measurements, we start by computing the relative
-brightness. Magnitude is defined on a logarithmic scale where magnitude 1 has
-100 times the brightness of magnitude 6. To convert magnitude to relative brightness, we use:
+brightness. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has
+100 times the brightness of magnitude 6. To convert magnitude to relative
+brightness $B$, we use
 
 \begin{equation}
-  a
+  B = \frac{1}{\sqrt[5]{100}^{M - 1}}.
 \end{equation}
 
+This is proportional to the amount of energy detected by a telescope. However,
+we instead want a number that is proportional to the number of photons detected
+by the telescope. Redshifting decreases the amount of energy carried by a
+photon from $E_{\text{emit}}$ to $E_{\text{obs}}$, but we can correct for this
+phenomenon by taking
+
 \begin{equation}
-\label{eq:g_def}
-  G = \sqrt{ \bigg( s_i + \frac{s_j p_j}{p_i} \bigg)
-             \bigg( s_j + \frac{s_i p_i}{p_j} \bigg)
-           }
-    = \frac{s_i p_i + s_j p_j}{\sqrt{p_i p_j}}.
+  B^{*} = B \frac{E_{\text{emit}}}{E_{\text{obs}}}.
 \end{equation}
+
+Since the energy for a photon is given by $E = \frac{hc}{\lambda}$ where $h$ is
+the Planck constant and $c$ is the speed of light, we have
+
+\begin{equation}
+\begin{aligned}
+  B^{*} &= B \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
+        &= B \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
+\end{aligned}
+\end{equation}
+
+We use the redshift equation $(1 + z)\lambda_{\text{emit}} =
+\lambda_{\text{obs}}$ to obtain
+
+\begin{equation}
+\begin{aligned}
+  B^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
+        &= B(1 + z).
+\end{aligned}
+\end{equation}
+
+We note that since all Type Ia supernova have approximately the same intrinsic
+brightness, we can use a geometric model to compute relative distances. Imagine
+holding up two coins, one in each hand.  If you arange them so that the
+distance from your eyes to the first coin double the distance from your eyes to
+the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
+More formally, for two objects of the same radius $r$, the appearant area $A$
+is
+
+\begin{equation}
+  A = \pi \bigg(\frac{r}{d}\bigg)^2
+\end{equation}
+
+where $d$ is the relative distance between the two objects.
+
+Replacing the area with the brightness, we have
+
+\begin{equation}
+\begin{aligned}
+  B^{*} = \pi \bigg(\frac{r}{d}\bigg)^2 \\
+      d = r \sqrt{\frac{\pi}{B^*}}.
+\end{aligned}
+\end{equation}
+
+Finally, since this equation has no specified units, we will need to find a calibration factor $k$.
+To beautify the equation, we can collect all constants (which includes $r$ since all Type Ia supernova have the same intrinsic brightness) into $k$.
+This gives
+
+\begin{equation}
+\begin{aligned}
+  d &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
+    &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
+\end{aligned}
+\end{equation}
+
+The results of this model are shown in Figure \ref{fig:corrected_uncalibrated}.
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
+  \caption{Uncalibrated distance model using the corrected $B^*$ values for
+  brightness.}
+  \label{fig:corrected_uncalibrated}
+\end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
+  \caption{Uncalibrated distance model using the uncorrected $B$ values for brightness.
+  The deviation from linearity suggests that distant objects are
+  farther away than expected due to an accelerated expansion rate.}
+  \label{fig:uncorrected_uncalibrated}
+\end{figure}
+
+It's worth noting that previous studies use $B$ instead of $B*$. According to
+\citet{betoule2014},
+
+\begin{displayquote}
+  Specifically, the distance estimator used in this analysis (and in most
+  similar cosmological analyses) assumes that supernovae with identical color,
+  shape and galactic environment have on average the same intrinsic luminosity
+  for all redshifts.
+\end{displayquote}
+
+This leads to
+
+\begin{equation}
+  d_{\text{uncorrected}} = k 10^\frac{M}{5}
+\end{equation}
+
+which is displayed in Figure \ref{fig:uncorrected_uncalibrated}.
 
@@
 
-\section{Discussion of discrepancy}
+Calibrating a distance model involves finding a linear regression line for a
+model and then computing the value $k$ required to make the regression model
+match a Hubble paramater. By arbitrary choice, we use $H_0 = 70 \frac{km/s}{Mpsc}$.
 
-\section{Conclusions}
-What the heck?
+The final units for distance will be in megaparsecs $Mpsc$. To find the
+recessional speed for a given redshift, we use $v = cz$ where $c$ is the speed
+of light.
+
+To compute a model, we use non-parametric regression via repeated means as described in
+\citet{siegel1982}. A comparison of both models is shown in Figure \ref{fig:calibrated}.
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
+  \caption{Calibrated distance model using both the corrected $B^*$ values as
+  well as the uncorrected $B$ brightness values.}
+  \label{fig:calibrated}
+\end{figure}
+
+\section{Next steps}
+\label{sec:nextsteps}
+
+Is my understanding of the literature correct? My understanding is that
+existing models don't correct for the impact of redshift on the brightness of
+distant objects, and models that use an accelerating expansion for the universe
+are based on adding that correction back into the model.
 

### 2024-11-05 src/redshift/supernova.py

@@ -377,30 +377,61 @@ def bootstrap_H0_graph(data, corrected, trials, save=True):
         plt.cla()
 
 
+def effective_magnitude_vs_log_redshift_graph(data, save=True):
+    xs = [sn.redshift for sn in data]
+    ys = [sn.magnitude for sn in data]
+    plt.scatter(xs, ys, s=2, marker=".", color="black")
+    plt.xscale("log")
+
+    plt.title("magnitude vs redshift")
+    plt.xlabel("z")
+    plt.ylabel("magnitude")
+    #coefficients = scipy.stats.siegelslopes(x=xs, y=ys)
+    #m, b = coefficients.slope, coefficients.intercept
+    #m, b = np.polyfit(xs, ys, 1)
+    #plt.axline(
+    #    (0, b),
+    #    (1, m + b),
+    #    color="black",
+    #    linewidth=0.5,
+    #)
+    if save:
+        plt.savefig(
+            GRAPHS_DIR / f"magnitude_vs_log_redshift.png",
+            bbox_inches="tight",
+        )
+        plt.cla()
+
+
 def generate_all_graphs(data, save=True):
     uncalibrated_graph(data, corrected=True, save=save)
     uncalibrated_graph(data, corrected=False, save=save)
     both_calibrated_redshift_vs_distance_graph(data, save=save)
     both_calibrated_velocity_vs_distance_graph(data, save=save)
-    bootstrap_H0_graph(data, corrected=True, trials=1000, save=save)
-    bootstrap_H0_graph(data, corrected=False, trials=1000, save=save)
-    bootstrap_z_vs_ud_graph(data, corrected=True, trials=1000, save=save)
+    #bootstrap_H0_graph(data, corrected=True, trials=1000, save=save)
+    #bootstrap_H0_graph(data, corrected=False, trials=1000, save=save)
+    #bootstrap_z_vs_ud_graph(data, corrected=True, trials=1000, save=save)
 
 
 if __name__ == "__main__":
+    plt.rcParams["figure.figsize"] = (15, 10)
+
     # data = Supernova.from_rochester()
     data = Supernova.from_betoule()
-    generate_all_graphs(data)
-    exit()
     #data = Supernova.from_perlmutter()
+    generate_all_graphs(data)
+    #effective_magnitude_vs_log_redshift_graph(data, save=False)
+    #plt.show()
+    exit()
 
-    xs = [sn.redshift for sn in data]
[…]

### 2024-11-05 paper/paper.tex
Add notes for Next steps

@@
 
-TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarizd in \citet{straumann2012}.
+TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarized in \citet{straumann2012}.
 
@@
 
-Luminosity distance, $D_L$, is the appearant distance of an object based on the
+Luminosity distance, $D_L$, is the apparent distance of an object based on the
 measured luminosity. This does not take into account any movement of the
@@
 the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
-More formally, for two objects of the same radius $r$, the appearant area $A$
+More formally, for two objects of the same radius $r$, the apparent area $A$
 is
@@
 
+If that's accurate, it would be interesting to repeat the computation of
+cosmological constants. Is there evidence for acceleration or deceleration
+for the expansion rate?
+
+Find a bigger dataset. Use \citet{abbott2024} perhaps?
+
+Is it necessary to figure out a hypothesis test? What would that even look
+like?
+
 \bibliographystyle{unsrtnat}

### 2024-11-08 src/redshift/supernova.py
Add a Hubble diagram

@@ -40,7 +40,7 @@ class Supernova:
 
     @property
     def corrected_magnitude(self):
-        return self.magnitude * (self.z + 1)
+        return self.magnitude - np.log(1 + self.z) / np.log(100**0.2)
 
     @staticmethod
     def _uncalibrated_distance(corrected, magnitude, z):
@@ -95,12 +95,13 @@ class Supernova:
         with open(DATA_DIR / "jla_lcparams.txt", "r") as csv_file:
             raw = csv.reader(csv_file)
             header = next(raw)
+            idx = {val: i for i, val in enumerate(header)}
             for row in raw:
                 sn = Supernova(
-                    name=row[name_idx],
-                    magnitude=float(row[magnitude_idx]),
-                    magnitude_error=float(row[magnitude_error_idx]),
-                    redshift=float(row[z_idx]),
+                    name=row[idx["#name"]],
+                    magnitude=float(row[idx["mb"]]),
+                    magnitude_error=float(row[idx["dmb"]]),
+                    redshift=float(row[idx["zcmb"]]),
                 )
                 data.append(sn)
         return data
@@ -167,10 +168,10 @@ class Calibration:
 
 
 def uncalibrated_graph(data, corrected=True, save=True):
-    plt.cla()
+    plt.rcParams["figure.figsize"] = (8, 6)
     xs = [sn.redshift for sn in data]
     ys = [sn.uncalibrated_distance(corrected) for sn in data]
-    plt.scatter(xs, ys, s=2, marker=".", color="blue" if corrected else "red")
+    plt.scatter(xs, ys, marker=".", color="blue" if corrected else "darkorange")
 
     coefficients = scipy.stats.siegelslopes(x=xs, y=ys)
     plt.axline(
@@ -201,16 +202,16 @@ def uncalibrated_graph(data, corrected=True, save=True):
 
 
 def both_calibrated_redshift_vs_distance_graph(data, save=True):
-    plt.cla()
+    plt.rcParams["figure.figsize"] = (8, 6)
     ys = [sn.redshift for sn in data]
 
     cal = Calibration(data, corrected=False)
     xs = [sn.calibrated_distance(cal) for sn in data]
-    plt.scatter(xs, ys, s=2, marker=".", color="red")
[…]

### 2024-11-10 paper/paper.tex
Recolor graphs

@@
 
-Luminosity distance, $D_L$, is the apparent distance of an object based on the
-measured luminosity. This does not take into account any movement of the
-observed object between the time when the light was emitted and the light is
-observed.
+Luminosity distance $D_L$, is the apparent distance of an object based on the
+observed luminisity, also known as the flux $F$.  This does not take into
+account any movement of the observed object between the time when the light was
+emitted and the light is observed. $D_L$ also does not take into account
+redshift. We are instead interested in $D_{L^*}$, which is the distance based
+on the luminosity corrected for redshift.
 
 Measurements of Type Ia supernova provide magnitude and redshift. To derive the
-luminosity distance from these measurements, we start by computing the relative
-brightness. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has
-100 times the brightness of magnitude 6. To convert magnitude to relative
-brightness $B$, we use
+luminosity distance from these measurements, we start by computing the flux
+$L$. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has 100
+times the brightness of magnitude 6, leading to
 
 \begin{equation}
-  B = \frac{1}{\sqrt[5]{100}^{M - 1}}.
+  F = \frac{1}{\sqrt[5]{100}^{M - 1}}.
 \end{equation}
@@
 \begin{equation}
-  B^{*} = B \frac{E_{\text{emit}}}{E_{\text{obs}}}.
+  F^{*} = F \frac{E_{\text{emit}}}{E_{\text{obs}}}.
 \end{equation}
@@
 \begin{aligned}
-  B^{*} &= B \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
-        &= B \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
+  F^{*} &= F \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
+        &= F \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
 \end{aligned}
@@
 \begin{aligned}
-  B^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
+  F^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
         &= B(1 + z).
+\end{aligned}
+\end{equation}
+
+To compute the corrected magnitue $M^*$, we can solve
+
+\begin{equation}
+\begin{aligned}
+   F^* &= \frac{1}{\sqrt[5]{100}^{M^* - 1}} \\
+   M^* &= M - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
 \end{aligned}
@@
 
-where $d$ is the relative distance between the two objects.
+where $D$ is the relative distance between the two objects.
 
@@
 
+\begin{equation*}
+  F^{*} = \pi \bigg(\frac{r}{D}\bigg)^2
+\end{equation*}
+
 \begin{equation}
-\begin{aligned}
-  B^{*} = \pi \bigg(\frac{r}{d}\bigg)^2 \\
-      d = r \sqrt{\frac{\pi}{B^*}}.
-\end{aligned}
+\label{eq:D*}
+  D_{L^*} = r \sqrt{\frac{\pi}{F^*}}.
 \end{equation}
 
-Finally, since this equation has no specified units, we will need to find a calibration factor $k$.
-To beautify the equation, we can collect all constants (which includes $r$ since all Type Ia supernova have the same intrinsic brightness) into $k$.
-This gives
+Since this equation has no specified units, we will need to find a
+calibration factor $k$. To beautify the equation, we can collect all constants
+(which includes $r$ since all Type Ia supernova have the same intrinsic
+brightness) into $k$. This gives
 
@@
 \begin{aligned}
-  d &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
+  D_{L^*} &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
           &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
@@
   \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
-  \caption{Uncalibrated distance model using the corrected $B^*$ values for
-  brightness.}
+  \caption{Uncalibrated distance model using the corrected $F^*$ values for
+  brightness. The data were obtained from \citet{betoule2014}.}
   \label{fig:corrected_uncalibrated}
@@
   \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
-  \caption{Uncalibrated distance model using the uncorrected $B$ values for brightness.
+  \caption{Uncalibrated distance model using the uncorrected $F$ values for brightness.
   The deviation from linearity suggests that distant objects are
@@
 
-It's worth noting that previous studies use $B$ instead of $B*$. According to
-\citet{betoule2014},
-
-\begin{displayquote}
-  Specifically, the distance estimator used in this analysis (and in most
-  similar cosmological analyses) assumes that supernovae with identical color,
-  shape and galactic environment have on average the same intrinsic luminosity
-  for all redshifts.
-\end{displayquote}
-
-This leads to
-
-\begin{equation}
-  d_{\text{uncorrected}} = k 10^\frac{M}{5}
-\end{equation}
-
-which is displayed in Figure \ref{fig:uncorrected_uncalibrated}.
-
 \section{Calibrated distance models}
-\label{sec:disproof}
+\label{sec:calibrated}
 
@@
   \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
-  \caption{Calibrated distance model using both the corrected $B^*$ values as
-  well as the uncorrected $B$ brightness values.}
+  \caption{Calibrated distance model using both the corrected $F^*$ values as
+  well as the uncorrected $F$ brightness values.}
   \label{fig:calibrated}
@@
 
-\section{Next steps}
-\label{sec:nextsteps}
+\section{Disagreement with existing research}
 
-Is my understanding of the literature correct? My understanding is that
-existing models don't correct for the impact of redshift on the brightness of
-distant objects, and models that use an accelerating expansion for the universe
-are based on adding that correction back into the model.
+Previous studies use $F$ instead of $F*$. According to \citet{betoule2014},
 
-If that's accurate, it would be interesting to repeat the computation of
-cosmological constants. Is there evidence for acceleration or deceleration
-for the expansion rate?
+\begin{displayquote}
+  Specifically, the distance estimator used in this analysis (and in most
+  similar cosmological analyses) assumes that supernovae with identical color,
+  shape and galactic environment have on average the same intrinsic luminosity
+  for all redshifts. This hypothesis is quantified by a linear model, yielding
+  a standardized distance modulus $\mu = 5 \log_{10}{(d_L / 10 \text{pc})}$:
 
-Find a bigger dataset. Use \citet{abbott2024} perhaps?
+  \begin{equation}
+  \label{eq:betoule_distance_modulus}
+    \mu = m_B^* - (M_B - \alpha \times X_1 + \beta \times C)
+  \end{equation}
 
-Is it necessary to figure out a hypothesis test? What would that even look
-like?
+  where $m_B^*$ corresponds to the observed peak magnitude in restframe $B$
+  band and $\alpha$, $\beta$ and $M_B$ are nuisance parameters in the distance
+  estimate.
+\end{displayquote}
+
+This statement may refer to the idea that a Type Ia supernova can have an
+evolving intrinsic luminosity $L$ over time as conditions within the universe
+change which was first hypothesized by \citet{tinsley1968}. In Equation
+\ref{eq:betoule_distance_modulus}, there is no correction for redshift, which
+suggests the interpretation that the flux $F$ is unaffected by redshift.
+
+The model where $F$ is not corrected for redshift is explored in Figure
+\ref{fig_uncorrected_uncalibrated} by replacing $F^*$ with $F$ in Equation
+\ref{eq:D*} and obtaining
+
+\begin{equation}
+  D_L = k 10^\frac{M}{5}.
+\end{equation}
+
+\section{Conclusions}
+\label{sec:conclusions}
 

### 2024-11-10 src/redshift/supernova.py

@@ -77,7 +77,7 @@ class Supernova:
                     name=row[idx["name"]],
                     magnitude=float(row[idx["mb_eff"]]),
                     magnitude_error=float(row[idx["mb_eff_error"]]),
-                    redshift=float(row[idx["z"]])
+                    redshift=float(row[idx["z"]]),
                 )
                 data.append(sn)
         return data
@@ -171,7 +171,18 @@ def uncalibrated_graph(data, corrected=True, save=True):
     plt.rcParams["figure.figsize"] = (8, 6)
     xs = [sn.redshift for sn in data]
     ys = [sn.uncalibrated_distance(corrected) for sn in data]
-    plt.scatter(xs, ys, marker=".", color="blue" if corrected else "darkorange")
+    if corrected:
+        plt.scatter(
+            xs,
+            ys,
+            s=15,
+            marker="^",
+            linewidths=0.7,
+            facecolors="none",
+            edgecolors="blue",
+        )
+    else:
+        plt.scatter(xs, ys, s=15, marker="x", linewidths=0.7, color="red")
 
     coefficients = scipy.stats.siegelslopes(x=xs, y=ys)
     plt.axline(
@@ -207,11 +218,19 @@ def both_calibrated_redshift_vs_distance_graph(data, save=True):
 
     cal = Calibration(data, corrected=False)
     xs = [sn.calibrated_distance(cal) for sn in data]
-    plt.scatter(xs, ys, marker=".", color="darkorange")
+    plt.scatter(xs, ys, s=15, marker="x", linewidths=0.7, color="red")
 
     cal = Calibration(data, corrected=True)
     xs = [sn.calibrated_distance(cal) for sn in data]
-    plt.scatter(xs, ys, marker=".", color="blue")
+    plt.scatter(
+        xs,
+        ys,
+        s=15,
+        marker="^",
+        linewidths=0.7,
+        facecolors="none",
+        edgecolors="blue",
+    )
 
     plt.xlabel("distance (Mpsc)")
     plt.ylabel("z")
@@ -231,11 +250,28 @@ def both_calibrated_velocity_vs_distance_graph(data, save=True):
 
     cal = Calibration(data, corrected=False)
     xs = [sn.calibrated_distance(cal) for sn in data]
-    plt.scatter(xs, ys, marker=".", color="darkorange", label="uncorrected")
+    plt.scatter(
+        xs,
[…]

### 2024-11-18 paper/paper.tex
Start the rewrite

@@
 
-\def \thetitle {Correcting supernova luminosity for redshift implies no accelerated expansion}
+\def \thetitle {Correcting supernova luminosity for time dilation implies no dark energy}
 \title{\thetitle}
@@
   Existing analysis of Type Ia supernova relies on the assumption that
-  luminosity is not affected by redshift. However, when luminosity is corrected
-  for redshift, the relationship between luminosity distance and redshift for
-  Type Ia supernova becomes linear. This implies that the expansion rate of the
-  universe is not accelerating and there is no need for dark energy to explain
-  observational data.
+  luminosity is not affected by time dilation. However, when luminosity is
+  corrected for time dilation, the relationship between luminosity distance and
+  redshift for Type Ia supernova becomes linear. This indicates that the
+  expansion rate of the universe is not accelerating and there is no need for
+  dark energy to explain observational data.
 \end{abstract}
@@
 
-\section{Derivation of luminosity distance}
+\section{The dimming effects of redshift}
+
+The characteristics of redshift depend on the reason distant objects are
+redshifted. The dominant model is the big bang theory, where the farther away
+an object is from us, the more quickly it is moving away from us. Another
+theory is the tired light hypothesis, as described by \citet{shao2013}, where
+distant objects are mostly stationary relative to us, but where the energy of
+light is lost as it travels through space. A feature of the tired light
+hypothesis is that since distant objects do not have a high relative velocity
+to us, they should not show time dilation. However, as shown by
+\citet{white2024}, distant supernova do experience time dilation. Based on
+this, we reject the tired light hypothesis and assume the big bang model.
+
+The magnitude measurements for Type Ia supernova goes through a long chain of
+data processing. The data used here was collected by the Dark Energy Survey
+Collaboration, as summarized in \citet{abbott2024}, while \citet{vincenzi2024}
+describes the data processing pipeline in more detail. However, the data
+processing does not explicitly correct for either redshift or time dilation.
+
+In the big bang model, there are two phenomena associated with redshift that we
+might expect to reduce the appearant magnitude of a Type Ia supernova. The
+first phenomenon is that the energy carried by a photon is inversely
+proportional to wavelength, so as redshift increases the wavelength of a
+photon, the energy decreases. The second phenomenon is that time dilation for
+objects moving quickly relative to our observational rest frame will reduce the
+rate at which photons are being emitted.
+
+The supernova data collected by the DES Collaboration used a CCD camera, a
+photon counting device, as described by \citet{flaughter2015}.  As noted by
+\citet{kim1996}, photometric measurements that depend on bolometers will need
+to be corrected for the reduced energy level of redshifted light, but with a
+photon counting device, this correction is not necessary.
+
+However, time dilation also reduces the magnitude of light. Instead of changing
+the properties of individual photons, it reduces the count of photons by a
+factor of $\frac{1}{1+z}$. This phenomenon will not be addressed by the nuances
+of any measuring device, so it must be explicitly corrected.
+
+\section{Correcting magnitude for time dilation}
 
 Luminosity distance $D_L$, is the apparent distance of an object based on the
-observed luminisity, also known as the flux $F$.  This does not take into
+observed luminosity, also known as the flux $F$. This does not take into
 account any movement of the observed object between the time when the light was
-emitted and the light is observed. $D_L$ also does not take into account
-redshift. We are instead interested in $D_{L^*}$, which is the distance based
-on the luminosity corrected for redshift.
+emitted and the light is observed.
 
-Measurements of Type Ia supernova provide magnitude and redshift. To derive the
-luminosity distance from these measurements, we start by computing the flux
-$L$. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has 100
-times the brightness of magnitude 6, leading to
+To derive the luminosity distance from these measurements, we start
+by computing the flux $L$. Magnitude $M$ is defined on a logarithmic scale
+where magnitude 1 has 100 times the brightness of magnitude 6, leading to
 
@@
 
-This is proportional to the amount of energy detected by a telescope. However,
-we instead want a number that is proportional to the number of photons detected
-by the telescope. Redshifting decreases the amount of energy carried by a
-photon from $E_{\text{emit}}$ to $E_{\text{obs}}$, but we can correct for this
-phenomenon by taking
-
-\begin{equation}
-  F^{*} = F \frac{E_{\text{emit}}}{E_{\text{obs}}}.
-\end{equation}
-
-Since the energy for a photon is given by $E = \frac{hc}{\lambda}$ where $h$ is
-the Planck constant and $c$ is the speed of light, we have
+This is proportional to the number of photons detected by a telescope. We can
+find the corrected flux $F^*$ by multiplying by $k(z)$, the redshift correction factor. Time
+dilation of quickly moving objects reduces the number of photons by a factor of
+$\frac{1}{1 + z}$, so we have
 
@@
 \begin{aligned}
-  F^{*} &= F \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
-        &= F \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
-\end{aligned}
-\end{equation}
-
-We use the redshift equation $(1 + z)\lambda_{\text{emit}} =
-\lambda_{\text{obs}}$ to obtain
-
-\begin{equation}
-\begin{aligned}
-  F^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
-        &= B(1 + z).
+  F^* &= F \times k(z) \\
+      &= F (1 + z).
 \end{aligned}
@@
 
-We note that since all Type Ia supernova have approximately the same intrinsic
-brightness, we can use a geometric model to compute relative distances. Imagine
-holding up two coins, one in each hand.  If you arange them so that the
-distance from your eyes to the first coin double the distance from your eyes to
-the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
-More formally, for two objects of the same radius $r$, the apparent area $A$
-is
-
-\begin{equation}
-  A = \pi \bigg(\frac{r}{d}\bigg)^2
-\end{equation}
-
-where $D$ is the relative distance between the two objects.
-
-Replacing the area with the brightness, we have
-
-\begin{equation*}
-  F^{*} = \pi \bigg(\frac{r}{D}\bigg)^2
-\end{equation*}
-
-\begin{equation}
-\label{eq:D*}
-  D_{L^*} = r \sqrt{\frac{\pi}{F^*}}.
-\end{equation}
-
-Since this equation has no specified units, we will need to find a
-calibration factor $k$. To beautify the equation, we can collect all constants
-(which includes $r$ since all Type Ia supernova have the same intrinsic
-brightness) into $k$. This gives
-
-\begin{equation}
-\begin{aligned}
-  D_{L^*} &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
-          &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
-\end{aligned}
-\end{equation}
-
-The results of this model are shown in Figure \ref{fig:corrected_uncalibrated}.
-
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
-  \caption{Uncalibrated distance model using the corrected $F^*$ values for
-  brightness. The data were obtained from \citet{betoule2014}.}
+  \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
+  \caption{todo}
   \label{fig:corrected_uncalibrated}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
-  \caption{Uncalibrated distance model using the uncorrected $F$ values for brightness.
-  The deviation from linearity suggests that distant objects are
-  farther away than expected due to an accelerated expansion rate.}
+  \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
+  \caption{todo}
   \label{fig:uncorrected_uncalibrated}
@@
 To compute a model, we use non-parametric regression via repeated means as described in
-\citet{siegel1982}. A comparison of both models is shown in Figure \ref{fig:calibrated}.
-
-\begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
-  \caption{Calibrated distance model using both the corrected $F^*$ values as
-  well as the uncorrected $F$ brightness values.}
-  \label{fig:calibrated}
-\end{figure}
+\citet{siegel1982}. A comparison of both models is shown in Figure .
 
@@
 Previous studies use $F$ instead of $F*$. According to \citet{betoule2014},
-
-\begin{displayquote}
-  Specifically, the distance estimator used in this analysis (and in most
-  similar cosmological analyses) assumes that supernovae with identical color,
-  shape and galactic environment have on average the same intrinsic luminosity
-  for all redshifts. This hypothesis is quantified by a linear model, yielding
-  a standardized distance modulus $\mu = 5 \log_{10}{(d_L / 10 \text{pc})}$:
-
-  \begin{equation}
-  \label{eq:betoule_distance_modulus}
-    \mu = m_B^* - (M_B - \alpha \times X_1 + \beta \times C)
-  \end{equation}
-
-  where $m_B^*$ corresponds to the observed peak magnitude in restframe $B$
-  band and $\alpha$, $\beta$ and $M_B$ are nuisance parameters in the distance
-  estimate.
-\end{displayquote}
-
-This statement may refer to the idea that a Type Ia supernova can have an
-evolving intrinsic luminosity $L$ over time as conditions within the universe
-change which was first hypothesized by \citet{tinsley1968}. In Equation
-\ref{eq:betoule_distance_modulus}, there is no correction for redshift, which
-suggests the interpretation that the flux $F$ is unaffected by redshift.
-
-The model where $F$ is not corrected for redshift is explored in Figure
-\ref{fig_uncorrected_uncalibrated} by replacing $F^*$ with $F$ in Equation
-\ref{eq:D*} and obtaining
 

### 2024-11-18 src/redshift/cepheid.py

@@ -1,0 +1,211 @@
+from __future__ import annotations
+from dataclasses import dataclass
+from matplotlib import pyplot as plt
+import os
+import math
+from pprint import pprint
+import csv
+import numpy as np
+import pathlib
+import scipy
+from enum import Enum
+
+REPO_DIR = pathlib.Path(os.environ["VIRTUAL_ENV"]).parent.resolve()
+DATA_DIR = REPO_DIR / "data"
+GRAPHS_DIR = REPO_DIR / "graphs"
+
+
+class Correction(Enum):
+    NONE = 0
+    RV = 1  # Recessional velocity
+    TL = 2  # Tired light
+
+
+@dataclass()
+class Cepheid:
+    field: str
+    alpha: float
+    delta: float
+    id: float
+    period: float
+    V_minus_I: float
+    F160W: float
+    sigma: float
+    offset: float
+    bias: float
+    IMrms: float
+    o_h: float
+    flag: str
+
+    _field2z = {
+        "n1309": 0.007125,
+        "n3021": 0.00514,
+        "n3370": 0.004266,
+        "n3982": 0.003699,
+        "n4038": 0.005477,
+        "n4258": 0.001494,
+        "n4536": 0.006031,
+        "n4639": 0.003395,
+        "n5584": 0.005464,
+    }
+
+    @staticmethod
+    def from_riess():
+        data = []
+        with open(DATA_DIR / "riess_2011_cepheids.csv", "r") as fin:
+            reader = csv.reader(fin)
+            header = next(reader)
+            idx = {val: i for i, val in enumerate(header)}
+
+            for row in reader:
+                params = {}
+                for key in [
+                    "alpha",
+                    "delta",
+                    "id",
+                    "period",
+                    "V_minus_I",
+                    "F160W",
+                    "sigma",
+                    "offset",
+                    "bias",
+                    "IMrms",
+                    "o_h",
+                ]:
+                    params[key] = float(row[idx[key]])
+
+                for key in ["field", "flag"]:
+                    params[key] = row[idx[key]]
+                data.append(Cepheid(**params))
+        return data
+
+    def magnitude(self, correction=Correction.NONE):
+        if correction == Correction.NONE:
+            return self.F160W
+        elif correction == Correction.RV:
+            return self.F160W - 2 * np.log(1 + self.z) / np.log(100**0.2)
[…]

### 2024-11-18 src/redshift/supernova.py

@@ -1,14 +1,16 @@
 from __future__ import annotations
+from bisect import bisect
 from dataclasses import dataclass, field, asdict
-from numpy.polynomial.polynomial import Polynomial
 from datetime import date
 from matplotlib import pyplot as plt
-from matplotlib import pyplot as plt
+from numpy.polynomial.polynomial import Polynomial
 from pprint import pprint
 from typing import ClassVar
+from enum import Enum
 import csv
 import jdcal
 import json
+import math
 import numpy as np
 import os
 import pathlib
@@ -20,6 +22,12 @@ DATA_DIR = REPO_DIR / "data"
 GRAPHS_DIR = REPO_DIR / "graphs"
 
 
+class Correction(Enum):
+    NONE = 0
+    ONE = 1  # Single correction factor: 1+z
+    TWO = 2  # Two correction factors: (1+z)^2
+
+
 def parse_jd_date(jd: str):
     year, month, day, _ = jdcal.jd2gcal(float(jd), 0)
     return date(year=year, month=month, day=day)
@@ -27,10 +35,17 @@ def parse_jd_date(jd: str):
 
 @dataclass()
 class Supernova:
+    redshift: float
     name: str | None
     magnitude: float
-    magnitude_error: float
-    redshift: float
+
+    magnitude_error: float | None = field(default=None)
+    magnitude_uncorrected: float | None = field(default=None)
+    x1: float | None = field(default=None)
+    color: float | None = field(default=None)
+    absolute_magnitude: float | None = field(default=None)
+
+    MU: float | None = field(default=None)
 
     H0: ClassVar[float] = 70
 
@@ -38,29 +53,27 @@ class Supernova:
     def z(self):
         return self.redshift
 
-    @property
-    def corrected_magnitude(self):
-        return self.magnitude - np.log(1 + self.z) / np.log(100**0.2)
-
-    @staticmethod
-    def _uncalibrated_distance(corrected, magnitude, z):
-        d = 10 ** (magnitude / 5)
-        if corrected:
-            d /= np.sqrt(z + 1)
-        return d
-
-    def uncalibrated_distance(self, corrected):
-        return self._uncalibrated_distance(corrected, self.magnitude, self.z)
-
-    def calibrated_distance(self, calibration: Calibration):
-        return calibration.correction * self.uncalibrated_distance(
-            corrected=calibration.corrected
-        )
[…]

### 2024-11-19 paper/paper.tex
Flesh out more of the rewrite.

@@
 
-TODO: Discuss \citet{riess1998}, \citet{perlmutter1999}, and \citet{perlmutter2003}, as well as their nobel prize, summarized in \citet{straumann2012}.
-
-Summarize dark energy. Emphasize that dark energy is a popular explanation for
-why distant supernova appear to be too far away.
-
-Talk about the difficulty of curating supernova data, and summarize the work
-done by \citet{betoule2014}.
+TODO.
 
@@
 \section{The dimming effects of redshift}
-
-The characteristics of redshift depend on the reason distant objects are
-redshifted. The dominant model is the big bang theory, where the farther away
-an object is from us, the more quickly it is moving away from us. Another
-theory is the tired light hypothesis, as described by \citet{shao2013}, where
-distant objects are mostly stationary relative to us, but where the energy of
-light is lost as it travels through space. A feature of the tired light
-hypothesis is that since distant objects do not have a high relative velocity
-to us, they should not show time dilation. However, as shown by
-\citet{white2024}, distant supernova do experience time dilation. Based on
-this, we reject the tired light hypothesis and assume the big bang model.
 
@@
 
-In the big bang model, there are two phenomena associated with redshift that we
-might expect to reduce the appearant magnitude of a Type Ia supernova. The
-first phenomenon is that the energy carried by a photon is inversely
-proportional to wavelength, so as redshift increases the wavelength of a
-photon, the energy decreases. The second phenomenon is that time dilation for
-objects moving quickly relative to our observational rest frame will reduce the
-rate at which photons are being emitted.
+In the big bang model, there are multiple phenomena associated with redshift that we
+might expect to reduce the apparent magnitude of a Type Ia supernova.
+
+\subsection{Recessional velocity redshift}
+
+The energy carried by a photon is inversely proportional to wavelength, given
+by the Planck relation
+
+\begin{equation}
+  E = \frac{hc}{\lambda}
+\end{equation}
+
+where $E$ is energy, $h$ is the Planck constant, $c$ is the speed of light, and
+$\lambda$ is the wavelength.
+
+As redshift increases the wavelength of a photon, the energy decreases.
 
 The supernova data collected by the DES Collaboration used a CCD camera, a
-photon counting device, as described by \citet{flaughter2015}.  As noted by
-\citet{kim1996}, photometric measurements that depend on bolometers will need
-to be corrected for the reduced energy level of redshifted light, but with a
-photon counting device, this correction is not necessary.
+photon counting device, as described by \citet{flaughter2015}.  \citet{kim1996}
+noted that photometric measurements that depend on bolometers will need to be
+corrected for the reduced energy level of redshifted light, but with a photon
+counting device, this correction is not necessary.
 
-However, time dilation also reduces the magnitude of light. Instead of changing
-the properties of individual photons, it reduces the count of photons by a
-factor of $\frac{1}{1+z}$. This phenomenon will not be addressed by the nuances
-of any measuring device, so it must be explicitly corrected.
+While the redshift phenomenon should impact the light detected from distant
+supernova, it shouldn't impact the magnitude measurements so it does not need
+to be explicitly corrected.
+
+\subsection{Time dilation}
+
+The second phenomenon is that time dilation for objects moving quickly relative
+to our observational rest frame will reduce the rate at which photons are being
+emitted. Instead of changing the properties of individual photons, time
+dilation reduces the count of photons by a factor of $\frac{1}{1+z}$.
+
+This phenomenon will not be addressed by the nuances of any measuring device,
+so it must be explicitly corrected.
+
+\subsection{Stretching of space}
+
+If space itself is stretching, it will both increase the wavelength of photons
+and also reduce the density of those photons. If space is stretching at a
+constant rate, the effect would be indistinguishable from the redshift and time
+dilation created by high relative recessional velocities. However, an
+accelarting expansion of the universe may indicate a non-constant rate of
+stretching. This would manifest by distant objects having a greater distance
+per redshift than nearby objects.
+
+This non-linear streching-of-space model would be indistinguishable from a
+scenario where a constant force is pushing all objects away from each other.
+
+\subsection{Tired light}
+
+And alternative to the big bang theory is the tired light hypothesis, as
+described by \citet{zwicky1929} and \citet{shao2013}. The idea is that distant
+objects are mostly stationary relative to us, but the energy of light is lost
+as it travels through space. A feature of the tired light hypothesis is that
+since distant objects do not have a high relative velocity to us, they should
+not show time dilation.
+
+However, as shown by \citet{blonden2008} and \citet{white2024}, distant
+supernova do experience time dilation. Based on this, we can reject the tired
+light hypothesis and assume the big bang model.
 
@@
 To derive the luminosity distance from these measurements, we start
-by computing the flux $L$. Magnitude $M$ is defined on a logarithmic scale
+by computing the flux $F$. Magnitude $m$ is defined on a logarithmic scale
 where magnitude 1 has 100 times the brightness of magnitude 6, leading to
@@
 \begin{equation}
-  F = \frac{1}{\sqrt[5]{100}^{M - 1}}.
+  F = \frac{1}{\sqrt[5]{100}^{m - 1}}.
 \end{equation}
@@
 This is proportional to the number of photons detected by a telescope. We can
-find the corrected flux $F^*$ by multiplying by $k(z)$, the redshift correction factor. Time
-dilation of quickly moving objects reduces the number of photons by a factor of
-$\frac{1}{1 + z}$, so we have
+find the corrected flux $F^*$ by multiplying by $k(z)$, the redshift correction
+factor. Time dilation of quickly moving objects reduces the number of photons
+by a factor of $\frac{1}{1 + z}$, so we have
 
@@
 
-To compute the corrected magnitue $M^*$, we can solve
+To compute the corrected magnitude $m^*$, we can solve
 
@@
 \begin{aligned}
-   F^* &= \frac{1}{\sqrt[5]{100}^{M^* - 1}} \\
-   M^* &= M - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
+   F^* &= \frac{1}{\sqrt[5]{100}^{m^* - 1}} \\
+   m^* &= m - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
 \end{aligned}
@@
 
+From here, we can use the standard distance modules $\mu$ defined as
+
+\begin{equation}
+  \mu = m^* - M
+\end{equation}
+
+where $M$ is the absolute magnitude. The luminosity distance $D_L$ in parsecs
+can then be calculated as
+
+\begin{equation}
+  D_L = 10^{1 + \frac{\mu}{5}}.
+\end{equation}
+
+\section{Linear distance vs redshift relationship}
+
+The theory of an accelerating expansion is based on there being a non-linear
+relationship between redshift and distance. More specifically, old objects (the
+ones that are more distant) should have more distance per redshift than newer
+objects.
+
+As shown in Figure \ref{fig:mu_distance_vs_redshift}, this non-linear
+relationship is only observed when $k(z) = 1$, meaning that magnitude is not
+corrected for time dilation.
+
+In contrast, when $k(z) = 1 + z$, time dilation is accounted for and there is a
+linear relationship between redshift and distance. A linear model rules out an
+accellerated expansion.
+
 \begin{figure}[h!]
   \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
-  \caption{todo}
-  \label{fig:corrected_uncalibrated}
+  \caption{The relationship between distance and redshift for two treatments of
+  magnitude data. The displayed points are roughly a third of the values in the
+  full DES dataset, selected evenly to aid visibility. The $k(z) = 1$ treatment
+  is clearly non-linear while the $k(z) = 1 + z$ treatment appears to be
+  linear.}
+  \label{fig:mu_distance_vs_redshift}
 \end{figure}
@@
   \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
-  \caption{todo}
+  \caption{The expansion rate of the universe based on the full DES dataset.
+  This displays the full DES dataset using $k(z) = 1 + z$. The velocity $v$ is
+  calculated from $v = zc$, where $c$ is the speed of light. Note that the axis
+  are flipped compared to \ref{fig:mu_distance_vs_redshift}. In a perfectly
+  calibrated dataset, the fitted line should match the Hubble constant. This
+  graph is based on an absolute magnitude for Type Ia supernova at
+  $M = -19.3232$, which yields a slope of about $63 \frac{\text{km/s}}{\text{Mpc}}$.
+  If the absolute magnitude of a Type Ia supernova is instead $M = -19.102746$,
+  the slope would be $70 \frac{\text{km/s}}{\text{Mpc}}$.}
   \label{fig:uncorrected_uncalibrated}
@@
 
-\section{Calibrated distance models}
-\label{sec:calibrated}
-
-Calibrating a distance model involves finding a linear regression line for a
-model and then computing the value $k$ required to make the regression model
-match a Hubble paramater. By arbitrary choice, we use $H_0 = 70 \frac{km/s}{Mpsc}$.
-
-The final units for distance will be in megaparsecs $Mpsc$. To find the
-recessional speed for a given redshift, we use $v = cz$ where $c$ is the speed
-of light.
-
-To compute a model, we use non-parametric regression via repeated means as described in
-\citet{siegel1982}. A comparison of both models is shown in Figure .
-
 \section{Disagreement with existing research}
 
-Previous studies use $F$ instead of $F*$. According to \citet{betoule2014},
-
-\begin{equation}
-  D_L = k 10^\frac{M}{5}.
-\end{equation}
-
-\section{Conclusions}
-\label{sec:conclusions}
+Previous studies use $F$ instead of $F*$. To the best of our knowledge, no
+studies that depend on the distance of Type Ia supernova, reaching back at
+least to \citet{riess1998} and \citet{perlmutter1999}, have accounted for time
+dilation.
 

### 2024-11-19 src/redshift/supernova.py

@@ -359,7 +359,7 @@ def generate_all_graphs(data):
 
 
 if __name__ == "__main__":
-    plt.rcParams["figure.figsize"] = (8, 6)
+    plt.rcParams["figure.figsize"] = (80, 60)
     plt.rcParams["text.usetex"] = True
 
     # data = Supernova.from_rochester()
@@ -369,6 +369,6 @@ if __name__ == "__main__":
     generate_all_graphs(data)
 
     #all_mu_distance_vs_redshift_graph(data, save=False)
-    #velocity_vs_distance_graph(data, save=False)
+    velocity_vs_distance_graph(data, save=False)
     #hubble_diagram_graph(data, save=False)
     #plt.show()

### 2024-11-25 paper/paper.tex
Update paper.tex
The velocity graph was based on the wrong equation for redshift to velocity. In fact, since the graph would lead to velocities greater than the speed of light, that suggests that a stretching of space model may be a better fit than a recessional velocity model. Either way, the graph was wrong and need to be revisited.

@@
 
-\begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
-  \caption{The expansion rate of the universe based on the full DES dataset.
-  This displays the full DES dataset using $k(z) = 1 + z$. The velocity $v$ is
-  calculated from $v = zc$, where $c$ is the speed of light. Note that the axis
-  are flipped compared to \ref{fig:mu_distance_vs_redshift}. In a perfectly
-  calibrated dataset, the fitted line should match the Hubble constant. This
-  graph is based on an absolute magnitude for Type Ia supernova at
-  $M = -19.3232$, which yields a slope of about $63 \frac{\text{km/s}}{\text{Mpc}}$.
-  If the absolute magnitude of a Type Ia supernova is instead $M = -19.102746$,
-  the slope would be $70 \frac{\text{km/s}}{\text{Mpc}}$.}
-  \label{fig:uncorrected_uncalibrated}
-\end{figure}
-
 \section{Disagreement with existing research}

### 2024-11-28 paper/paper.tex
Checkpoint

@@
 While the redshift phenomenon should impact the light detected from distant
-supernova, it shouldn't impact the magnitude measurements so it does not need
+supernova, it should not impact the magnitude measurements so it does not need
 to be explicitly corrected.
@@
 emitted. Instead of changing the properties of individual photons, time
-dilation reduces the count of photons by a factor of $\frac{1}{1+z}$.
+dilation reduces the count of photons by a factor of $\frac{1}{1+z}$ where $z$
+is the redshift.
 
@@
 
-And alternative to the big bang theory is the tired light hypothesis, as
+An alternative to the big bang theory is the tired light hypothesis, as
 described by \citet{zwicky1929} and \citet{shao2013}. The idea is that distant

### 2024-11-28 src/redshift/supernova.py

@@ -64,7 +64,10 @@ class Supernova:
     @property
     def velocity_kms(self):
         c = 299792.458  # km/s
-        return self.z * c
+
+        z2 = self.z * self.z
+
+        return (c * z2 + 2 * c * self.z) / (z2 + 2 * self.z + 2)
 
     def mu(self, correction=Correction.NONE):
         return self.corrected_magnitude(correction) - self.absolute_magnitude
@@ -317,6 +320,7 @@ def hubble_diagram_graph(data, save=True):
 
 
 def velocity_vs_distance_graph(data, correction=Correction.ONE, save=True):
+    c = 299792.458  # km/s
     plt.rcParams["figure.figsize"] = (8, 6)
 
     xs = [sn.mu_distance(correction=correction) / 1e6 for sn in data]
@@ -331,14 +335,17 @@ def velocity_vs_distance_graph(data, correction=Correction.ONE, save=True):
         edgecolors="blue",
         label="k(z) = 1"
     )
-    coefficients = scipy.stats.siegelslopes(x=xs, y=ys)
-    plt.axline(
-        (min_x, min_x * coefficients.slope + coefficients.intercept),
-        (max_x, max_x * coefficients.slope + coefficients.intercept),
-        color="black",
-        linewidth=0.5,
-        linestyle="--",
-    )
+
+    #coefficients = scipy.stats.siegelslopes(x=xs, y=ys)
+    #plt.axline(
+    #    (min_x, min_x * coefficients.slope + coefficients.intercept),
+    #    (max_x, max_x * coefficients.slope + coefficients.intercept),
+    #    color="black",
+    #    linewidth=0.5,
+    #    linestyle="--",
+    #)
+
+    plt.hlines(c, xmin=min_x, xmax=max_x, label="c (speed of light)")
 
     plt.title("Linear Hubble constant")
     plt.xlabel("distance (Mpc)")
@@ -350,6 +357,26 @@ def velocity_vs_distance_graph(data, correction=Correction.ONE, save=True):
             bbox_inches="tight",
         )
         plt.cla()
+
+
+def delta_distance_graph(data, save=True):
+    #c = 299792.458  # km/s
+
+    def delta(d_one, d_none):
+        t = d_none / 9.71561e-9
+        return math.log(d_none / d_one) / t
+
+    plt.rcParams["figure.figsize"] = (8, 6)
+
+    xs = [sn.mu_distance(correction=Correction.ONE) for sn in data]
[…]

### 2024-11-28 paper/paper.tex
Account for the stretching of space
After a confirmation from A. Riess that time dilation is addressed, I
started considering if there might be a third cause for dimming. And
yes, there is.

@@
 
-\def \thetitle {Correcting supernova luminosity for time dilation implies no dark energy}
+\def \thetitle {Correcting supernova luminosity for stretched space implies no dark energy}
 \title{\thetitle}
@@
 \begin{abstract}
-  Existing analysis of Type Ia supernova relies on the assumption that
-  luminosity is not affected by time dilation. However, when luminosity is
-  corrected for time dilation, the relationship between luminosity distance and
-  redshift for Type Ia supernova becomes linear. This indicates that the
-  expansion rate of the universe is not accelerating and there is no need for
-  dark energy to explain observational data.
+  Estimating the distant to Type Ia supernova requires that luminosity be
+  corrected for various sources of dimming associated with redshift. The first
+  source of dimming is due to the redshifting of a photon's wavelength, and
+  this is addressed by a nuance of how CCD cameras collect light. The second
+  source of dimming is time dilation. A third source of dimming is due to the
+  stretching of space -- as space expands, light needs to travel farther to
+  traverse the extra space. When reported magnitudes for Type Ia supernovae are
+  corrected by an additional factor of $1 + z$, the relationship between
+  luminosity distance and redshift for Type Ia supernova becomes linear. This
+  indicates that the expansion rate of the universe is not accelerating and
+  there is no need for dark energy to explain observational data.
 \end{abstract}

### 2024-12-03 paper/paper.tex
Updates

--- 2024-11-28 paper/paper.tex
@@
 studies that depend on the distance of Type Ia supernova, reaching back at
-least to \citet{riess1998} and \citet{perlmutter1999}, have accounted for time
-dilation.
+least to \citet{kim1996}, \citet{riess1998}, and \citet{perlmutter1999}, have
+accounted for time dilation.
 

### 2024-12-03 src/redshift/supernova.py

@@ -61,6 +61,17 @@ class Supernova:
         else:  # Tired light
             return self.magnitude - np.log(1 + self.z) / np.log(100**0.2)
 
+    def inflation_rate(self):
+        # A = P e^(rt)
+        # T = xA
+        # A/P = e^(rx A)
+        # ln(A/P) = rx A
+        # r = ln(A/P) / (Ax)
+        A = self.mu_distance(correction=Correction.ONE)
+        P = self.orig_distance(correction=Correction.ONE)
+        x = 3.26156
+        return math.log(A / P) / (x * A)
+
     @property
     def velocity_kms(self):
         c = 299792.458  # km/s
@@ -72,11 +83,25 @@ class Supernova:
     def mu(self, correction=Correction.NONE):
         return self.corrected_magnitude(correction) - self.absolute_magnitude
 
-    def mu_distance(self, correction=Correction.NONE, use_mpc=True):
+    def mu_distance(self, correction=Correction.ONE, use_mpc=True):
         d = 10 ** (1 + self.mu(correction) / 5)
         if use_mpc:
             d /= 1e6
         return d
+
+    def orig_distance(self, correction=Correction.ONE):
+        return self.mu_distance(correction) / (self.z + 1)
+
+    def delta_distance(self, correction=Correction.ONE):
+        return self.mu_distance(correction) - self.orig_distance(correction)
+
+    def energy_loss(self):
+        # E = hc / l
+        # E_loss = hc/l - hc/(l*(1+z))
+        # E_loss = (hc(1+z) - hc) / (l(1+z))
+        # E_loss = hcz / (l(1+z))
+        # E_loss = hc/l * (z / (1+z))
+        return self.z / (1 + self.z)
 
     @staticmethod
     def from_perlmutter():
@@ -239,9 +264,8 @@ def all_mu_distance_vs_redshift_graph(data, save=True):
         linestyle="--",
     )
 
-
-    #ys = [sn.mu_distance(correction=Correction.TWO) for sn in data]
-    #plt.scatter(
+    # ys = [sn.mu_distance(correction=Correction.TWO) for sn in data]
+    # plt.scatter(
     #    xs,
     #    ys,
     #    s=15,
@@ -250,18 +274,18 @@ def all_mu_distance_vs_redshift_graph(data, save=True):
[…]

### 2024-12-09 paper/paper.tex
Start with a re-write.

@@
 
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{hyperref}       % hyperlinks
 \usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
 \usepackage{amsfonts}       % blackboard math symbols
@@
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
 \usepackage{graphicx}
 \usepackage{natbib}
-\usepackage{doi}
 \usepackage{csquotes}
 
-\def \thetitle {Correcting supernova luminosity for time dilation implies no dark energy}
-\title{\thetitle}
+\title{Dark energy is due to a math error from 1935}
 
@@
 
-%%% Add PDF metadata to help others organize their library
-%%% Once the PDF is generated, you can check the metadata with
-%%% $ pdfinfo template.pdf
 \hypersetup{
-pdftitle={\thetitle},
+pdftitle={Dark energy is due to a math error from 1935},
 pdfsubject={astro-ph.CO},
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
-\newtheorem{lemma}{Lemma}
-
 \begin{document}
@@
 \begin{abstract}
-  Existing analysis of Type Ia supernova relies on the assumption that
-  luminosity is not affected by time dilation. However, when luminosity is
-  corrected for time dilation, the relationship between luminosity distance and
-  redshift for Type Ia supernova becomes linear. This indicates that the
-  expansion rate of the universe is not accelerating and there is no need for
-  dark energy to explain observational data.
+  Observations of distant objects, such as supernovae and galaxies, is dimmed
+  due to three phenomena associated with redshift: energy levels per photon,
+  spectral bandwidth, and time dilation. Observed magnitudes are reported with
+  k-corrections that should correct for these dimming effects, but since 1935,
+  the equations used to perform these k-corrections have been missing the
+  correction factor for time dilation. When observations of Type Ia supernova
+  are corrected for this missing factor, the relationship between luminosity
+  distance and redshift for Type Ia supernova becomes linear. This indicates
+  that the expansion rate of the universe is not accelerating and there is no
+  need for dark energy to explain observational data.
 \end{abstract}
@@
 
-TODO.
+Observations of Type Ia supernova are fundamental to the study of cosmology.
+These measurements are necessary to calibrate models that measure redshift and
+estimate distance. This relationship, often called the Hubble-Lema\^{i}tre law,
+[TODO: find citation] describes how quickly the universe is expanding. However,
+\citet{riess1998} and \citet{perlmutter1999} presented evidence that there
+isn't a linear relationship between redshift and distance, but instead, distant
+objects are father away than their redshift would predict (see Figure
+\ref{fig:mu_distance_vs_redshift}). This phenomenon, whatever its source, is
+referred to as dark energy.
+
+Type Ia supernova are used to explore the relationship between distances and
+redshifts because these events always happen in similar ways, so the absolute
+brightness is roughly always the same. An analogy is to imagine someone walking
+in the dark and lighting matches. As long as we know how brightly a match burns
+at a known distance, we can estimate the distance to any match by measuring the
+appearant brightness before applying some geometry.
+
+It turns out that measuring the apperant brightness of a Type Ia supernova is
+non-trivial. The aspect of the process that we will explore here concerns how
+redshift affects the light we observe. This problem is often referred to as
+k-corrections, and one of the first mathematical treatments of the problem was
+performed by \citet{desitter1934}.
+
+Willem de Sitter recognized three issues that would reduce the observed
+magnitude of a distant observation. First, a redshifted photon carries less
+energy than when it was originally emitted. Second, a narrow spectrum of
+emitted light will be spread out over a larger observed spectrum. Finally, time
+dilation will reduce the rate at which an observer detects photons. The
+correction for each of these issues is identical: take a measurement and
+multiply it by the factor $1 + z$.
+
+A year later, \citet{hubble1935} published a similar set of calculations for
+k-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
+correction term used by de Sitter. The Hubble k-corrections have been used ever
+since.
+
+Hubble and de Sitter were clearly aware of all three dimming effects associated
+with redshift, but by \citet{oke1968energy}, the two factors of $(1 + z)$ were
+attributed to the change in energy and to the spectral bandwidth elongation,
+which leaves time dilation as the factor that was omitted.
+
+In 1935, the correction of $(1 + z)^2$ empirically lined up the data so that
+there seemed to be a linear relationship between redshift and distance. It
+wasn't until \citet{riess1998}, sixty-three years later, that the omission of a
+third $(1 + z)$ correction factor resulted in faulty conclusions.
+
+Those faulty conclusions, however, have been the basis for a substantial amount
+of scientific interest. In 2011, three physicists received the Nobel Prize in
+Physics for discovering that the expansion rate of the universe is accelerating
+\citet{straumann2012}. The papers \citet{riess1998} and \citet{perlmutter1999}
+have each received over 20000 citations. It's not clear how much cosmology work
+will need to be revisited with corrected distance measurements, but it is a
+non-trivial amount.
 
@@
 data processing. The data used here was collected by the Dark Energy Survey
-Collaboration, as summarized in \citet{abbott2024}, while \citet{vincenzi2024}
-describes the data processing pipeline in more detail. However, the data
-processing does not explicitly correct for either redshift or time dilation.
+Collaboration, as summarized in \citet{abbott2024} and described in more detail
+by \citet{vincenzi2024}. However, the data processing does not explicitly
+correct for either redshift or time dilation.
 
@@
 \begin{figure}[h!]
-  \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
+  \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
   \caption{The relationship between distance and redshift for two treatments of
@@
   linear.}
+  \label{fig:mu_distance_vs_redshift}
+\end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
+  \caption{An example of how k-corrections take an observed spectrum and
+  produce a rest-frame spectrum. [TODO]
+  }
+  \label{fig:mu_distance_vs_redshift}
+\end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{velocity_vs_distance.png}
+  \caption{The relationship between expansion velocity and distance. The slope of this graph demonstrates the Hubble constant.
+  }
+  \label{fig:mu_distance_vs_redshift}
+\end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\linewidth]{bootstrapped_H0.png}
+  \caption{A histogram of 100000 bootstrap trials measuring the Hubble constant
+  $H0$. Each trial samples an absolute Type Ia magnitude $M \sim Norm(-19.2334,
+  0.0404)$ based on data published by \citet{camarena2020}. It then samples,
+  with replacement, a population of supernovae from the dataset published by
+  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
+  technique described by \citet{siegel1982}. The result of the bootstrap is $H0
+  \sim Norm(65.94, 1.29)$.
+  }
   \label{fig:mu_distance_vs_redshift}

### 2024-12-09 src/redshift/supernova.py

@@ -1,5 +1,6 @@
 from __future__ import annotations
 from bisect import bisect
+import dataclasses
 from dataclasses import dataclass, field, asdict
 from datetime import date
 from matplotlib import pyplot as plt
@@ -19,7 +20,7 @@ import scipy
 
 REPO_DIR = pathlib.Path(os.environ["VIRTUAL_ENV"]).parent.resolve()
 DATA_DIR = REPO_DIR / "data"
-GRAPHS_DIR = REPO_DIR / "graphs"
+GRAPHS_DIR = REPO_DIR / "paper"
 
 
 class Correction(Enum):
@@ -102,7 +103,12 @@ class Supernova:
 
     @property
     def hubble(self):
-        return self.rate * self.mu_distance(use_mpc=False) * 3.086e+13 / (365 * 24 * 60 * 60)
+        return (
+            self.rate
+            * self.mu_distance(use_mpc=False)
+            * 3.086e13
+            / (365 * 24 * 60 * 60)
+        )
 
     @staticmethod
     def from_perlmutter():
@@ -165,10 +171,10 @@ class Supernova:
                     x1=float(row[idx["x1"]]),
                     MU=float(row[idx["MU"]]),
                     # see perivolaropoulos2022 for the Camerena and Marra references
-                    #absolute_magnitude=-19.105, # ~70km/s / Mpc
-                    #absolute_magnitude=-19.2334, # Camarena and Marra 2020b
-                    absolute_magnitude=-19.3232, # Abbott
-                    #absolute_magnitude=-19.401, # Camarena and Marra 2020a
+                    # absolute_magnitude=-19.105, # ~70km/s / Mpc
+                    absolute_magnitude=-19.2334, # Camarena and Marra 2020b
+                    # absolute_magnitude=-19.3232,  # Abbott
+                    # absolute_magnitude=-19.401, # Camarena and Marra 2020a
                     color=float(row[idx["c"]]),
                 )
                 data.append(sn)
@@ -203,6 +209,138 @@ class Supernova:
                     Supernova(name=row[idx["SN"]], magnitude=magnitude, redshift=z)
                 )
         return supernovas
+
+
+def k_corrections_for_photon_counts_graph(save=False):
[…]

### 2024-12-14 paper/paper.tex
Start writing code to check raw spectra

@@
 
-\title{Dark energy is due to a math error from 1935}
+\title{Dark energy is due to a math error from 1930}
 
@@
 dilation created by high relative recessional velocities. However, an
-accelarting expansion of the universe may indicate a non-constant rate of
+accelerating expansion of the universe may indicate a non-constant rate of
 stretching. This would manifest by distant objects having a greater distance
@@
 linear relationship between redshift and distance. A linear model rules out an
-accellerated expansion.
+accelerated expansion.
 

### 2024-12-14 src/redshift/okay_corrections.py

@@ -1,0 +1,156 @@
+from dataclasses import dataclass, field
+import csv
+from datetime import date, date, timedelta
+from pprint import pprint
+import jdcal
+from redshift import supernova
+import pathlib
+import os
+
+
+REPO_DIR = pathlib.Path(os.environ["VIRTUAL_ENV"]).parent.resolve()
+DATA_DIR = REPO_DIR / "data"
+LC_DIR = DATA_DIR / "cfalc_allsnIa"
+SPEC_DIR = DATA_DIR / "cfaspec_M08snIa"
+
+
+def parse_jd_date(jd: str):
+    year, month, day, _ = jdcal.jd2gcal(float(jd), 0)
+    return date(year=year, month=month, day=day)
+
+
+@dataclass()
+class LightCurveBand:
+    band: str
+    mag: float
+    std_dev: float
+
+
+@dataclass()
+class LightCurve:
+    timestamp: date
+    bands: dict[str, LightCurveBand]
+
+
+@dataclass()
+class Spec:
+    timestamp: date
+    wave: list[float]
+    spec: list[float]
+
+
+@dataclass()
+class SnInfo:
+    name: str
+    sn_type: str
+    host: str
+    discovery_timestamp: date
+    max_mag_timestamp: date
+    max_mag: float
+    last_mag_timestamp: date
+    last_mag: float
+    z: float
+    z_host: float
+    reference: str
+
+    @staticmethod
+    def all_info():
+        if not hasattr(SnInfo, "_all_info_cache"):
+            SnInfo._all_info_cache = {}
+
+            with open(DATA_DIR / "rochester-data.csv", "r") as csv_file:
+                reader = csv.reader(csv_file)
+
+                header = next(reader)
+                idx = {field: i for i, field in enumerate(header)}
+
+                for row in reader:
+                    sn_info = SnInfo(
+                        name=row[idx["SN"]].upper(),
+                        sn_type=row[idx["Type"]],
+                        host=row[idx["Host"]],
+                        discovery_timestamp=parse_jd_date(row[idx["Discovery date (JD)"]]),
+                        max_mag_timestamp=parse_jd_date(row[idx["Max mag date (JD)"]]),
+                        max_mag=float(row[idx["Max mag"]]),
+                        last_mag_timestamp=parse_jd_date(row[idx["Last mag date (JD)"]]),
+                        last_mag=float(row[idx["Last mag"]]),
[…]

### 2024-12-14 paper/paper.tex
Mention the 1930 paper

@@
 \hypersetup{
-pdftitle={Dark energy is due to a math error from 1935},
+pdftitle={Dark energy is due to a math error from 1930},
 pdfsubject={astro-ph.CO},
@@
 \begin{abstract}
-  Observations of distant objects, such as supernovae and galaxies, is dimmed
+  Light from distant objects, such as supernovae and galaxies, is dimmed
   due to three phenomena associated with redshift: energy levels per photon,
   spectral bandwidth, and time dilation. Observed magnitudes are reported with
-  k-corrections that should correct for these dimming effects, but since 1935,
+  k-corrections that should correct for these dimming effects, but since 1930,
   the equations used to perform these k-corrections have been missing the
@@
 isn't a linear relationship between redshift and distance, but instead, distant
-objects are father away than their redshift would predict (see Figure
-\ref{fig:mu_distance_vs_redshift}). This phenomenon, whatever its source, is
-referred to as dark energy.
+objects are farther away than their redshift would predict (see Figure
+\ref{fig:mu_distance_vs_redshift}). This phenomenon is referred to as dark
+energy.
 
@@
 k-corrections, and one of the first mathematical treatments of the problem was
-performed by \citet{desitter1934}.
+performed by \citet{tolman1930}. However, when Tolman made his derivation, he
+did not consider the effects of a spectra that is stretched out due to
+redshift.
 
-Willem de Sitter recognized three issues that would reduce the observed
-magnitude of a distant observation. First, a redshifted photon carries less
-energy than when it was originally emitted. Second, a narrow spectrum of
-emitted light will be spread out over a larger observed spectrum. Finally, time
-dilation will reduce the rate at which an observer detects photons. The
-correction for each of these issues is identical: take a measurement and
-multiply it by the factor $1 + z$.
+A few years later, \citet{desitter1934}, discussed all three issues that would
+reduce the observed magnitude of a distant observation. The correction for each
+of these issues is identical: take a measurement for luminosity and multiply it
+by the factor $1 + z$.
 
@@
 k-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
-correction term used by de Sitter. The Hubble k-corrections have been used ever
+correction term used by de Sitter. They started their derivation by copying the
+incorrect equation from 1930. After their derivation, they noted,
+
+\begin{quote}
+It should be specially noted that this expression differs from the correction
+to m proposed by de Sitter, which contains the term $(1 + z)^3$ instead of
+$(1 + z)^2$. Expression (28), however, would seem to give the proper correction
+to use in connection with our equation (21), since it has been derived in such
+a way as to make appropriate allowance, first, for the double effect of nebular
+recession in reducing both the individual energy and the rate of arrival of
+photons, and then for the further circumstance that a change in spectral
+distribution of the energy that does arrive will lead to changes in its
+photographic effectiveness.
+\end{quote}
+
+The Hubble k-corrections with the incorrect correction term have been used ever
 since.
 
-Hubble and de Sitter were clearly aware of all three dimming effects associated
-with redshift, but by \citet{oke1968energy}, the two factors of $(1 + z)$ were
-attributed to the change in energy and to the spectral bandwidth elongation,
-which leaves time dilation as the factor that was omitted.
+By \citet{oke1968}, the two factors of $(1 + z)$ were attributed to the change
+in energy and to the spectral bandwidth elongation, which leaves time dilation
+as the factor that was omitted.
 
@@
 there seemed to be a linear relationship between redshift and distance. It
-wasn't until \citet{riess1998}, sixty-three years later, that the omission of a
+wasn't until \citet{riess1998}, sixty-eight years later, that the omission of a
 third $(1 + z)$ correction factor resulted in faulty conclusions.
@@
 The supernova data collected by the DES Collaboration used a CCD camera, a
-photon counting device, as described by \citet{flaughter2015}.  \citet{kim1996}
+photon counting device, as described by \citet{flaugher2015}.  \citet{kim1996}
 noted that photometric measurements that depend on bolometers will need to be
@@
 
-However, as shown by \citet{blonden2008} and \citet{white2024}, distant
+However, as shown by \citet{blondin2008} and \citet{white2024}, distant
 supernova do experience time dilation. Based on this, we can reject the tired
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
@@
   }
-  \label{fig:mu_distance_vs_redshift}
 \end{figure}
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \includegraphics[width=\linewidth]{velocity_vs_distance.png}
@@
   }
-  \label{fig:mu_distance_vs_redshift}
 \end{figure}
 
-\begin{figure}[h!]
+\begin{figure}[ht]
   \includegraphics[width=\linewidth]{bootstrapped_H0.png}
@@
   }
-  \label{fig:mu_distance_vs_redshift}
 \end{figure}

### 2024-12-14 src/redshift/supernova.py

@@ -392,6 +392,7 @@ def all_mu_distance_vs_redshift_graph(data, save=True):
         x=[sn.z for sn in data],
         y=[sn.mu_distance(correction=Correction.NONE) for sn in data],
     )
+    print(coefficients.slope)
     plt.axline(
         (0, coefficients.intercept),
         (1, coefficients.slope + coefficients.intercept),
@@ -806,11 +807,9 @@ if __name__ == "__main__":
 
     data = Supernova.from_abbott()
 
-    # data, m, b, sigma = my_model(data)
+    #generate_all_graphs(data)
 
-    generate_all_graphs(data)
-
-    # all_mu_distance_vs_redshift_graph(data, save=False)
+    all_mu_distance_vs_redshift_graph(data, save=False)
     # velocity_vs_distance_graph(data, correction=Correction.ONE, save=False)
     # energy_loss_vs_orig_distance(data, correction=Correction.ONE, save=False)
     # recessional_velocity_vs_intercept_time_graph(data, correction=Correction.ONE, save=False)

### 2024-12-16 src/redshift/okay_corrections.py
Add data for filters and Barris 2004 data

@@ -93,9 +93,15 @@ class SnInfo:
 
 @dataclass()
 class Observation:
+    name: str
     timestamp: date
-    light_curve: LightCurve
-    spec: Spec
+    filt: Filter
+    flux: float
+    flux_std_dev: float
+    epoch: timedelta
+    kcorr_filt: Filter | None = field(default=None)
+    kcorr_mag: float | None = field(default=None)
+    kcorr_mag_std_dev: float | None = field(default=None)
 
 
 @dataclass()

### 2024-12-26 paper/paper.tex
Add a code example

@@
 \usepackage{csquotes}
+\usepackage{float}
+\usepackage{listings}
+\usepackage{xcolor}
+\usepackage{fancyvrb}
 
-\title{Dark energy is due to a math error from 1930}
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,
+    breaklines=true,
+    captionpos=b,
+    keepspaces=true,
+    numbers=left,
+    numbersep=5pt,
+    showspaces=false,
+    showstringspaces=false,
+    showtabs=false,
+    tabsize=2
+}
+
+\lstset{style=mystyle}
+
+\title{Dark energy is based on a math error from 1930}
 
@@
 \hypersetup{
-pdftitle={Dark energy is due to a math error from 1930},
+pdftitle={Dark energy is based on a math error from 1930},
 pdfsubject={astro-ph.CO},
@@
 \begin{abstract}
-  Light from distant objects, such as supernovae and galaxies, is dimmed
-  due to three phenomena associated with redshift: energy levels per photon,
-  spectral bandwidth, and time dilation. Observed magnitudes are reported with
-  k-corrections that should correct for these dimming effects, but since 1930,
-  the equations used to perform these k-corrections have been missing the
-  correction factor for time dilation. When observations of Type Ia supernova
-  are corrected for this missing factor, the relationship between luminosity
-  distance and redshift for Type Ia supernova becomes linear. This indicates
-  that the expansion rate of the universe is not accelerating and there is no
-  need for dark energy to explain observational data.
+  We show that the magnitude of distant objects has been calculated incorrectly
+  since 1930. We describe how this math error has propagated for over nine
+  decades. Finally, we explore the consequences of correcting this flaw and
+  resolve two of the preeminent mysteries in cosmology: dark energy is not
+  supported by observations of Type Ia supernovae, and the Hubble tension is
+  due to a calculation error.
 \end{abstract}
@@
 % keywords can be removed
-\keywords{Cosmological Parameters \and Dark Energy \and Luminosity Distance}
+\keywords{Cosmological Parameters \and Dark Energy \and Luminosity Distance \and Hubble tension}
 
@@
 
-Observations of Type Ia supernova are fundamental to the study of cosmology.
-These measurements are necessary to calibrate models that measure redshift and
-estimate distance. This relationship, often called the Hubble-Lema\^{i}tre law,
-[TODO: find citation] describes how quickly the universe is expanding. However,
-\citet{riess1998} and \citet{perlmutter1999} presented evidence that there
-isn't a linear relationship between redshift and distance, but instead, distant
-objects are farther away than their redshift would predict (see Figure
-\ref{fig:mu_distance_vs_redshift}). This phenomenon is referred to as dark
-energy.
+The measurement of Type Ia supernovae is one of the primary sources of data for
+cosmological models. The measurements involve estimating the peak magnitude in
+the B filter \citet{riess1998} for the rest frame, meaning we want to know how
+bright the SnIa would be if its light didn't undergo redshift. Redshift causes
+the light that would be mesaured by the B filter in a rest frame to be shifted
+to another filter. In order to observe a SnIa in an arbitrary filter and report
+the magnitude in filter B, we use a technique called k-corrections.
+
+The first formal derivation of k-corrections was performed by
+\citet{tollman1930}, and it failed to account for bandwidth stretching, one of
+the dimming effects of redshift. This error was noted by \citet{desitter1934},
+but in \citet{hubble1935} the descrepancy was noted and ignored.
+\citet{oke1968} rederived k-corrections, but they failed to account time
+dilation, one of the other dimming effects of redshift. In \citet{kim1996},
+k-corrections were extended to handle additional cross-filter comparisons and
+address zero-point corrections, but they started their derivation by
+referencing the incorrect equation from \citet{oke1968}. \citet{hsiao2007}
+expanded on the work done by \citet{kim1996} by providing expected SnIa
+template spectra.  Finally, \citet{burns2010} implemented the popular software
+package Sn(OO)py which implemented the SnIa template spectra into
+k-corrections. This software package computes k-corrections differently from
+prior work, and in order to match prior values, the code adds an extra term.
+This history is explored in more depth in Section \ref{sec:history}.
+
+The effect of using an incorrect magnitude for SnIa is that we think objects
+are farther away than they really are, and the effect componds for greater
+distances. Up until \citet{riess1998}, we didn't have distant enough
+observations for this error to matter much for cosmology models, but in the
+late 1990s, it was clear that our measurements for distance and redshift were
+not linear. This observation led to a model that utilized a cosmological
+constant and dark energy in order to explain the non-linear distance-redshift
+graph. We will show in Section \ref{sec:correction} that correcting the flaw
+with k-corrections leads to a linear graph that does not need to rely on a
+cosmological constant.
+
+Since \citet{planck2020}, it has been evident that something was missing with
+our understanding of cosmology. This research used an alternative technique
+based on measurements of the cosmic microwave background to measure the Hubble
+constant, but as summarized in \citet{perivolaropoulos2022}, this measurement
+was incompatable with the Hubble constant measured from SnIa. As we will
+discuss in Section \ref{sec:tension}, fixing the error with k-corrections
+produces a measurement of the Hubble constant that is compatible with models
+based on the cosmic microwave background.
+
+\section{A brief history of k-corrections}
+\label{sec:history}
+
+Observations of Type Ia supernova are essential to calibrate models that
+measure redshift and estimate distance. This relationship, often called the
+Hubble-Lema\^{i}tre law, describes how quickly the universe is expanding.
+However, \citet{riess1998} and \citet{perlmutter1999} presented evidence that
+there isn't a linear relationship between redshift and distance, but instead,
+distant objects are farther away than their redshift would predict (see Figure
+\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
+acceleration of the universe is faster today than it was for old observations.
+Previously the cause of this phenomenon was unknown and was referred to as
+dark energy.
+
+\begin{figure}[h]
+  \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
+  \caption{The relationship between distance and redshift for two treatments of
+  magnitude data. The displayed points are roughly a third of the values in the
+  full DES dataset, selected evenly to aid visibility. The $k(z) = 1$ treatment
+  is clearly non-linear while the $k(z) = 1 + z$ treatment appears to be
+  linear.}
+  \label{fig:mu_distance_vs_redshift}
+\end{figure}
 
@@
 
-It turns out that measuring the apperant brightness of a Type Ia supernova is
-non-trivial. The aspect of the process that we will explore here concerns how
-redshift affects the light we observe. This problem is often referred to as
-k-corrections, and one of the first mathematical treatments of the problem was
-performed by \citet{tolman1930}. However, when Tolman made his derivation, he
-did not consider the effects of a spectra that is stretched out due to
-redshift.
+Measuring the apperant brightness of a Type Ia supernova is non-trivial. The
+aspect of the process that we will explore here concerns how redshift affects
+the light we observe. This problem is often referred to as k-corrections, and
+one of the first mathematical treatments of the problem was performed by
+\citet{tolman1930}. However, when Tolman made his derivation, he did not
+consider the effects of a spectra that is stretched out due to redshift.
 
@@
 in energy and to the spectral bandwidth elongation, which leaves time dilation
-as the factor that was omitted.
+as the factor that was omitted. A graph that demonstrates why it's essential to
+correct for both the spectra bandwidth warping and time dilation is presented
+in Figure \ref{fit:k-example}.
 
-In 1935, the correction of $(1 + z)^2$ empirically lined up the data so that
-there seemed to be a linear relationship between redshift and distance. It
-wasn't until \citet{riess1998}, sixty-eight years later, that the omission of a
-third $(1 + z)$ correction factor resulted in faulty conclusions.
+\begin{figure}[h]
+  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
+  \caption{An example of how k-corrections take an observed spectrum and
+  produce a rest-frame spectrum. [TODO]
+  }
+  \label{fig:k-example}
+\end{figure}
 
-Those faulty conclusions, however, have been the basis for a substantial amount
-of scientific interest. In 2011, three physicists received the Nobel Prize in
-Physics for discovering that the expansion rate of the universe is accelerating
-\citet{straumann2012}. The papers \citet{riess1998} and \citet{perlmutter1999}
-have each received over 20000 citations. It's not clear how much cosmology work
-will need to be revisited with corrected distance measurements, but it is a
-non-trivial amount.
+The modern treatment of k-corrections is based on the work of \citet{kim1996}.
 
-\begin{displayquote}
-\end{displayquote}
+\lstinputlisting[language=Python, caption=A demonstration that k-corrections
+calculated by snpy are off by \texttt{2.5*log10(1+z)}. The roundoff error is
+roughly \texttt{2e-16}.]{code_listing.py}
 
 \section{The dimming effects of redshift}
+\label{sec:redshift}
 
@@
 \section{Correcting magnitude for time dilation}
+\label{sec:correction}
 
@@
 \section{Linear distance vs redshift relationship}
+\label{hubblelaw}
 
@@
 \begin{figure}[ht]
-  \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
-  \caption{The relationship between distance and redshift for two treatments of
-  magnitude data. The displayed points are roughly a third of the values in the
-  full DES dataset, selected evenly to aid visibility. The $k(z) = 1$ treatment
-  is clearly non-linear while the $k(z) = 1 + z$ treatment appears to be
-  linear.}
-  \label{fig:mu_distance_vs_redshift}
-\end{figure}
-
-\begin{figure}[ht]
-  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
-  \caption{An example of how k-corrections take an observed spectrum and
-  produce a rest-frame spectrum. [TODO]
-  }
-\end{figure}
-
-\begin{figure}[ht]
   \includegraphics[width=\linewidth]{velocity_vs_distance.png}
@@
 \end{figure}
+
+\section{Hubble tension}
+\label{sec:tension}
 
@@
 
-\section{Disagreement with existing research}
-
 Previous studies use $F$ instead of $F*$. To the best of our knowledge, no

### 2024-12-26 paper/code_listing.py

@@ -1,0 +1,35 @@
+import snpy
+import numpy
+
+# Use an arbitrary epoch for the spectral energy density template.
+wave, flux = snpy.kcorr.get_SED(day=9)
+
+# Use an arbitrary redshift.
+z = 0.5
+
+# Use the B and R filters from the Lick telescope as examples.
+rest_filter = snpy.fset["Bkait"]
+obs_filter = snpy.fset["Rkait"]
+
+# Compute the desired rest magnitude.
+m_b = rest_filter.synth_mag(wave, flux)
+
+# Compute the observed magnitude after redshift effects.
+m_r = obs_filter.synth_mag(wave, flux, z=z)
+
+got_k = snpy.kcorr.K(wave, flux, rest_filter, obs_filter, z=z)[0]
+
+# From the definition of k-corrections:
+want_k = m_r - m_b
+
+def print_results():
+  """
+  >>> print_results()
+  got_k (-0.679138363247608) != want_k (-1.1193665108868114)
+  2.5*log10(1+z) == 0.4402281476392031
+  got_k - 2.5*log10(1+z) (-1.1193665108868112) == want_k (-1.1193665108868114)
+  """
+  print(f"got_k ({got_k}) != want_k ({want_k})")
+  print(f"2.5*log10(1+z) == {2.5 * numpy.log10(1+z)}")
+  fixed = got_k - 2.5*numpy.log10(1+z)
+  print(f"got_k - 2.5*log10(1+z) ({fixed}) == want_k ({want_k})")

### 2024-12-26 src/redshift/supernova.py
Done for the night

@@ -53,7 +53,7 @@ class Supernova:
             return self.magnitude
         elif correction == Correction.TWO:
             return self.magnitude - 2 * np.log(1 + self.z) / np.log(100**0.2)
-        else:  # Tired light
+        else:
             return self.magnitude - np.log(1 + self.z) / np.log(100**0.2)
 
     @property

### 2024-12-26 paper/paper.tex

@@
 to another filter. In order to observe a SnIa in an arbitrary filter and report
-the magnitude in filter B, we use a technique called k-corrections.
+the magnitude in the B filter we use a technique called k-corrections.
 
@@
 but in \citet{hubble1935} the descrepancy was noted and ignored.
-\citet{oke1968} rederived k-corrections, but they failed to account time
+\citet{oke1968} rederived k-corrections, but they failed to account for time
 dilation, one of the other dimming effects of redshift. In \citet{kim1996},
@@
 
-A few years later, \citet{desitter1934}, discussed all three issues that would
-reduce the observed magnitude of a distant observation. The correction for each
-of these issues is identical: take a measurement for luminosity and multiply it
-by the factor $1 + z$.
+A few years later, \citet{desitter1934}, discussed all three issues that reduce
+the observed magnitude of a distant observation. The correction for each of
+these issues is identical: take a measurement for luminosity and multiply it by
+the factor $1 + z$.
 
@@
   \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
-  \caption{An example of how k-corrections take an observed spectrum and
-  produce a rest-frame spectrum. [TODO]
+  \caption{An example of how k-corrections take an observed magnitude and
+  produce a rest frame magnitude. In this example, $z=1$. The observation
+  filter measures magnitude, which is equivalent to measuring the number of
+  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
+  applied which doubles the photons per nanometer. The top right panel shows
+  the effect of correcting for the bandwidth spectrum warping effect --
+  correcting all wavelengths for the rest frame means that the measured
+  wavelengths have blueshifted, ideally into the cross band B filter. Applying
+  both effects, shown in the bottom right panel, requires applying two
+  correction factors of $1+z$. This example omits the correction for a similar
+  effect related to lower energy due to the Planck relation because CCD cameras
+  obviate the need to correct for this effect.
   }
@@
 The modern treatment of k-corrections is based on the work of \citet{kim1996}.
+This work extended the calculations of k-corrections to extend to filters
+beyond B and V. It also introduced a term that deals with the zero-point for the
+actual filters. Equation 2 from this paper is the form of the k-corrections
+used in the modern day:
 
+\begin{equation}
+  K_{xy} = -2.5\text{log} \left(\frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}{\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) + 2.5\text{log}(1+z) + 2.5\text{log}\left(\frac{F(\lambda)S_x(\lambda)d\lambda}{F(1/(1+z))S_y(\lambda))d\lambda}\right).
+\end{equation}
+
+The first term of this equation deals with zero-points, which is a magnitude
+added to individual filters to correct for the light gathering abilities of the
+telescope. The third term measures the flux in the observation filter and divides it by  the flux that would be measured
+
+The next major advance in k-corrections was
+
+\citet{snpy}
+
+\begin{minipage}[c]{0.95\textwidth}
 \lstinputlisting[language=Python, caption=A demonstration that k-corrections
@@
 roughly \texttt{2e-16}.]{code_listing.py}
+\end{minipage}
 

### 2024-12-27 paper/paper.tex
Halfway through the derivation...
... but it's past the kiddo's bed time.

@@
 to another filter. In order to observe a SnIa in an arbitrary filter and report
-the magnitude in the B filter we use a technique called k-corrections.
+the magnitude in the B filter we use a technique called K-corrections.
 
-The first formal derivation of k-corrections was performed by
-\citet{tollman1930}, and it failed to account for bandwidth stretching, one of
+The first formal derivation of K-corrections was performed by
+\citet{tolman1930}, and it failed to account for bandwidth stretching, one of
 the dimming effects of redshift. This error was noted by \citet{desitter1934},
 but in \citet{hubble1935} the descrepancy was noted and ignored.
-\citet{oke1968} rederived k-corrections, but they failed to account for time
+\citet{oke1968} rederived K-corrections, but they failed to account for time
 dilation, one of the other dimming effects of redshift. In \citet{kim1996},
-k-corrections were extended to handle additional cross-filter comparisons and
+K-corrections were extended to handle additional cross-filter comparisons and
 address zero-point corrections, but they started their derivation by
@@
 package Sn(OO)py which implemented the SnIa template spectra into
-k-corrections. This software package computes k-corrections differently from
+K-corrections. This software package computes K-corrections differently from
 prior work, and in order to match prior values, the code adds an extra term.
@@
 graph. We will show in Section \ref{sec:correction} that correcting the flaw
-with k-corrections leads to a linear graph that does not need to rely on a
+with K-corrections leads to a linear graph that does not need to rely on a
 cosmological constant.
@@
 was incompatable with the Hubble constant measured from SnIa. As we will
-discuss in Section \ref{sec:tension}, fixing the error with k-corrections
+discuss in Section \ref{sec:tension}, fixing the error with K-corrections
 produces a measurement of the Hubble constant that is compatible with models
@@
 
-\section{A brief history of k-corrections}
+\section{A brief history of K-corrections}
 \label{sec:history}
@@
 aspect of the process that we will explore here concerns how redshift affects
-the light we observe. This problem is often referred to as k-corrections, and
+the light we observe. This problem is often referred to as K-corrections, and
 one of the first mathematical treatments of the problem was performed by
@@
 A year later, \citet{hubble1935} published a similar set of calculations for
-k-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
+K-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
 correction term used by de Sitter. They started their derivation by copying the
@@
 
-The Hubble k-corrections with the incorrect correction term have been used ever
+The Hubble K-corrections with the incorrect correction term have been used ever
 since.
@@
 correct for both the spectra bandwidth warping and time dilation is presented
-in Figure \ref{fit:k-example}.
+in Figure \ref{fig:k-example}.
 
 \begin{figure}[h]
-  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
-  \caption{An example of how k-corrections take an observed magnitude and
+  \includegraphics[width=\linewidth]{K-corrections_for_photon_counts.png}
+  \caption{An example of how K-corrections take an observed magnitude and
   produce a rest frame magnitude. In this example, $z=1$. The observation
@@
 
-The modern treatment of k-corrections is based on the work of \citet{kim1996}.
-This work extended the calculations of k-corrections to extend to filters
+The modern treatment of K-corrections is based on the work of \citet{kim1996}.
+This work extended the calculations of K-corrections to extend to filters
 beyond B and V. It also introduced a term that deals with the zero-point for the
-actual filters. Equation 2 from this paper is the form of the k-corrections
+actual filters. Equation 2 from this paper is the form of the K-corrections
 used in the modern day:
@@
 \begin{equation}
-  K_{xy} = -2.5\text{log} \left(\frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}{\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) + 2.5\text{log}(1+z) + 2.5\text{log}\left(\frac{F(\lambda)S_x(\lambda)d\lambda}{F(1/(1+z))S_y(\lambda))d\lambda}\right).
+\label{eq:kim2}
+  K_{xy} =
+    -2.5\text{log} \left(
+      \frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
+           {\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
+    + 2.5\text{log}(1+z)
+    + 2.5\text{log}\left(
+      \frac{\int F(\lambda)S_x(\lambda)d\lambda}
+           {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
 \end{equation}
 
-The first term of this equation deals with zero-points, which is a magnitude
-added to individual filters to correct for the light gathering abilities of the
-telescope. The third term measures the flux in the observation filter and divides it by  the flux that would be measured
+This equation has two problems with it, which we will explore in Section
+\ref{sec:derivation}.
 
-The next major advance in k-corrections was
+\section{Derivation of K-corrections}
+\label{sec:derivation}
+
+The definition of K-corrections is
+
+\begin{equation}
+\begin{aligned}
+\label{eq:definition}
+  m_x &= M_x + \mu + K_{xy} \\
+      &= M_x + m_y - M_y + K_{xy} \\
+      &= m_y + K_{xy}.
+\end{aligned}
+\end{equation}
+
+The second line of Equation \ref{eq:definition} expands the distance modulus
+$\mu$ using $\mu = m = M$ where $m$ is the observed magnitude and $M$ is the
+absolute magnitude. Since the absolute magnitude is an intrinsic property of a
+stellar object, we can use $M = M_x = M_y$, so the absolute magnitude terms
+cancel out in the third line.
+
+We will also need to use the flux to magnitude formula:
+
+\begin{equation}
+\begin{aligned}
+\label{eq:flux2mag}
+  m_x &= -2.5 \text{log}(\mathcal{F}_x) + C_x \\
+      &= -2.5 \text{log}(C'_x \mathcal{F}_x) .
+\end{aligned}
+\end{equation}
+
+Here, $C_x$ represents the zero-point for the filter $x$ on some particular
+telescope. In order to use consistend magnitude values across different
+telescopes that have different light gathering powers, we take the measured
+magnitude and multiply it by the ratio of the flux rate for the standard
+telescope and filter to the flux rate for this particular telescope and
+filter.
+
+Since the K-correction is a magnitude value, we can define
+
+\begin{equation}
+K_x = -2.5\text{log}(k_x C_x)
+\end{equation}
+
+and use Equation \ref{eq:flux2mag} to recombine the flux term $\mathcal{F}_y$
+with $m_y$ from Equation \ref{eq:definition}. This gives
+
+\begin{equation}
+\begin{aligned}
+            m_x &= -2.5 \text{log}(\mathcal{F}_y) + K_{xy} \\
+                &= -2.5 \left( \text{log}(\mathcal{F}_y) + \text{log}(k_x C_x) \right) \\
+                &= -2.5 \text{log}(\mathcal{F}_y \times k_{xy} \times C_x) \\
+  \mathcal{F}_x &= \mathcal{F}_y \times k_{xy} \times C_x .
+\end{aligned}
+\end{equation}
+
+The work up to this point has been to translate the K-corrections equation from
+a magnitude problem to a flux problem. This has intuitive benefits, at least
+for the authors. The goal is to make $k_{xy}$ equal the ratio of the flux rate
+that we want in filter $x$ to the flux rate that we observe in filter $y$.
+
+The first term of this equation deals with zero-points $C$, which is a
+magnitude added to individual filters to correct for the light gathering
+abilities of the filter together with the telescope. We are converting the
+magnitude from the $y$ filter to the $x$ filter by using $m_x = m_y - k_{xy}$,
+so $k_{xy}$ needs to include $C_y - C_x$.
+
+The numerator of the third term, $\int F(\lambda)S_x(\lambda)d\lambda$,
+measures what the flux would be if there was no redshift in the target filter.
+The denominator $\int F(\lambda/(1+z))S_y(\lambda))d\lambda$ takes the
+observation filter's sensitivity $S_y(\lambda)$ at each wavelength $\lambda$
+and multiples it by the rest frame spectral energy density $F(\lambda/(1+z))$
+that corresponds to the blueshifted wavelength $\lambda / (1+z)$.
+
+The effect of
+multiplying the filter sensitivity $S(\lambda)$ by the blueshifted spectral energy density $F(\lambda / (1+z))$ is the same as if we created a new
+spectral energy density $F'(\lambda) = F(\lambda / (1+z))$. The key thing to
+notice with $F'$ is that it artificially inflates the total amount of flux by a
+factor of $1 + z$. That is,
+
+\begin{equation}
+(1+z) \times \int_{a}^{b} S(\lambda) d\lambda = \int_{a(1+z)}^{b(1+z)} S'(\lambda) d\lambda .
+\end{equation}
+
+In order to discuss flux instead of magnitude, we can rewrite Equation \ref{eq:kim2} as
+
+\begin{equation}
+\begin{aligned}
+\label{eq:kim_flux}
+  K_{xy} &= -2.5 \text{log}(\mathcal{F}) + C_x - C_y \\
+         &= -2.5 \text{log}\left(
+              \frac{(1+z) \int F(\lambda)S_x(\lambda)d\lambda}
+                   {\int F(1/(1+z))S_y(\lambda))d\lambda}\right) + C_x - C_y \\
+  \mathcal{R} &= (1+z) \times \frac{\int F(\lambda)S_x(\lambda)d\lambda}
+                                   {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}
+\end{aligned}
+\end{equation}
+
+where $C_x$ and $C_y$ represent the zero-point magnitudes for the target filter
+and the observation filter respectively.
+
+at a
+blueshifted wavelength given by $F(\lambda / (1+z))$. In other words, it calculates what the observation filter would measure if it was blue shifted.
+
+if the observation filter were blueshifted, similar to the top-right panel of Figure \ref{fig:k-example}, the denominator
+
+the flux that would be measured
+
+The next major advance in K-corrections was
 
@@
 \begin{minipage}[c]{0.95\textwidth}
-\lstinputlisting[language=Python, caption=A demonstration that k-corrections
+\lstinputlisting[language=Python, caption=A demonstration that K-corrections
 calculated by snpy are off by \texttt{2.5*log10(1+z)}. The roundoff error is

### 2024-12-28 paper/paper.tex

@@
 
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{K-corrections_for_photon_counts.png}
+\begin{figure}[H]
+  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
   \caption{An example of how K-corrections take an observed magnitude and
@@
 This work extended the calculations of K-corrections to extend to filters
-beyond B and V. It also introduced a term that deals with the zero-point for the
-actual filters. Equation 2 from this paper is the form of the K-corrections
-used in the modern day:
+beyond B and V. It also introduced a term that deals with the zero-point for
+the actual filters. In the modern day, filters measure the photon flux as
+upposed to the energy flux. Historically, bolometric devices would measure the
+energy flux, but modern CCD cameras effectively measure the photon flux.
+
+Quoting \citet{kim1996}:
+
+\begin{quote}
+  Therefore, the correct K correction caluculation to be used with measured
+  photometric magnitudes is the integral photon counts:
 
   \begin{equation}
-\label{eq:kim2}
+  \label{eq:kim}
     K_{xy} =
       -2.5\text{log} \left(
-      \frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
-           {\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
+        \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
+             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
       + 2.5\text{log}(1+z)
       + 2.5\text{log}\left(
-      \frac{\int F(\lambda)S_x(\lambda)d\lambda}
-           {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
+        \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
+             {\int \lambda F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
   \end{equation}
+\end{quote}
 
-This equation has two problems with it, which we will explore in Section
-\ref{sec:derivation}.
+This equation has three errors, which we will explore in Section
+\ref{sec:consequences}.
 
@@
 
-The definition of K-corrections is
+With modern CCD cameras, a telescope observaion consists of a single value
+$\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
+second. A summary of how this works is provided by \citet{lesser2015}. The
+measured energy is produced by electrons not photons, so the measured number is
+proportional to the number of photons. However, we need to calculate the
+expected number of photons collected by using a spectral energy density
+function $F$. The value $F(\lambda)$ gives the amount of energy collected by a
+bolometric device for the wavelength $\lambda$.
+
+To convert the spectral energy density $F$ to the photon density $F'$, we need
+to use the Plank relation $E = \frac{hc}{\lambda}$ where $E$ is the energy, $h$
+is Planck's constant, and $c$ is the speed of light. This gives us
+
+\begin{equation}
+\begin{aligned}
+   F(\lambda) &= F'(\lambda) \times \frac{hc}{\lambda} \\
+  F'(\lambda) &= \frac{\lambda F(\lambda)}{hc}.
+\end{aligned}
+\end{equation}
+
+It's important to note that for the blueshifted wavelength $\lambda / (1+z)$,
+this equation produces
+
+\begin{equation}
+ F'\left(\frac{\lambda}{1+z}\right) = \frac{\left(\frac{\lambda}{1 + z}\right) F\left(\frac{\lambda}{1+z}\right)}{hc}.
+\end{equation}
+
+However, this equation is misleading and error prone. We will want to use it to
+help calculate the amount of flux in an observation filter at the redshifted
+wavelength $\lambda \times (1 + z)$. In other words, we want to produce the
+photon density function $R'$ that is the redshifted version of $F'$.
+Redshifting does two things:
+
+\begin{itemize}
+  \item The stretching of space increases the distance between photons while
+  they are traveling. This phenomenon appears to an observer like time
+  dilation, although cosmological time dilation is due to a different mechanism
+  than relativistic time dilation. This effect reduces the photon arrival rate
+  by a factor of $1/(1+z)$.
+
+  In order to account for cosmological time dilation, we will need to multiply
+  $F'$ by $1/(1+z)$.
+
+  \item All wavelengths are changed by a factor of $1 + z$. When we integrate
+  $R'$ from wavelength $\lambda_a$ to wavelength $\lambda_b$, the values
+  correspond to the wavelengths $\lambda_a / (1+z)$ to $\lambda_b / (1+z)$ in
+  $F'$. We will integrate over a width of $\lambda_b - \lambda_a$, but
+  $F'(\lambda / (1+z))$ will refer to values in a width of
+  $(\lambda_b - \lambda_a) / (1+z)$.
+
+  In order to account for this bandwidth spectral warping effect, we will need
+  to multiply $F'$ by a second factor of $1/(1+z)$.
+\end{itemize}
+
+Combining these two phenomena together, we can calculated the redshifted
+spectral energy density $R$ using
+
+\begin{equation}
+\begin{aligned}
+\label{eq:redshifted_density}
+  R'(\lambda) &= F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} \\
+  R(\lambda) &= \frac{F(\lambda / (1+z))}{(1+z)hc} \times \frac{1}{(1 + z)^2} .
+\end{aligned}
+\end{equation}
+
+In order to calculate the amount of flux $\mathcal{F}_x$ measured in filter
+$x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
+sensity $S_x(\lambda)$, which represents the proportion of photons filter $x$
+will measure at wavelength $\lambda$. We then need to sum over all wavelengths,
+which is expressed with the equation
+
+\begin{equation}
+\begin{aligned}
+\label{eq:flux_definition}
+  \mathcal{F}_x &= \int F'(\lambda) S_x(\lambda) d\lambda \\
+                &= \int \lambda F(\lambda) S_x(\lambda) d\lambda.
+\end{aligned}
+\end{equation}
+
+The limits of integration are techinically from 0 to $\infty$, but these are
+usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
+outside of a filter's bandpass.
+
+We will also use the energy flux $\mathcal{F}$ to magnitude $m$ formula:
+
+\begin{equation}
+\begin{aligned}
+\label{eq:flux2mag}
+                             m_x &= -2.5 \text{log}(\mathcal{F}_x) + P_x \\
+  -2.5 \text{log}(\mathcal{F}_x) &= m_x - P_x .
+\end{aligned}
+\end{equation}
+
+$P_x$ represents the zero-point for the filter $x$ on some particular
+telescope. In order to use consistant magnitude values across telescopes that
+have different light gathering abilities, we take the measured magnitude and
+multiply it by the ratio of the standard flux rate to the flux rate for this
+particular telescope and filter. For convenience, we use $P_x = -2.5
+\text{log}(P'_x)$ so that we can work with flux instead of with magnitude.
+
+Now that we have the identities in Equations \ref{eq:flux_definition} and
+\ref{eq:flux2mag} we will change directions and look at the definition of
+K-corrections $K_{xy}$. This value allows us to make an observation in filter
+$y$ and report what the magnitude would have been in filter $x$ if no redshift
+occured:
 
@@
 \label{eq:definition}
-  m_x &= M_x + \mu + K_{xy} \\
-      &= M_x + m_y - M_y + K_{xy} \\
-      &= m_y + K_{xy}.
+  m_y &= M_x + \mu + K_{xy} \\
+      &= M_x + m_x - M_x + K_{xy} \\
+      &= m_x + K_{xy} \\
+  m_x &= m_y - K_{xy} .
 \end{aligned}
@@
 The second line of Equation \ref{eq:definition} expands the distance modulus
-$\mu$ using $\mu = m = M$ where $m$ is the observed magnitude and $M$ is the
-absolute magnitude. Since the absolute magnitude is an intrinsic property of a
-stellar object, we can use $M = M_x = M_y$, so the absolute magnitude terms
-cancel out in the third line.
+$\mu$ using $\mu = m - M$ where $m$ is the observed magnitude and $M$ is the
+absolute magnitude.
 
-We will also need to use the flux to magnitude formula:
+Since the K-correction is a magnitude value and we wish to work on flux values,
+it is convenient to define the following substitution:
+
+\begin{equation}
+\label{eq:k_substitution}
+  K_{xy} = 2.5\text{log}(K'_{xy}) .
+\end{equation}
+
+Note that this substitution omits the minus ($-$) sign.
+
+Starting with Equation \ref{eq:flux2mag} and then
+recombining the flux term $\mathcal{F}_y$ with $m_y$ from Equation
+\ref{eq:definition}, we have
 
@@
 \begin{aligned}
-\label{eq:flux2mag}
-  m_x &= -2.5 \text{log}(\mathcal{F}_x) + C_x \\
-      &= -2.5 \text{log}(C'_x \mathcal{F}_x) .
+\label{eq:as_flux}
+  -2.5 \text{log}(\mathcal{F}_x)
+      &= m_x - P_x \\
+      &= m_y - K_{xy} - P_x \\
+      &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
+      &= -2.5 \text{log}(\mathcal{F}_y)
+         - 2.5 \text{log}(P'_y)
+         - 2.5 \text{log}(K'_{xy})
+         + 2.5 \text{log}(P_x) \\
+      &= -2.5 \left(
+         \text{log}(\mathcal{F}_y)
+         + \text{log}(K'_{xy})
+         + \text{log}(P'_y)
+         - \text{log}(P'_x)
+        \right) \\
+      &= -2.5 \text{log}\left(
+        \mathcal{F}_y
+        \times K'_{xy}
+        \times \frac{P'_y}{P'_x}\right) \\
+  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x}.
 \end{aligned}
@@
 
-Here, $C_x$ represents the zero-point for the filter $x$ on some particular
-telescope. In order to use consistend magnitude values across different
-telescopes that have different light gathering powers, we take the measured
-magnitude and multiply it by the ratio of the flux rate for the standard
-telescope and filter to the flux rate for this particular telescope and
-filter.
-
-Since the K-correction is a magnitude value, we can define
+It's useful to inspect this equation to consider whether the term
+$\frac{P'_y}{P'_x}$ is correct, or if it might be flipped to the inverse of
+what it should be. However, if we rewrite Equation \ref{eq:as_flux} as
 
 \begin{equation}
-K_x = -2.5\text{log}(k_x C_x)
+  \mathcal{F}_x \times P'_x = \mathcal{F}_y \times P'_y \times K'_{xy}
 \end{equation}
 
-and use Equation \ref{eq:flux2mag} to recombine the flux term $\mathcal{F}_y$
-with $m_y$ from Equation \ref{eq:definition}. This gives
+then the meaning is a bit more clear. The left hand side
+$\mathcal{F}_x \times P'_x$ is the rate of photon collection for an idealized
+telescope in filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon
+collection for an idealized telescope in filter $y$. We are able to observe the
+value $\mathcal{F}_y \times P'_y$ and want to use the fudge factor $K'_{xy}$ to
+produce the value $\mathcal{F}_x \times P'_x$.
+
+We can isolate $K'_{xy}$ and then use Equation \ref{eq:flux_definition} to expand
 
@@
 \begin{aligned}
-            m_x &= -2.5 \text{log}(\mathcal{F}_y) + K_{xy} \\
-                &= -2.5 \left( \text{log}(\mathcal{F}_y) + \text{log}(k_x C_x) \right) \\
-                &= -2.5 \text{log}(\mathcal{F}_y \times k_{xy} \times C_x) \\
-  \mathcal{F}_x &= \mathcal{F}_y \times k_{xy} \times C_x .
+  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x} \\
+        K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} .
 \end{aligned}
@@
 
-The work up to this point has been to translate the K-corrections equation from
-a magnitude problem to a flux problem. This has intuitive benefits, at least
-for the authors. The goal is to make $k_{xy}$ equal the ratio of the flux rate
-that we want in filter $x$ to the flux rate that we observe in filter $y$.
-
-The first term of this equation deals with zero-points $C$, which is a
-magnitude added to individual filters to correct for the light gathering
-abilities of the filter together with the telescope. We are converting the
-magnitude from the $y$ filter to the $x$ filter by using $m_x = m_y - k_{xy}$,
-so $k_{xy}$ needs to include $C_y - C_x$.
-
-The numerator of the third term, $\int F(\lambda)S_x(\lambda)d\lambda$,
-measures what the flux would be if there was no redshift in the target filter.
-The denominator $\int F(\lambda/(1+z))S_y(\lambda))d\lambda$ takes the
-observation filter's sensitivity $S_y(\lambda)$ at each wavelength $\lambda$
-and multiples it by the rest frame spectral energy density $F(\lambda/(1+z))$
-that corresponds to the blueshifted wavelength $\lambda / (1+z)$.
-
-The effect of
-multiplying the filter sensitivity $S(\lambda)$ by the blueshifted spectral energy density $F(\lambda / (1+z))$ is the same as if we created a new
-spectral energy density $F'(\lambda) = F(\lambda / (1+z))$. The key thing to
-notice with $F'$ is that it artificially inflates the total amount of flux by a
-factor of $1 + z$. That is,
-
-\begin{equation}
-(1+z) \times \int_{a}^{b} S(\lambda) d\lambda = \int_{a(1+z)}^{b(1+z)} S'(\lambda) d\lambda .
-\end{equation}
-
-In order to discuss flux instead of magnitude, we can rewrite Equation \ref{eq:kim2} as
+Now we use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
+to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
+spectral energy density function $F$. Note that $\mathcal{F}_x$ uses the rest
+frame spectral energy density $F$ while $\mathcal{F}_y$ uses the redshifted
+spectral energy density $R(\lambda)$:
 
@@
 \begin{aligned}
-\label{eq:kim_flux}
-  K_{xy} &= -2.5 \text{log}(\mathcal{F}) + C_x - C_y \\
-         &= -2.5 \text{log}\left(
-              \frac{(1+z) \int F(\lambda)S_x(\lambda)d\lambda}
-                   {\int F(1/(1+z))S_y(\lambda))d\lambda}\right) + C_x - C_y \\
-  \mathcal{R} &= (1+z) \times \frac{\int F(\lambda)S_x(\lambda)d\lambda}
-                                   {\int F(\lambda/(1+z))S_y(\lambda))d\lambda}
+  K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} \\
+         &= \frac{P'_x \int F'(\lambda) S_x d\lambda}
+                 {P'_y \int R'(\lambda) S_y d\lambda} \\
+         &= \frac{P'_x}{P'_y} \times
+              \frac{\int F'(\lambda) S_x d\lambda}
+                   {\int F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} d\lambda} \\
+         &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
+              \frac{\int \frac{\lambda F(\lambda)}{hc} S_x d\lambda}
+                   {\int \frac{F(\lambda / (1+z))}{(1+z)hc} S_y d\lambda} \\
+         &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} .
 \end{aligned}
@@
 
-where $C_x$ and $C_y$ represent the zero-point magnitudes for the target filter
-and the observation filter respectively.
+Finally, we can use Equation \ref{eq:k_substitution} to convert the flux $K'_{xy}$ back
+into the magnitude $K_{xy}$:
 
-at a
-blueshifted wavelength given by $F(\lambda / (1+z))$. In other words, it calculates what the observation filter would measure if it was blue shifted.
+\begin{equation}
+\begin{aligned}
+\label{eq:K2k}
+  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
+         &= 2.5\text{log}\left(
+            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
+            \frac{\int \lambda F(\lambda) S_x d\lambda}
+                 {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}\right) \\
+         &= 2.5 \left(
+            \text{log} \left( \frac{P'_x}{P'_y} \right)
+            + \text{log}( {(1 + z)^2})
+            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}
+            \right) \right) \\
+         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
+            + 5 \text{log} (1 + z)
+            + 2.5 \text{log} \left(
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) \\
+         &= 5 \text{log} (1 + z)
+            + 2.5 \text{log} \left(
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+            - P_x + P_y .
+\end{aligned}
+\end{equation}
 
-if the observation filter were blueshifted, similar to the top-right panel of Figure \ref{fig:k-example}, the denominator
+\section{Consequences}
+\label{sec:consequences}
 
-the flux that would be measured
+In order to fully compare our derivation against Equation \ref{eq:kim}, we need
+to use the identity
 
-The next major advance in K-corrections was
+\begin{equation}
+  P = -2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+\end{equation}
 
-\citet{snpy}
+where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an idealized
+spectral energy distribution at $z = 0$ for which $U = B = V = R = I = 0$ in
+the photometric system being used." Combining this with Equation \ref{eq:K2k}, we have
+
+\begin{equation}
+\begin{aligned}
+  K_{xy} &= 5 \text{log} (1 + z)
+            + 2.5 \text{log} \left(
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+            - P_x + P_y \\
+         &= 5 \text{log} (1 + z)
+            + 2.5 \text{log} \left(
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+            + 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+            - 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
+         &= 2.5 \text{log} \left(
+              \frac{\int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
+                   {\int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
+             \right)
+            + 5 \text{log} (1 + z)
+            + 2.5 \text{log} \left(
+              \frac{\int \lambda F(\lambda) S_x d\lambda}
+                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) .
+\end{aligned}
+\end{equation}
 

### 2024-12-28 paper/paper.tex

@@
 % keywords can be removed
-\keywords{Cosmological Parameters \and Dark Energy \and Luminosity Distance \and Hubble tension}
+\keywords{Cosmological Parameters \and K-corrections \and Dark Energy \and Luminosity Distance \and Hubble tension}
 
@@
 bright the SnIa would be if its light didn't undergo redshift. Redshift causes
-the light that would be mesaured by the B filter in a rest frame to be shifted
+the light that would be measured by the B filter in a rest frame to be shifted
 to another filter. In order to observe a SnIa in an arbitrary filter and report
@@
 the dimming effects of redshift. This error was noted by \citet{desitter1934},
-but in \citet{hubble1935} the descrepancy was noted and ignored.
+but in \citet{hubble1935} the discrepancy was noted and ignored.
 \citet{oke1968} rederived K-corrections, but they failed to account for time
@@
 The effect of using an incorrect magnitude for SnIa is that we think objects
-are farther away than they really are, and the effect componds for greater
+are farther away than they really are, and the effect compounds for greater
 distances. Up until \citet{riess1998}, we didn't have distant enough
@@
 constant, but as summarized in \citet{perivolaropoulos2022}, this measurement
-was incompatable with the Hubble constant measured from SnIa. As we will
+was incompatible with the Hubble constant measured from SnIa. As we will
 discuss in Section \ref{sec:tension}, fixing the error with K-corrections
@@
 at a known distance, we can estimate the distance to any match by measuring the
-appearant brightness before applying some geometry.
+apparent brightness before applying some geometry.
 
-Measuring the apperant brightness of a Type Ia supernova is non-trivial. The
+Measuring the apparent brightness of a Type Ia supernova is non-trivial. The
 aspect of the process that we will explore here concerns how redshift affects
@@
 the actual filters. In the modern day, filters measure the photon flux as
-upposed to the energy flux. Historically, bolometric devices would measure the
+opposed to the energy flux. Historically, bolometric devices would measure the
 energy flux, but modern CCD cameras effectively measure the photon flux.
@@
 \begin{quote}
-  Therefore, the correct K correction caluculation to be used with measured
+  Therefore, the correct K correction calculation to be used with measured
   photometric magnitudes is the integral photon counts:
@@
 
-With modern CCD cameras, a telescope observaion consists of a single value
+With modern CCD cameras, a telescope observation consists of a single value
 $\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
@@
 $x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
-sensity $S_x(\lambda)$, which represents the proportion of photons filter $x$
+sensitivity $S_x(\lambda)$, which represents the proportion of photons filter $x$
 will measure at wavelength $\lambda$. We then need to sum over all wavelengths,
@@
 
-The limits of integration are techinically from 0 to $\infty$, but these are
+The limits of integration are technically from 0 to $\infty$, but these are
 usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
@@
 $P_x$ represents the zero-point for the filter $x$ on some particular
-telescope. In order to use consistant magnitude values across telescopes that
+telescope. In order to use consistent magnitude values across telescopes that
 have different light gathering abilities, we take the measured magnitude and
@@
 \begin{equation}
-  P = -2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+  P = -2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
 \end{equation}
@@
                    {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
-            + 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
-            - 2.5 \text{log} \left( \int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
+            + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+            - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
          &= 2.5 \text{log} \left(
-              \frac{\int \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
-                   {\int \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
+              \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
+                   {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
              \right)
@@
 
-\begin{minipage}[c]{0.95\textwidth}
-\lstinputlisting[language=Python, caption=A demonstration that K-corrections
-calculated by snpy are off by \texttt{2.5*log10(1+z)}. The roundoff error is
-roughly \texttt{2e-16}.]{code_listing.py}
-\end{minipage}
+Three differences with Equation \ref{eq:kim} stand out:
 
-\section{The dimming effects of redshift}
-\label{sec:redshift}
+\begin{itemize}
+  \item The sign is different for the first term. This will have a subtle but
+  frustrating effect for real values. Typically the zero-point values are
+  similar, so this term is close to 0. However, the term isn't always zero. As
+  we observe more distant supernovae, it is useful to switch our observational
+  filter to a filter that is sensitive to longer wavelengths. Each time we make
+  this switch we introduce a small but consistent bias.
 
-The magnitude measurements for Type Ia supernova goes through a long chain of
-data processing. The data used here was collected by the Dark Energy Survey
-Collaboration, as summarized in \citet{abbott2024} and described in more detail
-by \citet{vincenzi2024}. However, the data processing does not explicitly
-correct for either redshift or time dilation.
+  This effect by itself can alter estimates of $H_0$ by several km/s / Mpc.
+  While we present an estimate of the Hubble constant in Figure
+  \ref{fig:H0bootstrap}, we aren't terribly confident in the numbers because we
+  were unable to correct for the zero-point errors.
 
-In the big bang model, there are multiple phenomena associated with redshift that we
-might expect to reduce the apparent magnitude of a Type Ia supernova.
+  \item The second term is multiplied by a $2.5$ in \citet{kim1996} but is
+  multiplied by a $5$ here. This is the manifestation of the error in
+  \citet{tolman1930}.
 
-\subsection{Recessional velocity redshift}
+  \item In our derivation, the third term is has an extra $1 + z$ expression.
+  Based on an inspection of the SN(oo)py software package presented by
+  \citet{snpy}, this error is ignored and software package authors implement it
+  as the expression is intended, not precisely as the expression is written.
+\end{itemize}
 
-The energy carried by a photon is inversely proportional to wavelength, given
-by the Planck relation
+\section{Dark energy and the Hubble tension}
+\label{sec:tension}
 
-\begin{equation}
-  E = \frac{hc}{\lambda}
-\end{equation}
+As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
+are corrected by adding $-2.5\text{log}(1+z)$, there is a linear relationship
+between redshift and luminosity distance. This is in accordance with the
+Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there is no
+visual acceleration.
 
-where $E$ is energy, $h$ is the Planck constant, $c$ is the speed of light, and
-$\lambda$ is the wavelength.
+Since the corrected values are approximately linear, we can use them to
+estimate the Hubble constant $H0$. This is demonstrated in Figure
+\ref{fig:expansion}. Furthermore, we performed a bootstrap calculation to
+estimate the distribution of $H0$ estimates in Figure \ref{fig:H0bootstrap}.
 
-As redshift increases the wavelength of a photon, the energy decreases.
-
-The supernova data collected by the DES Collaboration used a CCD camera, a
-photon counting device, as described by \citet{flaugher2015}.  \citet{kim1996}
-noted that photometric measurements that depend on bolometers will need to be
-corrected for the reduced energy level of redshifted light, but with a photon
-counting device, this correction is not necessary.
-
-While the redshift phenomenon should impact the light detected from distant
-supernova, it should not impact the magnitude measurements so it does not need
-to be explicitly corrected.
-
-\subsection{Time dilation}
-
-The second phenomenon is that time dilation for objects moving quickly relative
-to our observational rest frame will reduce the rate at which photons are being
-emitted. Instead of changing the properties of individual photons, time
-dilation reduces the count of photons by a factor of $\frac{1}{1+z}$ where $z$
-is the redshift.
-
-This phenomenon will not be addressed by the nuances of any measuring device,
-so it must be explicitly corrected.
-
-\subsection{Stretching of space}
-
-If space itself is stretching, it will both increase the wavelength of photons
-and also reduce the density of those photons. If space is stretching at a
-constant rate, the effect would be indistinguishable from the redshift and time
-dilation created by high relative recessional velocities. However, an
-accelerating expansion of the universe may indicate a non-constant rate of
-stretching. This would manifest by distant objects having a greater distance
-per redshift than nearby objects.
-
-This non-linear streching-of-space model would be indistinguishable from a
-scenario where a constant force is pushing all objects away from each other.
-
-\subsection{Tired light}
-
-An alternative to the big bang theory is the tired light hypothesis, as
-described by \citet{zwicky1929} and \citet{shao2013}. The idea is that distant
-objects are mostly stationary relative to us, but the energy of light is lost
-as it travels through space. A feature of the tired light hypothesis is that
-since distant objects do not have a high relative velocity to us, they should
-not show time dilation.
-
-However, as shown by \citet{blondin2008} and \citet{white2024}, distant
-supernova do experience time dilation. Based on this, we can reject the tired
-light hypothesis and assume the big bang model.
-
-\section{Correcting magnitude for time dilation}
-\label{sec:correction}
-
-Luminosity distance $D_L$, is the apparent distance of an object based on the
-observed luminosity, also known as the flux $F$. This does not take into
-account any movement of the observed object between the time when the light was
-emitted and the light is observed.
-
-To derive the luminosity distance from these measurements, we start
-by computing the flux $F$. Magnitude $m$ is defined on a logarithmic scale
-where magnitude 1 has 100 times the brightness of magnitude 6, leading to
-
-\begin{equation}
-  F = \frac{1}{\sqrt[5]{100}^{m - 1}}.
-\end{equation}
-
-This is proportional to the number of photons detected by a telescope. We can
-find the corrected flux $F^*$ by multiplying by $k(z)$, the redshift correction
-factor. Time dilation of quickly moving objects reduces the number of photons
-by a factor of $\frac{1}{1 + z}$, so we have
-
-\begin{equation}
-\begin{aligned}
-  F^* &= F \times k(z) \\
-      &= F (1 + z).
-\end{aligned}
-\end{equation}
-
-To compute the corrected magnitude $m^*$, we can solve
-
-\begin{equation}
-\begin{aligned}
-   F^* &= \frac{1}{\sqrt[5]{100}^{m^* - 1}} \\
-   m^* &= m - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
-\end{aligned}
-\end{equation}
-
-From here, we can use the standard distance modules $\mu$ defined as
-
-\begin{equation}
-  \mu = m^* - M
-\end{equation}
-
-where $M$ is the absolute magnitude. The luminosity distance $D_L$ in parsecs
-can then be calculated as
-
-\begin{equation}
-  D_L = 10^{1 + \frac{\mu}{5}}.
-\end{equation}
-
-\section{Linear distance vs redshift relationship}
-\label{hubblelaw}
-
-The theory of an accelerating expansion is based on there being a non-linear
-relationship between redshift and distance. More specifically, old objects (the
-ones that are more distant) should have more distance per redshift than newer
-objects.
-
-As shown in Figure \ref{fig:mu_distance_vs_redshift}, this non-linear
-relationship is only observed when $k(z) = 1$, meaning that magnitude is not
-corrected for time dilation.
-
-In contrast, when $k(z) = 1 + z$, time dilation is accounted for and there is a
-linear relationship between redshift and distance. A linear model rules out an
-accelerated expansion.
+The value estimated here, $H0 \sim 65.94 \pm 1.29$ is highly suspicious because of the
+flipped zero-point corrections, but it is consistent with estimates of $H0$
+that are based on the CMB. \citet{planck2020} published the CMB value of $H0
+\sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It is interesting to
+note that if the DES observations are restricted to only those with $z < 0.1$,
+which presumably is a small enough redshift that the K-corrections will use the
+same filter for both the target and observation filter and thus the zero-point
+corrections will cancel out, gives the estimate $H0 \sim 67.8 \pm 1.86$.
 
@@
   }
+\label{fig:expansion}
 \end{figure}
-
-\section{Hubble tension}
-\label{sec:tension}
 
@@
   technique described by \citet{siegel1982}. The result of the bootstrap is $H0
-  \sim Norm(65.94, 1.29)$.
+  \sim Norm(65.94, 1.29^2)$.
   }
+\label{fig:H0bootstrap}
 \end{figure}
 
-Previous studies use $F$ instead of $F*$. To the best of our knowledge, no
-studies that depend on the distance of Type Ia supernova, reaching back at
-least to \citet{kim1996}, \citet{riess1998}, and \citet{perlmutter1999}, have
-accounted for time dilation.
+\section{Conclusions}
+
+A lot of data is going to have to be reanalyzed.
 

### 2024-12-28 paper/paper.tex

@@
   We show that the magnitude of distant objects has been calculated incorrectly
-  since 1930. We describe how this math error has propagated for over nine
-  decades. Finally, we explore the consequences of correcting this flaw and
+  since 1930. We describe how this math error in the formula for K-corrections
+  has propagated for over nine decades before re-deriving the K-corrections
+  equation. Finally, we explore the consequences of correcting this flaw and
   resolve two of the preeminent mysteries in cosmology: dark energy is not
@@
 \end{abstract}
-
-% keywords can be removed
-\keywords{Cosmological Parameters \and K-corrections \and Dark Energy \and Luminosity Distance \and Hubble tension}
 
@@
 the B filter \citet{riess1998} for the rest frame, meaning we want to know how
-bright the SnIa would be if its light didn't undergo redshift. Redshift causes
+bright the SnIa would be if its light did not undergo redshift. Redshift causes
 the light that would be measured by the B filter in a rest frame to be shifted
@@
 The first formal derivation of K-corrections was performed by
-\citet{tolman1930}, and it failed to account for bandwidth stretching, one of
+\citet{tolman1930} and it failed to account for bandwidth stretching, one of
 the dimming effects of redshift. This error was noted by \citet{desitter1934},
@@
 address zero-point corrections, but they started their derivation by
-referencing the incorrect equation from \citet{oke1968}. \citet{hsiao2007}
-expanded on the work done by \citet{kim1996} by providing expected SnIa
-template spectra. Finally, \citet{burns2010} implemented the popular software
-package Sn(OO)py which implemented the SnIa template spectra into
-K-corrections. This software package computes K-corrections differently from
-prior work, and in order to match prior values, the code adds an extra term.
+referencing the incorrect equation from \citet{oke1968}. The derivation in
+\citet{kim1996} forms the basis for modern implementations of K-corrections.
 This history is explored in more depth in Section \ref{sec:history}.
@@
 constant and dark energy in order to explain the non-linear distance-redshift
-graph. We will show in Section \ref{sec:correction} that correcting the flaw
+graph. We will show in Section \ref{sec:tension} that correcting the flaw
 with K-corrections leads to a linear graph that does not need to rely on a
@@
 our understanding of cosmology. This research used an alternative technique
-based on measurements of the cosmic microwave background to measure the Hubble
+based on measurements of the cosmic microwave background to compute the Hubble
 constant, but as summarized in \citet{perivolaropoulos2022}, this measurement
@@
 \begin{equation}
- F'\left(\frac{\lambda}{1+z}\right) = \frac{\left(\frac{\lambda}{1 + z}\right) F\left(\frac{\lambda}{1+z}\right)}{hc}.
+ F'\left(\frac{\lambda}{1+z}\right) = \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right).
 \end{equation}
@@
 \label{eq:redshifted_density}
-  R'(\lambda) &= F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} \\
-  R(\lambda) &= \frac{F(\lambda / (1+z))}{(1+z)hc} \times \frac{1}{(1 + z)^2} .
+  R'(\lambda) &= F'\left(\frac{\lambda}{1+z}\right) \times \frac{1}{(1 + z)^2} \\
+  R(\lambda) &= \frac{\lambda}{(1+z)hc} \times F\left(\frac{\lambda}{1+z}\right) \times \frac{1}{(1 + z)^2} .
 \end{aligned}
 \end{equation}
+
+We deliberately do not combine all of the factors of $1+z$ together because
+this form is more natural to implement in code.
 
@@
   K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} \\
-         &= \frac{P'_x \int F'(\lambda) S_x d\lambda}
-                 {P'_y \int R'(\lambda) S_y d\lambda} \\
+         &= \frac{P'_x \int F'(\lambda) S_x(\lambda) d\lambda}
+                 {P'_y \int R'(\lambda) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times
-              \frac{\int F'(\lambda) S_x d\lambda}
-                   {\int F'(\lambda / (1+z)) \times \frac{1}{(1 + z)^2} d\lambda} \\
+              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
+                   {\int F'(\frac{\lambda}{1+z}) \times \frac{1}{(1 + z)^2} S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
-              \frac{\int \frac{\lambda F(\lambda)}{hc} S_x d\lambda}
-                   {\int \frac{F(\lambda / (1+z))}{(1+z)hc} S_y d\lambda} \\
+              \frac{\int \frac{\lambda}{hc} F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} .
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
 \end{aligned}
@@
             \frac{P'_x}{P'_y} \times (1 + z)^2 \times
-            \frac{\int \lambda F(\lambda) S_x d\lambda}
-                 {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}\right) \\
+            \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                 {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}\right) \\
          &= 2.5 \left(
@@
             + \text{log}( {(1 + z)^2})
-            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda}
+            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}
             \right) \right) \\
@@
             + 2.5 \text{log} \left(
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) \\
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
          &= 5 \text{log} (1 + z)
             + 2.5 \text{log} \left(
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
             - P_x + P_y .
@@
             + 2.5 \text{log} \left(
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
             - P_x + P_y \\
@@
             + 2.5 \text{log} \left(
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right)
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
             + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
@@
             + 2.5 \text{log} \left(
-              \frac{\int \lambda F(\lambda) S_x d\lambda}
-                   {\int \frac{\lambda}{1+z} F(\lambda / (1+z)) S_y d\lambda} \right) .
+              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) .
 \end{aligned}
@@
   \item The sign is different for the first term. This will have a subtle but
-  frustrating effect for real values. Typically the zero-point values are
+  frustrating effect for real measurements. Typically the zero-point values are
   similar, so this term is close to 0. However, the term isn't always zero. As
   we observe more distant supernovae, it is useful to switch our observational
-  filter to a filter that is sensitive to longer wavelengths. Each time we make
-  this switch we introduce a small but consistent bias.
+  filter to a filter that is sensitive to longer wavelengths. Each observation
+  filter will have its own small bias.
 
@@
   \ref{fig:H0bootstrap}, we aren't terribly confident in the numbers because we
-  were unable to correct for the zero-point errors.
+  were unable to correct for the zero-point correction errors or verify that
+  these errors don't exist.
 

### 2024-12-30 paper/code_listing.py
Use the American Astronomical Society style

@@ -1,39 +1,0 @@
-import snpy
-import numpy
-
-# Use an arbitrary epoch for the spectral energy density template.
-wave, flux = snpy.kcorr.get_SED(day=9)
-
-# Use an arbitrary redshift.
-z = 0.5
-
-# Use the B and R filters from the Lick telescope as examples.
-rest_filter = snpy.fset["Bkait"]
-obs_filter = snpy.fset["Rkait"]
-
-# Compute the desired rest magnitude.
-m_b = rest_filter.synth_mag(wave, flux)
-
-# Compute the observed magnitude after redshift effects.
-m_r = obs_filter.synth_mag(wave, flux, z=z)
-
-# TODO(lpe): Wait, why is m_r brighter than m_b? Shouldn't the fix term have
-# the opposite sign?
-# Huh... m_r is brighter than m_b even if SED is forced to be flat.
-
-got_k = snpy.kcorr.K(wave, flux, rest_filter, obs_filter, z=z)[0]
-
-# From the definition of k-corrections:
-want_k = m_r - m_b
-
-def print_results():
-  """
-  >>> print_results()
-  got_k (-0.679138363247608) != want_k (-1.1193665108868114)
-  2.5*log10(1+z) == 0.4402281476392031
-  got_k - 2.5*log10(1+z) (-1.1193665108868112) == want_k (-1.1193665108868114)
-  """
-  print(f"got_k ({got_k}) != want_k ({want_k})")
-  print(f"2.5*log10(1+z) == {2.5 * numpy.log10(1+z)}")
-  fixed = got_k - 2.5*numpy.log10(1+z)
-  print(f"got_k - 2.5*log10(1+z) ({fixed}) == want_k ({want_k})")

### 2024-12-30 paper/dark_energy_corrections.tex

--- 2024-12-28 paper/paper.tex
@@
-\documentclass{article}
+\documentclass[linenumbers]{aastex631}
 
-\usepackage{arxiv}
+\usepackage{amsmath}
 
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{amsmath}
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{graphicx}
-\usepackage{natbib}
-\usepackage{csquotes}
-\usepackage{float}
-\usepackage{listings}
-\usepackage{xcolor}
-\usepackage{fancyvrb}
+\shorttitle{Dark energy is based on a math error from 1930}
+\shortauthors{Evans}
 
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
-
-\lstdefinestyle{mystyle}{
-    backgroundcolor=\color{backcolour},
-    commentstyle=\color{codegreen},
-    keywordstyle=\color{magenta},
-    numberstyle=\tiny\color{codegray},
-    stringstyle=\color{codepurple},
-    basicstyle=\ttfamily\footnotesize,
-    breakatwhitespace=false,
-    breaklines=true,
-    captionpos=b,
-    keepspaces=true,
-    numbers=left,
-    numbersep=5pt,
-    showspaces=false,
-    showstringspaces=false,
-    showtabs=false,
-    tabsize=2
-}
-
-\lstset{style=mystyle}
+\begin{document}
 
@@
 
-\date{\today}
+\correspondingauthor{Logan P. Evans}
+\email{loganpevans@gmail.com}
 
-\author{
-  \href{https://orcid.org/0000-0001-6450-3262}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Logan P.~Evans}
-  \\ \texttt{loganpevans@gmail.com}
-}
-
-% Uncomment to override  the `A preprint' in the header
-%\renewcommand{\headeright}{Technical Report}
-%\renewcommand{\undertitle}{Technical Report}
-\renewcommand{\shorttitle}{\textit{arXiv} Template}
-
-\hypersetup{
-pdftitle={Dark energy is based on a math error from 1930},
-pdfsubject={astro-ph.CO},
-pdfauthor={Logan P.~Evans},
-pdfkeywords={cosmological parameters, dark energy},
-}
-
-\begin{document}
-\maketitle
+\author[0000-0001-6450-3262]{Logan P. Evans}
 
 \begin{abstract}
-  We show that the magnitude of distant objects has been calculated incorrectly
-  since 1930. We describe how this math error in the formula for K-corrections
-  has propagated for over nine decades before re-deriving the K-corrections
-  equation. Finally, we explore the consequences of correcting this flaw and
-  resolve two of the preeminent mysteries in cosmology: dark energy is not
-  supported by observations of Type Ia supernovae, and the Hubble tension is
-  due to a calculation error.
+We show that the apparent magnitude of distant objects has been calculated
+incorrectly since 1930. We describe how this redshift correction flaw in the
+formula for K-corrections has propagated for over nine decades. We also
+re-derive the K-corrections equation. This derivation reveals that the
+correction for zero-points in different filters also has a flaw. We explore the
+consequences of properly correcting apparant magnitudes for redshift and
+conclude that this resolves two of the preeminent mysteries in cosmology: dark
+energy is not supported by observations of Type Ia supernovae, and the Hubble
+tension is due to a calculation error.
 \end{abstract}
+
+%% https://astrothesaurus.org
+\keywords{Type Ia supernovae(1728) --- Apparent magnitude(59)}
 
@@
 
-Since \citet{planck2020}, it has been evident that something was missing with
-our understanding of cosmology. This research used an alternative technique
-based on measurements of the cosmic microwave background to compute the Hubble
-constant, but as summarized in \citet{perivolaropoulos2022}, this measurement
-was incompatible with the Hubble constant measured from SnIa. As we will
-discuss in Section \ref{sec:tension}, fixing the error with K-corrections
-produces a measurement of the Hubble constant that is compatible with models
-based on the cosmic microwave background.
+\citet{planck2020} used an alternative technique to compute the Hubble constant
+that is based on measurements of the cosmic microwave background. CMB based
+computations of $H0$ has made it evident that something was missing with our
+understanding of cosmology because this measurement is incompatible with the
+Hubble constant when measured from SnIa. As we will discuss in Section
+\ref{sec:tension}, fixing the error with K-corrections produces a measurement
+of the Hubble constant that is compatible with models based on the cosmic
+microwave background.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
@@
   magnitude data. The displayed points are roughly a third of the values in the
-  full DES dataset, selected evenly to aid visibility. The $k(z) = 1$ treatment
-  is clearly non-linear while the $k(z) = 1 + z$ treatment appears to be
-  linear.}
+  full SnIa dataset published in \citet{abbott2024}, selected evenly to aid
+  visibility. The $k(z) = 1$ treatment, which represents the uncorrected
+  values, is clearly non-linear while the $k(z) = 1 + z$ treatment which fixes
+  the K-correction redshift error, appears to be linear.}
   \label{fig:mu_distance_vs_redshift}
@@
 
-Type Ia supernova are used to explore the relationship between distances and
+Type Ia supernovae are used to explore the relationship between distances and
 redshifts because these events always happen in similar ways, so the absolute
@@
 
-Measuring the apparent brightness of a Type Ia supernova is non-trivial. The
-aspect of the process that we will explore here concerns how redshift affects
-the light we observe. This problem is often referred to as K-corrections, and
-one of the first mathematical treatments of the problem was performed by
+However, redshifting light dims an observation in three ways:
+
+\begin{itemize}
+  \item The energy of a wave is inversely proportional to its wavelength, so a
+  redshift of $z$ means the amount of energy per photon is reduced by a factor
+  of $\frac{1}{1+z}$.
+
+  \item The bandwidth is stretched out. If a rest frame would observe photons
+  between teh wavelengths of 400nm and 401nm, then with a redshift of $z = 1$,
+  redshifting these photons will spread them across the wavelengths from 800nm
+  to 802nm.
+
+  \item Cosmological time dilation reduces the rate at which photons arive.
+\end{itemize}
+
+To complicate matters, we use the B-band magnitude to calculate luminosity
+distance. We want to know how bright a supernova appears for wavelengths around
+445nm as if no redshift had occured. However, we typically need to observe the
+supernova with a filter that is sensitive to longer wavelengths, such as the
+i-band filter which is sensitive to wavelengths from 700nm-850nm
+\citep{flaugher2015}. The K-corrections formula allows us to take a magnitude
+measured in an observation filter $y$ and compute the magnitude in the target
+filter $y$.
+
+The first mathematical treatments of K-corrections was performed by
 \citet{tolman1930}. However, when Tolman made his derivation, he did not
-consider the effects of a spectra that is stretched out due to redshift.
+consider the effects of a spectra that is stretched out due to redshift. See
+the top two panels of Figure \ref{fig:k-example} for an example of this effect.
 
@@
 It should be specially noted that this expression differs from the correction
-to m proposed by de Sitter, which contains the term $(1 + z)^3$ instead of
+to $m$ proposed by de Sitter, which contains the term $(1 + z)^3$ instead of
 $(1 + z)^2$. Expression (28), however, would seem to give the proper correction
@@
 
-\begin{figure}[H]
+\begin{figure}
   \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
@@
 photon density function $R'$ that is the redshifted version of $F'$.
-Redshifting does two things:
+Redshifting the photon density does two things:
 
@@
 
-Combining these two phenomena together, we can calculated the redshifted
+Combining these two phenomena together, we can calculate the redshifted
 spectral energy density $R$ using
@@
 
-Note that this substitution omits the minus ($-$) sign.
+Note that this substitution omits the minus ($-$) sign that we used on a
+similar substitution for $P_x$.
 
@@
 
-then the meaning is a bit more clear. The left hand side
+\noindent then the meaning is a bit more clear. The left hand side
 $\mathcal{F}_x \times P'_x$ is the rate of photon collection for an idealized
@@
   \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x} \\
-        K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} .
+        K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} .
 \end{aligned}
@@
 \begin{aligned}
-  K'_{xy} &= \frac{\mathcal{F}_x P'_x}{\mathcal{F}_y P'_y} \\
-         &= \frac{P'_x \int F'(\lambda) S_x(\lambda) d\lambda}
-                 {P'_y \int R'(\lambda) S_y(\lambda) d\lambda} \\
+  K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} \\
+         &= \frac{P'_x}{P'_y} \times
+              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
+                   {\int R'(\lambda) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times
@@
 \begin{equation}
-  P = -2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+  P = -2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S(\lambda) d\lambda \right)
 \end{equation}
 
-where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an idealized
-spectral energy distribution at $z = 0$ for which $U = B = V = R = I = 0$ in
-the photometric system being used." Combining this with Equation \ref{eq:K2k}, we have
+\noindent where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an
+idealized spectral energy distribution at $z = 0$ for which
+$U = B = V = R = I = 0$ in the photometric system being used." Combining this
+with Equation \ref{eq:K2k}, we have
 
@@
 As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
-are corrected by adding $-2.5\text{log}(1+z)$, there is a linear relationship
-between redshift and luminosity distance. This is in accordance with the
-Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there is no
-visual acceleration.
+are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
+relationship between redshift and luminosity distance. This is in accordance
+with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
+is no visual acceleration.
 
@@
 
-The value estimated here, $H0 \sim 65.94 \pm 1.29$ is highly suspicious because of the
-flipped zero-point corrections, but it is consistent with estimates of $H0$
-that are based on the CMB. \citet{planck2020} published the CMB value of $H0
-\sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It is interesting to
-note that if the DES observations are restricted to only those with $z < 0.1$,
-which presumably is a small enough redshift that the K-corrections will use the
-same filter for both the target and observation filter and thus the zero-point
-corrections will cancel out, gives the estimate $H0 \sim 67.8 \pm 1.86$.
+The value estimated here, $H0 \sim 65.94 \pm 1.29$ is highly suspicious because
+of the flipped zero-point corrections, but it is consistent with estimates of
+$H0$ that are based on the CMB. \citet{planck2020} published the CMB value of
+$H0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It is
+interesting to note that restricting the DES observations to only those with $z
+< 0.1$, which presumably is a small enough redshift that all observations will
+have been made with the same filter, gives the estimate
+$H0 \sim 67.8 \pm 1.86$.
 
-\begin{figure}[ht]
+\begin{figure}
   \includegraphics[width=\linewidth]{velocity_vs_distance.png}
@@
 
-\begin{figure}[ht]
+\begin{figure}
   \includegraphics[width=\linewidth]{bootstrapped_H0.png}
@@
 
-\bibliographystyle{unsrtnat}
-\bibliography{references}
+\bibliography{references}{}
+\bibliographystyle{aasjournal}
 

### 2025-01-04 paper/dark_energy_corrections.tex
Incorporate some suggestions

@@
 
-\shorttitle{Dark energy is based on a math error from 1930}
+\shorttitle{Correcting K-correction}
 \shortauthors{Evans}
@@
 
-\title{Dark energy is based on a math error from 1930}
+\title{Correcting K-correction: restoring the time dilation term and fixing the
+inverted zero-point term removes accelerating expansion and resolves the Hubble
+tension}
 
@@
 \begin{abstract}
-We show that the apparent magnitude of distant objects has been calculated
-incorrectly since 1930. We describe how this redshift correction flaw in the
-formula for K-corrections has propagated for over nine decades. We also
-re-derive the K-corrections equation. This derivation reveals that the
-correction for zero-points in different filters also has a flaw. We explore the
-consequences of properly correcting apparant magnitudes for redshift and
-conclude that this resolves two of the preeminent mysteries in cosmology: dark
-energy is not supported by observations of Type Ia supernovae, and the Hubble
-tension is due to a calculation error.
+We rederive the K-correction equation and discover that the version of the
+equation used in modern cosmology contains three errors. The oldest of these
+errors traces back nine decades; in 1930 the equation did not correct for
+spectral bandwidth stretching, followed by a rederivation in 1968 that
+accounted for spectral bandwidth stretching but did not correct for time
+dilation. Two new errors were introduced in 1996, one of which causes
+systematic distance biases by inverting the zero-point correction term. We
+conclude that properly correcting apparent magnitudes for redshift resolves two
+of the preeminent mysteries in cosmology: first, dark energy is not supported
+by observations of Type Ia supernovae and second, the Hubble tension is due to
+the errors in the K-correction equation.
 \end{abstract}
@@
 
-The measurement of Type Ia supernovae is one of the primary sources of data for
-cosmological models. The measurements involve estimating the peak magnitude in
-the B filter \citet{riess1998} for the rest frame, meaning we want to know how
-bright the SnIa would be if its light did not undergo redshift. Redshift causes
-the light that would be measured by the B filter in a rest frame to be shifted
-to another filter. In order to observe a SnIa in an arbitrary filter and report
-the magnitude in the B filter we use a technique called K-corrections.
+The estimate of Type Ia supernovae (SnIa) distances is one of the primary
+sources of data for cosmological models. Performing these distance estimates
+involves taking a measurement of redshifted light in our observation frame and
+then calculating the rest frame magnitude as if no redshift had occurred. It is
+standard to report rest frame magnitudes in the $B$ filter, which is sensitive to
+blue light, regardless of the filter used to take measurements in the
+observation frame. The equation that converts from an observation frame
+magnitude to a rest frame magnitude in the $B$ filter is called K-correction.
 
-The first formal derivation of K-corrections was performed by
-\citet{tolman1930} and it failed to account for bandwidth stretching, one of
-the dimming effects of redshift. This error was noted by \citet{desitter1934},
-but in \citet{hubble1935} the discrepancy was noted and ignored.
-\citet{oke1968} rederived K-corrections, but they failed to account for time
-dilation, one of the other dimming effects of redshift. In \citet{kim1996},
-K-corrections were extended to handle additional cross-filter comparisons and
-address zero-point corrections, but they started their derivation by
-referencing the incorrect equation from \citet{oke1968}. The derivation in
-\citet{kim1996} forms the basis for modern implementations of K-corrections.
-This history is explored in more depth in Section \ref{sec:history}.
+The first formal derivation of K-correction was performed by
+\citet{tolman1930}, but it did not account for spectral bandwidth stretching,
+one of the dimming effects of redshift. An alternative K-correction was
+correctly derived by \citet{desitter1934}. However, in \citet{hubble1935}, the
+discrepancy was noted yet dismissed. \citet{oke1968} rederived the K-correction
+equation.  They accounted for spectral bandwidth stretching, but they did not
+account for time dilation, one of the other dimming effects of redshift. The
+paper by \citet{kim1996}, which is the basis for modern implementations of
+K-correction, extended the work of \citet{oke1968} to handle additional
+cross-filter comparisons and added a term that was intended to address
+zero-point corrections. This history is explored in more depth in Section
+\ref{sec:history}.
 
@@
 are farther away than they really are, and the effect compounds for greater
-distances. Up until \citet{riess1998}, we didn't have distant enough
-observations for this error to matter much for cosmology models, but in the
-late 1990s, it was clear that our measurements for distance and redshift were
-not linear. This observation led to a model that utilized a cosmological
-constant and dark energy in order to explain the non-linear distance-redshift
-graph. We will show in Section \ref{sec:tension} that correcting the flaw
-with K-corrections leads to a linear graph that does not need to rely on a
-cosmological constant.
+distances. Up until \citet{riess1998}, we did not have distant enough
+observations for this error to matter much for cosmological models, but by the
+late 1990s, it became clear that our measurements for distance and redshift were
+not linear. This realization led to a model that utilized a cosmological
+constant $\Lambda$ and dark energy in order to explain the non-linear
+distance-redshift graph. We will show in Section \ref{sec:tension} that
+correcting the flaw with K-correction leads to a linear graph that does not
+need to rely on a cosmological constant.
 
-\citet{planck2020} used an alternative technique to compute the Hubble constant
-that is based on measurements of the cosmic microwave background. CMB based
-computations of $H0$ has made it evident that something was missing with our
-understanding of cosmology because this measurement is incompatible with the
-Hubble constant when measured from SnIa. As we will discuss in Section
-\ref{sec:tension}, fixing the error with K-corrections produces a measurement
-of the Hubble constant that is compatible with models based on the cosmic
-microwave background.
+\citet{planck2015} used an alternative technique to compute the Hubble constant
+$H_0$ that is based on measurements of the cosmic microwave background (CMB).
+CMB-based computations of $H_0$ has made it evident that something was missing
+with our understanding of cosmology because this technique produces a
+significantly different value than when the constant is derived using SnIa.  As
+we will discuss in Section \ref{sec:tension}, fixing the error with
+K-correction produces a measurement of the Hubble constant that is compatible
+with models based on the CMB.
 
-\section{A brief history of K-corrections}
+\section{A brief history of K-correction}
 \label{sec:history}
 
-Observations of Type Ia supernova are essential to calibrate models that
-measure redshift and estimate distance. This relationship, often called the
-Hubble-Lema\^{i}tre law, describes how quickly the universe is expanding.
-However, \citet{riess1998} and \citet{perlmutter1999} presented evidence that
-there isn't a linear relationship between redshift and distance, but instead,
-distant objects are farther away than their redshift would predict (see Figure
+Observational data from SnIa are essential for the calibration of models that
+use redshift to estimate distance. The approximately linear relationship
+between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
+describes how quickly the universe is expanding. However, \citet{riess1998}
+and \citet{perlmutter1999} presented evidence that there isn't a linear
+relationship between redshift and distance, but instead, distant objects are
+farther away than their redshift would predict (see Figure
 \ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
 acceleration of the universe is faster today than it was for old observations.
-Previously the cause of this phenomenon was unknown and was referred to as
-dark energy.
+Previously the cause of this phenomenon was unknown and was referred to as dark
+energy.
 
@@
 
-Type Ia supernovae are used to explore the relationship between distances and
-redshifts because these events always happen in similar ways, so the absolute
-brightness is roughly always the same. An analogy is to imagine someone walking
-in the dark and lighting matches. As long as we know how brightly a match burns
-at a known distance, we can estimate the distance to any match by measuring the
-apparent brightness before applying some geometry.
+SnIa are used to explore the relationship between distance and redshift because
+these events always happen in similar ways, which keeps the absolute brightness
+roughly constant. An analogy is to imagine someone walking in the dark and
+lighting matches. If we know how brightly a match burns at a known distance, we
+can estimate the distance to any match by measuring the apparent brightness
+before applying some geometry.
 
@@
 \begin{itemize}
-  \item The energy of a wave is inversely proportional to its wavelength, so a
+  \item The energy of a wave is inversely proportional to its wavelength; thus a
   redshift of $z$ means the amount of energy per photon is reduced by a factor
@@
 
-  \item The bandwidth is stretched out. If a rest frame would observe photons
-  between teh wavelengths of 400nm and 401nm, then with a redshift of $z = 1$,
-  redshifting these photons will spread them across the wavelengths from 800nm
-  to 802nm.
+  \item The bandwidth stretches. If a rest frame observes photons
+  between the wavelengths of 400nm and 401nm, then a redshift of $z = 1$
+  stretches the wavelength from 800nm to 802nm.
 
-  \item Cosmological time dilation reduces the rate at which photons arive.
+  \item Cosmological time dilation reduces the rate at which photons arrive.
 \end{itemize}
 
-To complicate matters, we use the B-band magnitude to calculate luminosity
+To complicate matters, we use the $B$ band magnitude to calculate luminosity
 distance. We want to know how bright a supernova appears for wavelengths around
-445nm as if no redshift had occured. However, we typically need to observe the
+445nm as if no redshift had occurred. However, we typically need to observe the
 supernova with a filter that is sensitive to longer wavelengths, such as the
-i-band filter which is sensitive to wavelengths from 700nm-850nm
-\citep{flaugher2015}. The K-corrections formula allows us to take a magnitude
+$i$ band filter which is sensitive to wavelengths from 700nm-850nm
+\citep{flaugher2015}. The K-correction formula allows us to take a magnitude
 measured in an observation filter $y$ and compute the magnitude in the target
@@
 
-The first mathematical treatments of K-corrections was performed by
+The first mathematical treatments of K-correction was performed by
 \citet{tolman1930}. However, when Tolman made his derivation, he did not
-consider the effects of a spectra that is stretched out due to redshift. See
+consider the effects of a spectrum that is stretched due to redshift. See
 the top two panels of Figure \ref{fig:k-example} for an example of this effect.
@@
 A year later, \citet{hubble1935} published a similar set of calculations for
-K-corrections, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
+K-correction, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
 correction term used by de Sitter. They started their derivation by copying the
-incorrect equation from 1930. After their derivation, they noted,
+incorrect equation from 1930. After their derivation, they noted:
 
@@
 
-The Hubble K-corrections with the incorrect correction term have been used ever
+The Hubble K-correction with the incorrect correction term have been used ever
 since.
@@
 in energy and to the spectral bandwidth elongation, which leaves time dilation
-as the factor that was omitted. A graph that demonstrates why it's essential to
-correct for both the spectra bandwidth warping and time dilation is presented
+as the factor that was omitted. A graph that demonstrates why it is essential to
+correct for both the spectra bandwidth stretching and time dilation is presented
 in Figure \ref{fig:k-example}.
@@
   \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
-  \caption{An example of how K-corrections take an observed magnitude and
+  \caption{An example of how K-correction takes an observed magnitude and
   produce a rest frame magnitude. In this example, $z=1$. The observation
@@
   applied which doubles the photons per nanometer. The top right panel shows
-  the effect of correcting for the bandwidth spectrum warping effect --
+  the effect of correcting for the spectral bandwidth stretching effect --
   correcting all wavelengths for the rest frame means that the measured
-  wavelengths have blueshifted, ideally into the cross band B filter. Applying
+  wavelengths have blueshifted, ideally into the cross band $B$ filter. Applying
   both effects, shown in the bottom right panel, requires applying two
@@
 
-The modern treatment of K-corrections is based on the work of \citet{kim1996}.
-This work extended the calculations of K-corrections to extend to filters
-beyond B and V. It also introduced a term that deals with the zero-point for
-the actual filters. In the modern day, filters measure the photon flux as
-opposed to the energy flux. Historically, bolometric devices would measure the
-energy flux, but modern CCD cameras effectively measure the photon flux.
+The modern treatment of K-correction is based on the work of \citet{kim1996}.
+This work extended the calculations of K-correction to extend to filters beyond
+the blue $B$ and visible $V$ bands. It also introduced a term that deals with
+the zero-point for the actual filters. In the modern day, filters measure the
+photon flux as opposed to the energy flux. Historically, bolometric devices
+would measure the energy flux, but modern charge-coupled device (CCD) cameras
+effectively measure the photon flux.
 
@@
 
-This equation has three errors, which we will explore in Section
+This equation has three errors that we will explore in Section
 \ref{sec:consequences}.
 
-\section{Derivation of K-corrections}
+\section{Derivation of K-correction}
 \label{sec:derivation}
@@
 $\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
-second. A summary of how this works is provided by \citet{lesser2015}. The
-measured energy is produced by electrons not photons, so the measured number is
-proportional to the number of photons. However, we need to calculate the
-expected number of photons collected by using a spectral energy density
-function $F$. The value $F(\lambda)$ gives the amount of energy collected by a
-bolometric device for the wavelength $\lambda$.
+second. A summary of how this works is provided by \citet{lesser2015}.
+Photogenerated electrons are collected in potential wells, which means that the
+measured energy is proportional to the number of photons. However, we need to
+calculate the expected number of photons collected by using a spectral energy
+density function $F$. The value $F(\lambda)$ gives the amount of energy
+collected by a bolometric device for the wavelength $\lambda$.
 
@@
 
-It's important to note that for the blueshifted wavelength $\lambda / (1+z)$,
+It is important to note that for the blueshifted wavelength $\lambda / (1+z)$,
 this equation produces
@@
 
-  In order to account for this bandwidth spectral warping effect, we will need
+  In order to account for this spectral bandwidth stretching effect, we will need
   to multiply $F'$ by a second factor of $1/(1+z)$.
@@
 
-Combining these two phenomena together, we can calculate the redshifted
-spectral energy density $R$ using
+Combining these two phenomena, we can calculate the redshifted spectral energy
+density $R$ using
 
@@
 \ref{eq:flux2mag} we will change directions and look at the definition of
-K-corrections $K_{xy}$. This value allows us to make an observation in filter
+K-correction $K_{xy}$. This value allows us to make an observation in filter
 $y$ and report what the magnitude would have been in filter $x$ if no redshift
-occured:
+occurred:
 
@@
 
-The second line of Equation \ref{eq:definition} expands the distance modulus
+\noindent The second line of Equation \ref{eq:definition} expands the distance modulus
 $\mu$ using $\mu = m - M$ where $m$ is the observed magnitude and $M$ is the
@@
 
-It's useful to inspect this equation to consider whether the term
-$\frac{P'_y}{P'_x}$ is correct, or if it might be flipped to the inverse of
-what it should be. However, if we rewrite Equation \ref{eq:as_flux} as
+It is useful to consider whether the term $\frac{P'_y}{P'_x}$ is correct or if
+it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as
 
@@
 
-\noindent then the meaning is a bit more clear. The left hand side
-$\mathcal{F}_x \times P'_x$ is the rate of photon collection for an idealized
-telescope in filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon
-collection for an idealized telescope in filter $y$. We are able to observe the
-value $\mathcal{F}_y \times P'_y$ and want to use the fudge factor $K'_{xy}$ to
-produce the value $\mathcal{F}_x \times P'_x$.
+\noindent then the meaning becomes more clear. The left side, $\mathcal{F}_x
+\times P'_x$, is the rate of photon collection for an idealized telescope in
+filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon collection
+for an idealized telescope in filter $y$. We observe the value $\mathcal{F}_y
+\times P'_y$ and want to use the fudge factor $K'_{xy}$ to produce the value
+$\mathcal{F}_x \times P'_x$.
 
@@
 
-Now we use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
+We now use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
 to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
 spectral energy density function $F$. Note that $\mathcal{F}_x$ uses the rest
-frame spectral energy density $F$ while $\mathcal{F}_y$ uses the redshifted
+frame spectral energy density $F$, while $\mathcal{F}_y$ uses the redshifted
 spectral energy density $R(\lambda)$:
@@
 
-\noindent where, according to \citet{kim1996}, "$\mathcal{Z}(\lambda)$ is an
+\noindent where, according to \citet{kim1996}, ``$\mathcal{Z}(\lambda)$ is an
 idealized spectral energy distribution at $z = 0$ for which
-$U = B = V = R = I = 0$ in the photometric system being used." Combining this
+$U = B = V = R = I = 0$ in the photometric system being used.'' Combining this
 with Equation \ref{eq:K2k}, we have
@@
   \item The sign is different for the first term. This will have a subtle but
-  frustrating effect for real measurements. Typically the zero-point values are
-  similar, so this term is close to 0. However, the term isn't always zero. As
-  we observe more distant supernovae, it is useful to switch our observational
-  filter to a filter that is sensitive to longer wavelengths. Each observation
-  filter will have its own small bias.
+  frustrating effect for real measurements. The zero-point values are usually,
+  but not always, close to zero. As we observe more distant supernovae, it is
+  useful to switch our observational filter to a filter that is sensitive to
+  longer wavelengths. Each observation filter will have its own small bias.
 
-  This effect by itself can alter estimates of $H_0$ by several km/s / Mpc.
-  While we present an estimate of the Hubble constant in Figure
-  \ref{fig:H0bootstrap}, we aren't terribly confident in the numbers because we
-  were unable to correct for the zero-point correction errors or verify that
-  these errors don't exist.
+  This effect by itself can alter estimates of $H_0$ by several km s$^{-1}$
+  Mpc$^{-1}$.  While we present an estimate of the Hubble constant in Figure
+  \ref{fig:H0bootstrap}, we are not terribly confident in the numbers because
+  we were unable to correct for the zero-point errors, or verify that these
+  errors may not exist.
 
-  \item The second term is multiplied by a $2.5$ in \citet{kim1996} but is
-  multiplied by a $5$ here. This is the manifestation of the error in
+  \item The second term is multiplied by $2.5$ in \citet{kim1996}, but is
+  multiplied by $5$ here. This is the manifestation of the error in
   \citet{tolman1930}.
 
-  \item In our derivation, the third term is has an extra $1 + z$ expression.
+  \item In our derivation, the third term has an extra $1 + z$ expression.
   Based on an inspection of the SN(oo)py software package presented by
   \citet{snpy}, this error is ignored and software package authors implement it
-  as the expression is intended, not precisely as the expression is written.
+  as intended, not precisely as written.
 \end{itemize}
@@
 Since the corrected values are approximately linear, we can use them to
-estimate the Hubble constant $H0$. This is demonstrated in Figure
+estimate the Hubble constant $H_0$. This is demonstrated in Figure
 \ref{fig:expansion}. Furthermore, we performed a bootstrap calculation to
-estimate the distribution of $H0$ estimates in Figure \ref{fig:H0bootstrap}.
+estimate the distribution of $H_0$ estimates in Figure \ref{fig:H0bootstrap}.
 
-The value estimated here, $H0 \sim 65.94 \pm 1.29$ is highly suspicious because
-of the flipped zero-point corrections, but it is consistent with estimates of
-$H0$ that are based on the CMB. \citet{planck2020} published the CMB value of
-$H0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It is
-interesting to note that restricting the DES observations to only those with $z
-< 0.1$, which presumably is a small enough redshift that all observations will
-have been made with the same filter, gives the estimate
-$H0 \sim 67.8 \pm 1.86$.
+The value estimated here, $H_0 \sim 65.94 \pm 1.29$ is highly suspicious
+because of the flipped zero-point corrections, but it is consistent with
+estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
+CMB value of $H_0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It
+is interesting to note that restricting the Dark Energy Survey observations of
+SnIa \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
+small enough redshift that all observations will have been made with the same
+filter, gives the estimate $H_0 \sim 67.8 \pm 1.86$.
 
@@
   \includegraphics[width=\linewidth]{bootstrapped_H0.png}
-  \caption{A histogram of 100000 bootstrap trials measuring the Hubble constant
-  $H0$. Each trial samples an absolute Type Ia magnitude $M \sim Norm(-19.2334,
-  0.0404)$ based on data published by \citet{camarena2020}. It then samples,
+  \caption{A histogram of $100{\small,}000$ bootstrap trials measuring the Hubble constant
+  $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
+  0.0404)$ for SnIa based on data published by \citet{camarena2020}. It then samples,
   with replacement, a population of supernovae from the dataset published by
   \citet{abbott2024}. Finally, it uses the non-parametric linear regression
-  technique described by \citet{siegel1982}. The result of the bootstrap is $H0
+  technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
   \sim Norm(65.94, 1.29^2)$.
@@
 
-A lot of data is going to have to be reanalyzed.
+Since the K-correction error has corrupted all astronomical measurements that
+depend on both magnitude and redshift, a lot of data needs to be reanalysed.
+Only once the data is cleaned can cosmological parameters, such as those used
+by the Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the
+$\Lambda$-CDM model, be reevaluated.
+
+The reasons that the K-correction errors went undiscovered for so long should
+also be explored. Many hints existed that something was wrong, yet the
+problems persisted.
 

### 2025-01-04 src/redshift/supernova.py

@@ -169,7 +169,7 @@ class Supernova:
                     MU=float(row[idx["MU"]]),
                     # see perivolaropoulos2022 for the Camerena and Marra references
                     # absolute_magnitude=-19.105, # ~70km/s / Mpc
-                    absolute_magnitude=-19.2334, # Camarena and Marra 2020b
+                    absolute_magnitude=-19.2334,  # Camarena and Marra 2020b
                     # absolute_magnitude=-19.3232,  # Abbott
                     # absolute_magnitude=-19.401, # Camarena and Marra 2020a
                     color=float(row[idx["c"]]),
@@ -680,11 +680,11 @@ def generate_all_graphs(data):
     plt.rcParams["hatch.linewidth"] = linewidth
     velocity_vs_distance_graph(data, save=True)
 
-    #plt.cla()
-    #plt.rcParams["figure.figsize"] = figsize
-    #plt.rcParams["text.usetex"] = True
-    #plt.rcParams["hatch.linewidth"] = linewidth
-    #bootstrap_hubble_parameter_graph(data, save=True)
+    # plt.cla()
+    # plt.rcParams["figure.figsize"] = figsize
+    # plt.rcParams["text.usetex"] = True
+    # plt.rcParams["hatch.linewidth"] = linewidth
+    # bootstrap_hubble_parameter_graph(data, save=True)
 
     plt.cla()
     plt.rcParams["figure.figsize"] = figsize
@@ -841,15 +841,15 @@ if __name__ == "__main__":
 
     generate_all_graphs(data)
 
-    #all_lum_distance_vs_redshift_graph(data, save=False)
+    # all_lum_distance_vs_redshift_graph(data, save=False)
     # velocity_vs_distance_graph(data, correction=Correction.ONE, save=False)
     # energy_loss_vs_orig_distance(data, correction=Correction.ONE, save=False)
     # recessional_velocity_vs_intercept_time_graph(data, correction=Correction.ONE, save=False)
 
-    #graph_model(data)
-    #distance_residuals_graph(data)
+    # graph_model(data)
+    # distance_residuals_graph(data)
 
-    #graph(data)
+    # graph(data)
 
-    #bootstrap_hubble_parameter_graph(data)
-    #plt.show()
+    # bootstrap_hubble_parameter_graph(data)
+    # plt.show()

### 2025-01-04 paper/dark_energy_corrections.tex

@@
 
-\title{Correcting K-correction: restoring the time dilation term and fixing the
-inverted zero-point term removes accelerating expansion and resolves the Hubble
-tension}
+\title{Correcting K-correction: fixing the time dilation and zero-point terms resolves the Hubble tension and removes evidence for accelerating expansion}
 
@@
 We rederive the K-correction equation and discover that the version of the
-equation used in modern cosmology contains three errors. The oldest of these
+equation used to compute magnitudes contains three errors. The oldest of these
 errors traces back nine decades; in 1930 the equation did not correct for
@@
 depend on both magnitude and redshift, a lot of data needs to be reanalysed.
-Only once the data is cleaned can cosmological parameters, such as those used
-by the Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the
-$\Lambda$-CDM model, be reevaluated.
+Cosmological parameters, such as those used by the
+Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the $\Lambda$-CDM
+model, can only be recalculated once the data is cleaned.
 

### 2025-01-05 paper/dark_energy_corrections.tex
Use a new figure showing the ratio calculation

@@
 
-\title{Correcting K-correction: fixing the time dilation and zero-point terms resolves the Hubble tension and removes evidence for accelerating expansion}
+\title{Correcting K-correction: dark energy is based on a math error from 1930}
 
@@
 \begin{figure}
-  \includegraphics[width=.75\linewidth]{K-corrections_for_photon_counts.png}
-  \caption{An example of how K-correction takes an observed magnitude and
-  produce a rest frame magnitude. In this example, $z=1$. The observation
-  filter measures magnitude, which is equivalent to measuring the number of
-  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
-  applied which doubles the photons per nanometer. The top right panel shows
-  the effect of correcting for the spectral bandwidth stretching effect --
-  correcting all wavelengths for the rest frame means that the measured
-  wavelengths have blueshifted, ideally into the cross band $B$ filter. Applying
-  both effects, shown in the bottom right panel, requires applying two
-  correction factors of $1+z$. This example omits the correction for a similar
-  effect related to lower energy due to the Planck relation because CCD cameras
-  obviate the need to correct for this effect.
+  \includegraphics[width=.75\linewidth, height=0.75\vsize]{k_equation_flow.png}
+  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
+  are able to observe a SnIa in the redshifted observation frame, but we want
+  to compute the magnitude in the rest frame as if no redshift has occurred.
+  This computation starts with $F(\lambda$, the spectral energy density that
+  describes the expected luminosity in the rest frame. Using the SED, we can
+  compute the photon density $F'(\lambda)$ for the rest frame. We show the
+  process of computing $R'(\lambda$, the photon density in the observation
+  frame, in three phases starting at the top right of the figure. First we
+  stretch the photon density, but this step inflates counts. In the second
+  step, we correct for the inflated counts by multiplying by $\frac{1}{1+z}$;
+  at this point, the total count equals the total count of $F'(\lambda)$.
+  Finally, in the third step we finish calculating the observation frame photon
+  density $R'(\lambda)$ by accounting for time dilation, which also reduces
+  photon counts by a factor of $\frac{1}{1+z}$.  Given the rest frame and
+  observation frame photon densities, we can compute the expected ratio of
+  photons by totalling the area under the curves in the two panels at the
+  bottom of the graph. This example does not show the process of converting
+  photon flux to magnitude, nor does it address the zero-point correction.
   }

### 2025-01-05 src/redshift/supernova.py

@@ -4,6 +4,7 @@ import dataclasses
 from dataclasses import dataclass, field, asdict
 from datetime import date
 from matplotlib import pyplot as plt
+from matplotlib.patches import FancyArrowPatch
 from numpy.polynomial.polynomial import Polynomial
 from pprint import pprint
 from typing import ClassVar
@@ -337,6 +338,343 @@ def k_corrections_for_photon_counts_graph(save=False):
             GRAPHS_DIR / f"K-corrections_for_photon_counts.png",
             bbox_inches="tight",
         )
+        plt.cla()
+
+def k_equation_flow_graph(save=False):
+    z = 0.5
+
+    lo = 100
+    hi = 2000
+    xs = np.linspace(lo, hi, hi - lo)
+
+    fig = plt.figure(figsize=[8.0, 10.0])
+    fig.suptitle(r"Calculating $K'_{xy}$, the ratio of rest frame to observation frame counts for $z = 0.5$")
+
+    def F():
+        ax = fig.add_axes([0.1, 9/11, 0.3, 0.075])
+        ax.spines["top"].set_visible(False)
+        ax.spines["right"].set_visible(False)
+        ax.set_title(r"$F(\lambda)$: rest frame spectral energy density")
+        ax.set_xlabel(r"$\lambda$")
+        ax.set_ylabel(r"spectral energy density")
+
+        norm = scipy.stats.norm(450, 100)
+        unif = scipy.stats.uniform(1000, 250)
+
+        ys = [(norm.pdf(x) + unif.pdf(x) / 2.0) / 1e6 for x in xs]
+
+        ax.plot(xs, ys)
+        return ys
+    ys_F = F()
+
+    def arrow_to_counts():
+        ax = fig.add_axes([0.15, 8.1/11, 0.1, 0.04])
+        ax.spines["top"].set_visible(False)
+        ax.spines["bottom"].set_visible(False)
+        ax.spines["left"].set_visible(False)
+        ax.spines["right"].set_visible(False)
+        ax.set_xticks([])
+        ax.set_xticks([], minor=True)
+        ax.set_yticks([])
+        ax.set_yticks([], minor=True)
+        arrow = FancyArrowPatch(
+            (0.5, 1.0),  # Starting point in axes coordinates (x, y)
+            (0.5, 0.0),  # Ending point in axes coordinates (x, y)
+            arrowstyle="->",  # Arrow style 
[…]

### 2025-01-05 src/redshift/supernova.py
Fix a color

@@ -534,7 +534,7 @@ def k_equation_flow_graph(save=False):
 
         B_dist = scipy.stats.uniform(445 - 94/2, 445 + 94/2)
         S_x = [B_dist.pdf(x) * 400 for x in xs]
-        ax.plot(xs, S_x, color="blue")
+        ax.plot(xs, S_x)
 
         R_dist = scipy.stats.uniform(806 - 149/2, 806 + 149/2)
         S_y = [R_dist.pdf(x) * 600 for x in xs]

### 2025-01-05 paper/dark_energy_corrections.tex
AAS doesn't like stacked fractions...

@@
   redshift of $z$ means the amount of energy per photon is reduced by a factor
-  of $\frac{1}{1+z}$.
+  of $1 / (1+z)$.
 
@@
   stretch the photon density, but this step inflates counts. In the second
-  step, we correct for the inflated counts by multiplying by $\frac{1}{1+z}$;
+  step, we correct for the inflated counts by multiplying by $1/(1+z)$;
   at this point, the total count equals the total count of $F'(\lambda)$.
@@
   density $R'(\lambda)$ by accounting for time dilation, which also reduces
-  photon counts by a factor of $\frac{1}{1+z}$.  Given the rest frame and
+  photon counts by a factor of $1/(1+z)$.  Given the rest frame and
   observation frame photon densities, we can compute the expected ratio of
@@
 To convert the spectral energy density $F$ to the photon density $F'$, we need
-to use the Plank relation $E = \frac{hc}{\lambda}$ where $E$ is the energy, $h$
+to use the Plank relation $E = hc / \lambda$ where $E$ is the energy, $h$
 is Planck's constant, and $c$ is the speed of light. This gives us
@@
 
-It is useful to consider whether the term $\frac{P'_y}{P'_x}$ is correct or if
+It is useful to consider whether the term $P'_y / P'_x$ is correct or if
 it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as
@@
               \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
-                   {\int F'(\frac{\lambda}{1+z}) \times \frac{1}{(1 + z)^2} S_y(\lambda) d\lambda} \\
+                   {\int F'(\lambda / (1+z)) \times (1 / (1 + z)^2) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
-              \frac{\int \frac{\lambda}{hc} F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
+              \frac{\int (\lambda / hc) F(\lambda) S_x(\lambda) d\lambda}
+                   {\int (\lambda / ((1+z)hc)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
+                   {\int (\lambda / (1+z) F(\lambda / (1+z)) S_y(\lambda) d\lambda} .
 \end{aligned}
@@
             \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                 {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}\right) \\
+                 {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda}\right) \\
          &= 2.5 \left(
@@
             + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}
+                                    {\int (\lambda / (1+z)) F((\lambda)/ (1+z)) S_y(\lambda) d\lambda}
             \right) \right) \\
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\
          &= 5 \text{log} (1 + z)
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
             - P_x + P_y .
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
             - P_x + P_y \\
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right)
-            + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
-            - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\ 
+            + 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
+            - 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
          &= 2.5 \text{log} \left(
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) .
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) .
 \end{aligned}

### 2025-01-05 src/redshift/supernova.py
Update graphics

@@ -261,7 +261,7 @@ def k_corrections_for_photon_counts_graph(save=False):
 
     axs[1, 0].sharex(axs[1, 1])
     axs[1, 0].sharey(axs[1, 1])
-    axs[1, 0].plot(xs, ps_10, "tab:red")
+    axs[1, 0].plot(xs, ps_10, g)
     axs[1, 0].set_title("Corrected for time dilation")
     axs[1, 0].set_xlabel(r"$\lambda$ (nm)")
     axs[1, 0].set_ylabel("photons")
@@ -273,7 +273,7 @@ def k_corrections_for_photon_counts_graph(save=False):
         ps_10,
         where=[True if 1000 <= x <= 1200 else False for x in xs],
         facecolor="darkred",
-        edgecolor="red",
+        edgecolor="tab:red",
         hatch=r"//",
         label=f"photons/nm = {photon_count:.0f}/200nm = {photon_count // 200:.0f}/nm",
     )
@@ -289,7 +289,7 @@ def k_corrections_for_photon_counts_graph(save=False):
 
     axs[0, 1].sharex(axs[1, 1])
     axs[0, 1].sharey(axs[1, 1])
-    axs[0, 1].plot(xs, ps_01, "tab:red")
+    axs[0, 1].plot(xs, ps_01, g)
     axs[0, 1].set_title("Corrected for redshift")
     axs[0, 1].set_xlabel(r"$\lambda$ (nm)")
     axs[0, 1].set_ylabel("photons")
@@ -301,7 +301,7 @@ def k_corrections_for_photon_counts_graph(save=False):
         ps_01,
         where=[True if 500 <= x <= 600 else False for x in xs],
         facecolor="darkred",
-        edgecolor="red",
+        edgecolor="tab:red",
         hatch=r"//",
         label=f"photons/nm = {photon_count:.0f}/100nm = {photon_count // 100:.0f}/nm",
     )
@@ -335,19 +335,23 @@ def k_corrections_for_photon_counts_graph(save=False):
 
     if save:
         plt.savefig(
-            GRAPHS_DIR / f"K-corrections_for_photon_counts.png",
+            GRAPHS_DIR / f"K-corrections_for_photon_counts.pdf",
             bbox_inches="tight",
         )
-        plt.cla()
+        plt.clf()
 
 def k_equation_flow_graph(save=False):
+    plt.clf()
+    plt.rcParams["text.usetex"] = True
+    #plt.rcParams["hatch.linewidth"] = 4
+
     z = 0.5
[…]

### 2025-01-05 paper/dark_energy_corrections.tex

@@
 \author[0000-0001-6450-3262]{Logan P. Evans}
+\noaffiliation
 
@@
 \begin{figure}
-  \includegraphics[width=\linewidth]{mu_distance_vs_redshift.png}
-  \caption{The relationship between distance and redshift for two treatments of
-  magnitude data. The displayed points are roughly a third of the values in the
-  full SnIa dataset published in \citet{abbott2024}, selected evenly to aid
-  visibility. The $k(z) = 1$ treatment, which represents the uncorrected
-  values, is clearly non-linear while the $k(z) = 1 + z$ treatment which fixes
-  the K-correction redshift error, appears to be linear.}
+  \plotone{lum_distance_vs_redshift.pdf}
+  \caption{The relationship between luminosity distance and redshift for two
+  treatments of magnitude data. The displayed points are roughly a third of the
+  values in the full SnIa dataset published in \citet{abbott2024}, selected
+  evenly to aid visibility. The $k(z) = 1$ treatment, which represents the
+  uncorrected values, is clearly non-linear while the $k(z) = 1 + z$ treatment
+  which fixes the K-correction redshift error, appears to be linear.}
   \label{fig:mu_distance_vs_redshift}
@@
 
-\begin{figure}
-  \includegraphics[width=.75\linewidth, height=0.75\vsize]{k_equation_flow.png}
-  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
-  are able to observe a SnIa in the redshifted observation frame, but we want
-  to compute the magnitude in the rest frame as if no redshift has occurred.
-  This computation starts with $F(\lambda$, the spectral energy density that
-  describes the expected luminosity in the rest frame. Using the SED, we can
-  compute the photon density $F'(\lambda)$ for the rest frame. We show the
-  process of computing $R'(\lambda$, the photon density in the observation
-  frame, in three phases starting at the top right of the figure. First we
-  stretch the photon density, but this step inflates counts. In the second
-  step, we correct for the inflated counts by multiplying by $1/(1+z)$;
-  at this point, the total count equals the total count of $F'(\lambda)$.
-  Finally, in the third step we finish calculating the observation frame photon
-  density $R'(\lambda)$ by accounting for time dilation, which also reduces
-  photon counts by a factor of $1/(1+z)$.  Given the rest frame and
-  observation frame photon densities, we can compute the expected ratio of
-  photons by totalling the area under the curves in the two panels at the
-  bottom of the graph. This example does not show the process of converting
-  photon flux to magnitude, nor does it address the zero-point correction.
-  }
-  \label{fig:k-example}
-\end{figure}
-
 The modern treatment of K-correction is based on the work of \citet{kim1996}.
@@
 collected by a bolometric device for the wavelength $\lambda$.
+
+\begin{figure}
+  \plotone{k_equation_flow.pdf}
+  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
+  are able to observe a SnIa in the redshifted observation frame, but we want
+  to compute the magnitude in the rest frame as if no redshift has occurred.
+  This computation starts with $F(\lambda$, the spectral energy density, which
+  we then convert to $F'(\lambda)$, the photon density for the rest frame. We
+  show the process of computing $R'(\lambda$, the photon density in the
+  observation frame, in three phases starting at the top right of the figure.
+  First we stretch the photon density, but this step inflates counts. In the
+  second step, we correct for the inflated counts by multiplying by $1/(1+z)$;
+  at this point, the total count equals the total count of $F'(\lambda)$.
+  Finally, in the third step we finish calculating the observation frame photon
+  density $R'(\lambda)$ by accounting for time dilation, which also reduces
+  photon counts by a factor of $1/(1+z)$. We can compute the expected ratio of
+  photons by totalling the area under the curves in the bottom two panels. This
+  example does not show the process of converting photon flux to magnitude, nor
+  does it address the zero-point correction.
+  }
+  \label{fig:k-example}
+\end{figure}
 
@@
 
+\begin{figure}
+  \plotone{velocity_vs_distance.pdf}
+  \caption{The relationship between expansion velocity and distance. The slope
+  of this graph demonstrates the Hubble constant. The data for these SnIa
+  observations comes from the Dark Energy Spectroscopic Instrument
+  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
+  dilation by adding $-2.5 log(1 + z)$.
+  }
+\label{fig:expansion}
+\end{figure}
+
 Since the corrected values are approximately linear, we can use them to
@@
 
-The value estimated here, $H_0 \sim 65.94 \pm 1.29$ is highly suspicious
+\begin{figure}
+  \plotone{bootstrapped_H0.pdf}
+  \caption{A histogram of $10{,}000$ bootstrap trials measuring the Hubble constant
+  $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
+  0.0404)$ for SnIa based on data published by \citet{camarena2020}. It then samples,
+  with replacement, a population of supernovae from the dataset published by
+  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
+  technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
+  \sim Norm(65.94, 1.30^2)$.
+  }
+\label{fig:H0bootstrap}
+\end{figure}
+
+The value estimated here, $H_0 \sim 65.94 \pm 1.30$ is highly suspicious
 because of the flipped zero-point corrections, but it is consistent with
@@
 filter, gives the estimate $H_0 \sim 67.8 \pm 1.86$.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{velocity_vs_distance.png}
-  \caption{The relationship between expansion velocity and distance. The slope of this graph demonstrates the Hubble constant.
-  }
-\label{fig:expansion}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{bootstrapped_H0.png}
-  \caption{A histogram of $100{\small,}000$ bootstrap trials measuring the Hubble constant
-  $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
-  0.0404)$ for SnIa based on data published by \citet{camarena2020}. It then samples,
-  with replacement, a population of supernovae from the dataset published by
-  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
-  technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
-  \sim Norm(65.94, 1.29^2)$.
-  }
-\label{fig:H0bootstrap}
-\end{figure}
 

### 2025-01-06 paper/dark_energy_corrections.tex

@@
 We rederive the K-correction equation and discover that the version of the
-equation used to compute magnitudes contains three errors. The oldest of these
-errors traces back nine decades; in 1930 the equation did not correct for
-spectral bandwidth stretching, followed by a rederivation in 1968 that
-accounted for spectral bandwidth stretching but did not correct for time
-dilation. Two new errors were introduced in 1996, one of which causes
+equation that is commonly used to calculate magnitudes contains three errors.
+The oldest of these errors traces back nine decades; in 1930 the equation did
+not correct for spectral bandwidth stretching, followed by a rederivation in
+1968 that accounted for spectral bandwidth stretching but did not correct for
+time dilation. Two new errors were introduced in 1996, one of which causes
 systematic distance biases by inverting the zero-point correction term. We
@@
 
-The first formal derivation of K-correction was performed by
-\citet{tolman1930}, but it did not account for spectral bandwidth stretching,
-one of the dimming effects of redshift. An alternative K-correction was
-correctly derived by \citet{desitter1934}. However, in \citet{hubble1935}, the
-discrepancy was noted yet dismissed. \citet{oke1968} rederived the K-correction
-equation.  They accounted for spectral bandwidth stretching, but they did not
-account for time dilation, one of the other dimming effects of redshift. The
-paper by \citet{kim1996}, which is the basis for modern implementations of
-K-correction, extended the work of \citet{oke1968} to handle additional
-cross-filter comparisons and added a term that was intended to address
-zero-point corrections. This history is explored in more depth in Section
+\citet{tolman1930} published the first formal derivation of K-correction, but
+he did not account for spectral bandwidth stretching, one of the dimming
+effects of redshift. An alternative K-correction was correctly derived by
+\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy was noted
+yet dismissed. \citet{oke1968} rederived the K-correction equation where they
+accounted for spectral bandwidth stretching, but they did not account for time
+dilation, one of the other dimming effects of redshift. The paper by
+\citet{kim1996}, which is the basis for modern implementations of K-correction,
+extended the work of \citet{oke1968} to handle additional cross-filter
+comparisons and added a term that was intended to address zero-point
+corrections. This history is explored in more depth in Section
 \ref{sec:history}.
@@
 constant $\Lambda$ and dark energy in order to explain the non-linear
-distance-redshift graph. We will show in Section \ref{sec:tension} that
-correcting the flaw with K-correction leads to a linear graph that does not
+distance-redshift graph. We will show in Section \ref{sec:conclusions} that
+correcting the flaws with K-correction leads to a linear graph that does not
 need to rely on a cosmological constant.
@@
 $H_0$ that is based on measurements of the cosmic microwave background (CMB).
-CMB-based computations of $H_0$ has made it evident that something was missing
+CMB-based computations of $H_0$ have made it evident that something is missing
 with our understanding of cosmology because this technique produces a
 significantly different value than when the constant is derived using SnIa.  As
-we will discuss in Section \ref{sec:tension}, fixing the error with
+we will discuss in Section \ref{sec:conclusions}, fixing the errors with
 K-correction produces a measurement of the Hubble constant that is compatible
@@
   values in the full SnIa dataset published in \citet{abbott2024}, selected
-  evenly to aid visibility. The $k(z) = 1$ treatment, which represents the
-  uncorrected values, is clearly non-linear while the $k(z) = 1 + z$ treatment
-  which fixes the K-correction redshift error, appears to be linear.}
+  evenly to aid visibility. The red $k(z) = 1$ treatment, which represents the
+  uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
+  treatment, which fixes the K-correction redshift error, appears to be linear.}
   \label{fig:mu_distance_vs_redshift}
@@
 
-However, redshifting light dims an observation in three ways:
+However, redshifting dims the luminosity of an observation in three ways:
 
@@
 
-  \item The bandwidth stretches. If a rest frame observes photons
-  between the wavelengths of 400nm and 401nm, then a redshift of $z = 1$
-  stretches the wavelength from 800nm to 802nm.
+  \item The bandwidth stretches. If the rest frame observes photons in the
+  bandwidth from 400nm and 401nm, then a redshift of $z = 1$ stretches the
+  wavelengths to the bandwidth from 800nm to 802nm. The number of photons per
+  bandwidth is reduced by a factor of $1 / (1+z)$.
 
   \item Cosmological time dilation reduces the rate at which photons arrive.
+  The number of photons that arive per second is reduced by a factor of $1 / (1+z)$.
 \end{itemize}
@@
 measured in an observation filter $y$ and compute the magnitude in the target
-filter $y$.
+filter $x$.
 
-The first mathematical treatments of K-correction was performed by
+The first mathematical treatment of K-correction was performed by
 \citet{tolman1930}. However, when Tolman made his derivation, he did not
-consider the effects of a spectrum that is stretched due to redshift. See
-the top two panels of Figure \ref{fig:k-example} for an example of this effect.
+consider the effects of a spectrum that is stretched due to redshift.
 
@@
 
-A year later, \citet{hubble1935} published a similar set of calculations for
-K-correction, but these equations used $(1 + z)^2$ instead of the $(1 + z)^3$
-correction term used by de Sitter. They started their derivation by copying the
-incorrect equation from 1930. After their derivation, they noted:
+A year later, \citet{hubble1935} published a similar set of calculations where they noted:
 
@@
 
-The Hubble K-correction with the incorrect correction term have been used ever
-since.
+\noindent However, even though they considered all three dimming effects of
+redshift, they started their derivation by copying the incorrect equation from
+1930. The incorrect correction term has been used ever since.
 
-By \citet{oke1968}, the two factors of $(1 + z)$ were attributed to the change
-in energy and to the spectral bandwidth elongation, which leaves time dilation
-as the factor that was omitted. A graph that demonstrates why it is essential to
-correct for both the spectra bandwidth stretching and time dilation is presented
-in Figure \ref{fig:k-example}.
+In a paper published by \citet{oke1968}, the two factors of $(1 + z)$ were
+attributed to the change in energy and to the spectral bandwidth elongation,
+which leaves time dilation as the factor that was omitted.
 
@@
 the blue $B$ and visible $V$ bands. It also introduced a term that deals with
-the zero-point for the actual filters. In the modern day, filters measure the
-photon flux as opposed to the energy flux. Historically, bolometric devices
-would measure the energy flux, but modern charge-coupled device (CCD) cameras
+the zero-point for the actual filters. Historically, bolometric devices would
+measure the energy flux, but modern charge-coupled device (CCD) cameras
 effectively measure the photon flux.
@@
 With modern CCD cameras, a telescope observation consists of a single value
-$\mathcal{F}_x$ erg/s, which represents the energy collected in filter $x$ per
-second. A summary of how this works is provided by \citet{lesser2015}.
+$\mathcal{F}_y$ erg/s, which represents the energy collected per second in
+filter $y$. A summary of how this works is provided by \citet{lesser2015}.
 Photogenerated electrons are collected in potential wells, which means that the
@@
 
-However, this equation is misleading and error prone. We will want to use it to
+\noindent However, this equation is misleading and error prone. We will want to use it to
 help calculate the amount of flux in an observation filter at the redshifted
@@
 \begin{itemize}
+  \item All wavelengths are increased by a factor of $1 + z$. When we integrate
+  $R'$ from wavelength $\lambda_a$ to wavelength $\lambda_b$, the values
+  correspond to the wavelengths $\lambda_a / (1+z)$ to $\lambda_b / (1+z)$ in
+  $F'$. We will integrate over a width of $\lambda_b - \lambda_a$, but
+  $F'(\lambda / (1+z))$ will refer to values in a width of
+  $(\lambda_b - \lambda_a) / (1+z)$.
+
+  In order to account for this spectral bandwidth stretching effect, we will need
+  to multiply $F'$ by a second factor of $1/(1+z)$.
   \item The stretching of space increases the distance between photons while
@@
   $F'$ by $1/(1+z)$.
-
-  \item All wavelengths are changed by a factor of $1 + z$. When we integrate
-  $R'$ from wavelength $\lambda_a$ to wavelength $\lambda_b$, the values
-  correspond to the wavelengths $\lambda_a / (1+z)$ to $\lambda_b / (1+z)$ in
-  $F'$. We will integrate over a width of $\lambda_b - \lambda_a$, but
-  $F'(\lambda / (1+z))$ will refer to values in a width of
-  $(\lambda_b - \lambda_a) / (1+z)$.
-
-  In order to account for this spectral bandwidth stretching effect, we will need
-  to multiply $F'$ by a second factor of $1/(1+z)$.
 \end{itemize}
@@
 
-We deliberately do not combine all of the factors of $1+z$ together because
+\noindent We deliberately do not combine all of the factors of $1+z$ together because
 this form is more natural to implement in code.
@@
 
-The limits of integration are technically from 0 to $\infty$, but these are
+\noindent The limits of integration are technically from 0 to $\infty$, but these are
 usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
@@
 
-$P_x$ represents the zero-point for the filter $x$ on some particular
+\noindent $P_x$ represents the zero-point for the filter $x$ on some particular
 telescope. In order to use consistent magnitude values across telescopes that
@@
 Now that we have the identities in Equations \ref{eq:flux_definition} and
-\ref{eq:flux2mag} we will change directions and look at the definition of
+\ref{eq:flux2mag}, we will change directions and look at the definition of
 K-correction $K_{xy}$. This value allows us to make an observation in filter
@@
 
-Note that this substitution omits the minus ($-$) sign that we used on a
+\noindent Note that this substitution omits the minus ($-$) sign that we used on a
 similar substitution for $P_x$.
@@
 
-Finally, we can use Equation \ref{eq:k_substitution} to convert the flux $K'_{xy}$ back
+Finally, we can use Equation \ref{eq:k_substitution} to convert $K'_{xy}$ back
 into the magnitude $K_{xy}$:
@@
 
-  This effect by itself can alter estimates of $H_0$ by several km s$^{-1}$
-  Mpc$^{-1}$.  While we present an estimate of the Hubble constant in Figure
+  This effect by itself can alter estimates of $H_0$ by several percent. While
+  we present an estimate of the Hubble constant in Figure
   \ref{fig:H0bootstrap}, we are not terribly confident in the numbers because
@@
 
-\section{Dark energy and the Hubble tension}
-\label{sec:tension}
-
-As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
-are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
-relationship between redshift and luminosity distance. This is in accordance
-with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
-is no visual acceleration.
+\section{Conclusions}
+\label{sec:conslusions}
 
@@
 
-Since the corrected values are approximately linear, we can use them to
-estimate the Hubble constant $H_0$. This is demonstrated in Figure
-\ref{fig:expansion}. Furthermore, we performed a bootstrap calculation to
-estimate the distribution of $H_0$ estimates in Figure \ref{fig:H0bootstrap}.
+As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
+are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
+relationship between redshift and luminosity distance. This is in accordance
+with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
+is no visual acceleration. Since the corrected values are approximately linear,
+we can use them to estimate the Hubble constant $H_0$. This is demonstrated in
+Figure \ref{fig:expansion}. Furthermore, we performed a bootstrap calculation
+to estimate the distribution of $H_0$ estimates in Figure
+\ref{fig:H0bootstrap}.
 
@@
   technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
-  \sim Norm(65.94, 1.30^2)$.
+  \sim Norm(65.94, 1.3^2)$.
   }
@@
 
-The value estimated here, $H_0 \sim 65.94 \pm 1.30$ is highly suspicious
+The value estimated here, $H_0 = 65.94 \pm 1.3$ is highly suspicious
 because of the flipped zero-point corrections, but it is consistent with
 estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
-CMB value of $H_0 \sim 67.27 \pm 0.6$, and the one sigma error bars overlap. It
+CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap. It
 is interesting to note that restricting the Dark Energy Survey observations of
@@
 small enough redshift that all observations will have been made with the same
-filter, gives the estimate $H_0 \sim 67.8 \pm 1.86$.
-
-\section{Conclusions}
+filter, gives the estimate $H_0 = 67.8 \pm 1.9$.
 

### 2025-01-06 paper/dark_energy_corrections.tex
Fix missing parens

@@
   to compute the magnitude in the rest frame as if no redshift has occurred.
-  This computation starts with $F(\lambda$, the spectral energy density, which
+  This computation starts with $F(\lambda)$, the spectral energy density, which
   we then convert to $F'(\lambda)$, the photon density for the rest frame. We
-  show the process of computing $R'(\lambda$, the photon density in the
+  show the process of computing $R'(\lambda)$, the photon density in the
   observation frame, in three phases starting at the top right of the figure.

### 2025-01-09 paper/dark_energy_corrections.tex
Edits

--- 2025-01-06 paper/dark_energy_corrections.tex
@@
 \begin{abstract}
-We rederive the K-correction equation and discover that the version of the
-equation that is commonly used to calculate magnitudes contains three errors.
-The oldest of these errors traces back nine decades; in 1930 the equation did
-not correct for spectral bandwidth stretching, followed by a rederivation in
-1968 that accounted for spectral bandwidth stretching but did not correct for
-time dilation. Two new errors were introduced in 1996, one of which causes
-systematic distance biases by inverting the zero-point correction term. We
-conclude that properly correcting apparent magnitudes for redshift resolves two
-of the preeminent mysteries in cosmology: first, dark energy is not supported
-by observations of Type Ia supernovae and second, the Hubble tension is due to
-the errors in the K-correction equation.
+We rederive the K-correction equation and discover that the version commonly
+used to calculate magnitudes contains three errors, and the oldest of these errors
+traces back nine decades. The 1930 the equation did not correct for spectral
+bandwidth stretching. Two new errors were introduced in 1996, one of which
+causes systematic distance biases by inverting the zero-point correction term.
+We conclude that properly correcting apparent magnitudes for redshift resolves
+two of the preeminent mysteries in cosmology: first, dark energy is not
+supported by observations of Type Ia supernovae and second, the Hubble tension
+is due to the errors in the K-correction equation.
 \end{abstract}
@@
 
-The effect of using an incorrect magnitude for SnIa is that we think objects
-are farther away than they really are, and the effect compounds for greater
-distances. Up until \citet{riess1998}, we did not have distant enough
+The effect of using an incorrect redshift correction for SnIa is that we think
+objects are farther away than they really are; this effect compounds for
+greater distances. Up until \citet{riess1998}, we did not have distant enough
 observations for this error to matter much for cosmological models, but by the
-late 1990s, it became clear that our measurements for distance and redshift were
-not linear. This realization led to a model that utilized a cosmological
+late 1990s, it became clear that our measurements for distance and redshift
+were not linear. This realization led to a model that utilized a cosmological
 constant $\Lambda$ and dark energy in order to explain the non-linear
@@
 describes how quickly the universe is expanding. However, \citet{riess1998}
-and \citet{perlmutter1999} presented evidence that there isn't a linear
+and \citet{perlmutter1999} presented evidence that there is not a linear
 relationship between redshift and distance, but instead, distant objects are
@@
 acceleration of the universe is faster today than it was for old observations.
-Previously the cause of this phenomenon was unknown and was referred to as dark
-energy.
+The cause of this phenomenon was unknown and was referred to as dark energy.
 
@@
   values in the full SnIa dataset published in \citet{abbott2024}, selected
-  evenly to aid visibility. The red $k(z) = 1$ treatment, which represents the
-  uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
-  treatment, which fixes the K-correction redshift error, appears to be linear.}
+  with uniform redshift spacing to aid visibility. The red $k(z) = 1$ treatment,
+  which represents the uncorrected values, is clearly non-linear while the blue
+  $k(z) = 1 + z$ treatment, which fixes the K-correction redshift error,
+  appears to be linear.}
   \label{fig:mu_distance_vs_redshift}
@@
   \plotone{k_equation_flow.pdf}
-  \caption{The ratio $K'_{xy}$ is the crux of the K-correction algorithm. We
-  are able to observe a SnIa in the redshifted observation frame, but we want
-  to compute the magnitude in the rest frame as if no redshift has occurred.
-  This computation starts with $F(\lambda$, the spectral energy density, which
-  we then convert to $F'(\lambda)$, the photon density for the rest frame. We
-  show the process of computing $R'(\lambda$, the photon density in the
-  observation frame, in three phases starting at the top right of the figure.
-  First we stretch the photon density, but this step inflates counts. In the
-  second step, we correct for the inflated counts by multiplying by $1/(1+z)$;
-  at this point, the total count equals the total count of $F'(\lambda)$.
-  Finally, in the third step we finish calculating the observation frame photon
-  density $R'(\lambda)$ by accounting for time dilation, which also reduces
-  photon counts by a factor of $1/(1+z)$. We can compute the expected ratio of
-  photons by totalling the area under the curves in the bottom two panels. This
-  example does not show the process of converting photon flux to magnitude, nor
-  does it address the zero-point correction.
+  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
+  report in the target filter divided by the number of photons we measure in
+  the observation filter.  Deriving this value starts with $F(\lambda)$, the
+  spectral energy density, which we then convert to $F'(\lambda)$, the photon
+  density for the rest frame.  Starting at the top right corner of the figure,
+  we show the process of computing $R'(\lambda)$, the photon density in the
+  observation frame, in three phases. First we stretch the photon density, but
+  this step inflates counts. In the second step, we correct for the inflated
+  counts by multiplying by $1/(1+z)$; at this point, the total count equals the
+  total count of $F'(\lambda)$. Finally, in the third step we finish
+  calculating the observation frame photon density $R'(\lambda)$ by accounting
+  for time dilation, which also reduces photon counts by a factor of $1/(1+z)$.
+  We can compute the expected ratio of photons by totalling the area under the
+  curves in the bottom two panels.
   }
@@
 
-\noindent However, this equation is misleading and error prone. We will want to use it to
-help calculate the amount of flux in an observation filter at the redshifted
-wavelength $\lambda \times (1 + z)$. In other words, we want to produce the
-photon density function $R'$ that is the redshifted version of $F'$.
-Redshifting the photon density does two things:
+\noindent However, this equation is misleading and error prone. We will want to
+use it to help calculate the amount of flux in an observation filter at the
+redshifted wavelength $\lambda \times (1 + z)$. In other words, we want to
+produce the photon density function $R'$ that is the redshifted version of
+$F'$. Redshifting the photon density does two things:
 
@@
 
-  In order to account for this spectral bandwidth stretching effect, we will need
-  to multiply $F'$ by a second factor of $1/(1+z)$.
+  In order to account for this spectral bandwidth stretching effect, we
+  multiply $F'$ by $1/(1+z)$.
+
   \item The stretching of space increases the distance between photons while
-  they are traveling. This phenomenon appears to an observer like time
+  they are traveling. To an observer, this phenomenon appears like time
   dilation, although cosmological time dilation is due to a different mechanism
@@
 
-  In order to account for cosmological time dilation, we will need to multiply
-  $F'$ by $1/(1+z)$.
+  In order to account for cosmological time dilation, we multiply $F'$ by a
+  second factor of $1/(1+z)$.
 \end{itemize}
@@
 $x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
-sensitivity $S_x(\lambda)$, which represents the proportion of photons filter $x$
-will measure at wavelength $\lambda$. We then need to sum over all wavelengths,
-which is expressed with the equation
+the sensitivity $S_x(\lambda)$, which represents the proportion of photons with
+wavelength $\lambda$ that filter $x$ will measure. We then need to sum over
+all wavelengths, which is expressed with the equation
 
@@
 \end{equation}
-
-\noindent The limits of integration are technically from 0 to $\infty$, but these are
-usually not written because the sensitivity $S(\lambda)$ is 0 for wavelengths
-outside of a filter's bandpass.
 
@@
 \section{Conclusions}
-\label{sec:conslusions}
+\label{sec:conclusions}
 
@@
   of this graph demonstrates the Hubble constant. The data for these SnIa
-  observations comes from the Dark Energy Spectroscopic Instrument
-  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
-  dilation by adding $-2.5 log(1 + z)$.
+  observations comes from the Dark Energy Survey \citep{vincenzi2024}, but the
+  magnitudes are corrected to account for time dilation by adding
+  $-2.5 log(1 + z)$.
   }

### 2025-01-10 paper/dark_energy_corrections.tex
More revisions.

@@
 We rederive the K-correction equation and discover that the version commonly
-used to calculate magnitudes contains three errors, and the oldest of these errors
-traces back nine decades. The 1930 the equation did not correct for spectral
-bandwidth stretching. Two new errors were introduced in 1996, one of which
-causes systematic distance biases by inverting the zero-point correction term.
-We conclude that properly correcting apparent magnitudes for redshift resolves
-two of the preeminent mysteries in cosmology: first, dark energy is not
-supported by observations of Type Ia supernovae and second, the Hubble tension
-is due to the errors in the K-correction equation.
+used to calculate magnitudes contains multiple errors. The oldest of these
+errors traces back to 1930 and two new errors were introduced in 1996. We
+conclude that properly correcting apparent magnitudes for redshift resolves two
+of the preeminent mysteries in cosmology: first, dark energy is not supported
+by observations of Type Ia supernovae and second, the Hubble tension is due to
+the errors in the K-correction equation.
 \end{abstract}
@@
 involves taking a measurement of redshifted light in our observation frame and
-then calculating the rest frame magnitude as if no redshift had occurred. It is
-standard to report rest frame magnitudes in the $B$ filter, which is sensitive to
-blue light, regardless of the filter used to take measurements in the
-observation frame. The equation that converts from an observation frame
-magnitude to a rest frame magnitude in the $B$ filter is called K-correction.
+then calculating the rest frame magnitude as if no redshift had occurred. The
+equation that converts from an observation frame magnitude to a rest frame
+magnitude is called K-correction.
 
@@
 effects of redshift. An alternative K-correction was correctly derived by
-\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy was noted
-yet dismissed. \citet{oke1968} rederived the K-correction equation where they
-accounted for spectral bandwidth stretching, but they did not account for time
-dilation, one of the other dimming effects of redshift. The paper by
-\citet{kim1996}, which is the basis for modern implementations of K-correction,
-extended the work of \citet{oke1968} to handle additional cross-filter
-comparisons and added a term that was intended to address zero-point
-corrections. This history is explored in more depth in Section
+\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy was
+briefly discussed yet dismissed. \citet{oke1968} rederived the K-correction
+equation where they accounted for spectral bandwidth stretching, but they did
+not account for time dilation, one of the other dimming effects of redshift.
+The paper by \citet{kim1996}, which is the basis for modern implementations of
+K-correction, extended the work of \citet{oke1968} to handle additional
+cross-filter comparisons and added a term that was intended to address
+zero-point corrections. This history is explored in more depth in Section
 \ref{sec:history}.
@@
 distance-redshift graph. We will show in Section \ref{sec:conclusions} that
-correcting the flaws with K-correction leads to a linear graph that does not
+correcting the flaws of K-correction leads to a linear graph that does not
 need to rely on a cosmological constant.
@@
 
-\section{A brief history of K-correction}
+\section{
+  A brief history of K - correction
+}
 \label{sec:history}
@@
   \caption{The relationship between luminosity distance and redshift for two
-  treatments of magnitude data. The displayed points are roughly a third of the
-  values in the full SnIa dataset published in \citet{abbott2024}, selected
-  with uniform redshift spacing to aid visibility. The red $k(z) = 1$ treatment,
-  which represents the uncorrected values, is clearly non-linear while the blue
-  $k(z) = 1 + z$ treatment, which fixes the K-correction redshift error,
-  appears to be linear.}
+  treatments of magnitude data. The red $k(z) = 1$ treatment, which represents
+  the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
+  treatment, which fixes the K-correction redshift error, appears to be linear.
+  The displayed points are roughly a third of the values in the full SnIa
+  dataset published in \citet{abbott2024}, selected with uniform redshift
+  spacing to aid visibility. }
   \label{fig:mu_distance_vs_redshift}
@@
 SnIa are used to explore the relationship between distance and redshift because
-these events always happen in similar ways, which keeps the absolute brightness
-roughly constant. An analogy is to imagine someone walking in the dark and
-lighting matches. If we know how brightly a match burns at a known distance, we
-can estimate the distance to any match by measuring the apparent brightness
-before applying some geometry.
+these events have a roughly constant absolute magnitude, which allows us to use
+the apparent magnitude to estimate distance. An analogy is to imagine someone
+walking in the dark and lighting matches. If we know how brightly a match burns
+at a known distance, we can estimate the distance to any match by measuring the
+apparent brightness before applying some geometry.
 
@@
 
-A few years later, \citet{desitter1934}, discussed all three issues that reduce
+A few years later, \citet{desitter1934} discussed all three issues that reduce
 the observed magnitude of a distant observation. The correction for each of
@@
 The modern treatment of K-correction is based on the work of \citet{kim1996}.
-This work extended the calculations of K-correction to extend to filters beyond
-the blue $B$ and visible $V$ bands. It also introduced a term that deals with
-the zero-point for the actual filters. Historically, bolometric devices would
+This work extended the work of \citet{oke1968} to apply to filters beyond the
+blue $B$ and visible $V$ bands. It also introduced a term that deals with the
+zero-point for the actual filters. Historically, bolometric devices would
 measure the energy flux, but modern charge-coupled device (CCD) cameras
-effectively measure the photon flux.
+effectively measure the photon flux, so \citet{kim1996} derived a form of the
+K-correction equation that uses photon flux.
 
@@
 
+The K-correction $K_{xy}$ uses a spectral energy density $F$ template that
+specifies the expected spectrum for a SnIa observation. It also uses the
+observed redshift $z$ and the observed photon flux magnitude $m_y$.
+
 With modern CCD cameras, a telescope observation consists of a single value
 $\mathcal{F}_y$ erg/s, which represents the energy collected per second in
-filter $y$. A summary of how this works is provided by \citet{lesser2015}.
-Photogenerated electrons are collected in potential wells, which means that the
-measured energy is proportional to the number of photons. However, we need to
-calculate the expected number of photons collected by using a spectral energy
-density function $F$. The value $F(\lambda)$ gives the amount of energy
-collected by a bolometric device for the wavelength $\lambda$.
+filter $y$. Photogenerated electrons are collected in potential wells, which
+means that the energy measured in this filter is proportional to the number of
+photons \citep{lesser2015}. However, we need to calculate the expected number
+of photons collected by using a spectral energy density function $F$.
 
@@
   spectral energy density, which we then convert to $F'(\lambda)$, the photon
-  density for the rest frame.  Starting at the top right corner of the figure,
-  we show the process of computing $R'(\lambda)$, the photon density in the
-  observation frame, in three phases. First we stretch the photon density, but
-  this step inflates counts. In the second step, we correct for the inflated
-  counts by multiplying by $1/(1+z)$; at this point, the total count equals the
-  total count of $F'(\lambda)$. Finally, in the third step we finish
-  calculating the observation frame photon density $R'(\lambda)$ by accounting
-  for time dilation, which also reduces photon counts by a factor of $1/(1+z)$.
-  We can compute the expected ratio of photons by totalling the area under the
-  curves in the bottom two panels.
+  density for the rest frame. Starting at the top right corner of the figure we
+  show three steps used to compute $R'(\lambda)$, the photon density in the
+  observation frame. We first stretch the photon density, but this step
+  inflates counts. In the second step, we correct for the inflated counts by
+  multiplying by $1/(1+z)$; at this point, the total count equals the total
+  count of $F'(\lambda)$. Finally, in the third step we finish calculating the
+  observation frame photon density $R'(\lambda)$ by accounting for time
+  dilation, which also reduces photon counts by a factor of $1/(1+z)$. We can
+  compute the expected ratio of photons by totalling the area under the curves
+  in the bottom two panels.
   }
@@
 \noindent However, this equation is misleading and error prone. We will want to
-use it to help calculate the amount of flux in an observation filter at the
-redshifted wavelength $\lambda \times (1 + z)$. In other words, we want to
-produce the photon density function $R'$ that is the redshifted version of
-$F'$. Redshifting the photon density does two things:
+use it to help calculate the flux in an observation filter at the redshifted
+wavelength $\lambda \times (1 + z)$. In other words, we want to produce the
+photon density function $R'$ that is the redshifted version of $F'$.
+Redshifting the photon density does two things:
 
@@
 
-  In order to account for this spectral bandwidth stretching effect, we
+  In order to account for the spectral bandwidth stretching effect, we
   multiply $F'$ by $1/(1+z)$.
@@
 
-In order to calculate the amount of flux $\mathcal{F}_x$ measured in filter
-$x$, we need to compute the photon density $F'(\lambda)$ and multiply it by
-the sensitivity $S_x(\lambda)$, which represents the proportion of photons with
-wavelength $\lambda$ that filter $x$ will measure. We then need to sum over
-all wavelengths, which is expressed with the equation
+In order to calculate the flux $\mathcal{F}_x$ measured in filter $x$, we need
+to compute the photon density $F'(\lambda)$ and multiply it by the sensitivity
+$S_x(\lambda)$, which represents the proportion of photons with wavelength
+$\lambda$ that filter $x$ will measure. We then sum over all wavelengths, which
+is expressed with the equation
 
@@
 
-We will also use the energy flux $\mathcal{F}$ to magnitude $m$ formula:
+We will also use the flux $\mathcal{F}$ to magnitude $m$ formula:
 
@@
 
-It is useful to consider whether the term $P'_y / P'_x$ is correct or if
-it should be inverted, but if we rewrite Equation \ref{eq:as_flux} as
-
-\begin{equation}
-  \mathcal{F}_x \times P'_x = \mathcal{F}_y \times P'_y \times K'_{xy}
-\end{equation}
-
-\noindent then the meaning becomes more clear. The left side, $\mathcal{F}_x
-\times P'_x$, is the rate of photon collection for an idealized telescope in
-filter $x$ while $\mathcal{F}_y \times P'_y$ is the rate of photon collection
-for an idealized telescope in filter $y$. We observe the value $\mathcal{F}_y
-\times P'_y$ and want to use the fudge factor $K'_{xy}$ to produce the value
-$\mathcal{F}_x \times P'_x$.
-
-We can isolate $K'_{xy}$ and then use Equation \ref{eq:flux_definition} to expand
+\noindent We can isolate $K'_{xy}$ and then use Equation \ref{eq:flux_definition} to expand
 
@@
 
-We now use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
+\noindent We now use Equations \ref{eq:redshifted_density} and \ref{eq:flux_definition}
 to calculate the fluxes $\mathcal{F}_x$ and $\mathcal{F}_y$ in terms of the
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z) F(\lambda / (1+z)) S_y(\lambda) d\lambda} .
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} .
 \end{aligned}
@@
 
-Finally, we can use Equation \ref{eq:k_substitution} to convert $K'_{xy}$ back
-into the magnitude $K_{xy}$:
+Finally, we use Equation \ref{eq:k_substitution} to convert $K'_{xy}$ back into
+the magnitude $K_{xy}$:
 
@@
 
-In order to fully compare our derivation against Equation \ref{eq:kim}, we need
-to use the identity
+In order to fully compare our derivation against Equation \ref{eq:kim} (from
+\citet{kim1996}) we need to use the identity
 
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\
+                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\ \ \
             + 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
@@
   \item The sign is different for the first term. This will have a subtle but
-  frustrating effect for real measurements. The zero-point values are usually,
-  but not always, close to zero. As we observe more distant supernovae, it is
-  useful to switch our observational filter to a filter that is sensitive to
-  longer wavelengths. Each observation filter will have its own small bias.
+  frustrating effect for real measurements. The zero-point values for the two
+  filters are usually, but not always, roughly equal. As we observe more
+  distant supernovae, it is useful to switch our observational filter to a
+  filter that is sensitive to longer wavelengths, but each observation filter will
+  have its own small bias.
 
@@
   \ref{fig:H0bootstrap}, we are not terribly confident in the numbers because
-  we were unable to correct for the zero-point errors, or verify that these
-  errors may not exist.
+  we were unable to correct the zero-point errors, or verify that these errors
+  may not exist.
 
@@
   multiplied by $5$ here. This is the manifestation of the error in
-  \citet{tolman1930}.
+  \citet{tolman1930} and leads to the conclusion that the expansion of the
+  universe is accelerating.
 
@@
   Based on an inspection of the SN(oo)py software package presented by
-  \citet{snpy}, this error is ignored and software package authors implement it
-  as intended, not precisely as written.
+  \citet{burns2010} and the SNANA software package presented by
+  \citet{kessler2009}, this error is ignored and software package authors
+  implement it as intended, not precisely as written.
 \end{itemize}
@@
 is no visual acceleration. Since the corrected values are approximately linear,
-we can use them to estimate the Hubble constant $H_0$. This is demonstrated in
+we can use them to estimate the Hubble constant $H_0$ which is demonstrated in
 Figure \ref{fig:expansion}. Furthermore, we performed a bootstrap calculation
@@
   $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
-  0.0404)$ for SnIa based on data published by \citet{camarena2020}. It then samples,
-  with replacement, a population of supernovae from the dataset published by
-  \citet{abbott2024}. Finally, it uses the non-parametric linear regression
-  technique described by \citet{siegel1982}. The result of the bootstrap is $H_0
-  \sim Norm(65.94, 1.3^2)$.
+  0.0404)$ \citep{camarena2020} before it samples, with replacement, a
+  population of supernovae from the dataset published by \citet{abbott2024}.
+  Finally, it uses the non-parametric linear regression technique described by
+  \citet{siegel1982}. The result of the bootstrap is $H_0 \sim Norm(65.94, 1.3^2)$.
   }
@@
 SnIa \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
-small enough redshift that all observations will have been made with the same
-filter, gives the estimate $H_0 = 67.8 \pm 1.9$.
+small enough redshift that most of the observations will have been made with
+the same filter, gives the estimate $H_0 = 67.8 \pm 1.9$.
 

### 2025-02-01 paper/dark_energy_corrections.tex

@@
-\documentclass[linenumbers]{aastex631}
+\documentclass[aps,prl,reprint,amsmath]{revtex4-2}
 
-\usepackage{amsmath}
-
-\shorttitle{Correcting K-correction}
-\shortauthors{Evans}
+\usepackage{graphicx}
 
@@
 
-\correspondingauthor{Logan P. Evans}
+\author{Logan P. Evans}
  \email{loganpevans@gmail.com}
+ \noaffiliation
 
-\author[0000-0001-6450-3262]{Logan P. Evans}
-\noaffiliation
+\date{\today}
 
@@
 
-%% https://astrothesaurus.org
-\keywords{Type Ia supernovae(1728) --- Apparent magnitude(59)}
+\maketitle
 
@@
 
-\section{
-  A brief history of K - correction
-}
+\section{A brief history of K-correction}
 \label{sec:history}
@@
 \begin{figure}
-  \plotone{lum_distance_vs_redshift.pdf}
+  \includegraphics[width=\columnwidth]{lum_distance_vs_redshift.pdf}
   \caption{The relationship between luminosity distance and redshift for two
-  treatments of magnitude data. The red $k(z) = 1$ treatment, which represents
+  treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
   the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
@@
   \begin{equation}
+  \begin{aligned}
   \label{eq:kim}
     K_{xy} =
-      -2.5\text{log} \left(
+      &-2.5\text{log} \left(
         \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
-             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right)
-      + 2.5\text{log}(1+z)
-      + 2.5\text{log}\left(
+             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) \\
+      &+ 2.5\text{log}(1+z) \\
+      &+ 2.5\text{log}\left(
         \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
              {\int \lambda F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
+  \end{aligned}
   \end{equation}
@@
 \begin{figure}
-  \plotone{k_equation_flow.pdf}
+  \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
   \caption{The value $K'_{xy}$ is equal to the number of photons we want to
@@
       &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
-      &= -2.5 \text{log}(\mathcal{F}_y)
-         - 2.5 \text{log}(P'_y)
-         - 2.5 \text{log}(K'_{xy})
-         + 2.5 \text{log}(P_x) \\
-      &= -2.5 \left(
-         \text{log}(\mathcal{F}_y)
-         + \text{log}(K'_{xy})
-         + \text{log}(P'_y)
-         - \text{log}(P'_x)
-        \right) \\
+      &= -2.5 \text{log}(\mathcal{F}_y) \\
+         &\qquad - 2.5 \text{log}(P'_y) \\
+         &\qquad - 2.5 \text{log}(K'_{xy}) \\
+         &\qquad + 2.5 \text{log}(P'_x) \\
+      &= -2.5 \biggl(\text{log}(\mathcal{F}_y) + \text{log}(K'_{xy}) \\
+         &\qquad\qquad + \text{log}(P'_y) - \text{log}(P'_x)
+        \biggr) \\
       &= -2.5 \text{log}\left(
@@
               \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
-                   {\int F'(\lambda / (1+z)) \times (1 / (1 + z)^2) S_y(\lambda) d\lambda} \\
+                   {\int F'\left(\frac{\lambda}{1+z}\right) \times \left(\frac{1}{1 + z}\right)^2 S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
-              \frac{\int (\lambda / hc) F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / ((1+z)hc)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \\
+              \frac{\int \left(\frac{\lambda}{hc}\right) F(\lambda) S_x(\lambda) d\lambda}
+                   {\int \left(\frac{\lambda}{(1+z)hc}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} .
+                   {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
 \end{aligned}
@@
 
-  This effect by itself can alter estimates of $H_0$ by several percent. While
-  we present an estimate of the Hubble constant in Figure
-  \ref{fig:H0bootstrap}, we are not terribly confident in the numbers because
-  we were unable to correct the zero-point errors, or verify that these errors
-  may not exist.
-
   \item The second term is multiplied by $2.5$ in \citet{kim1996}, but is
@@
 \begin{figure}
-  \plotone{velocity_vs_distance.pdf}
+  \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
   \caption{The relationship between expansion velocity and distance. The slope
@@
 we can use them to estimate the Hubble constant $H_0$ which is demonstrated in
-Figure \ref{fig:expansion}. Furthermore, we performed a bootstrap calculation
-to estimate the distribution of $H_0$ estimates in Figure
-\ref{fig:H0bootstrap}.
-
-\begin{figure}
-  \plotone{bootstrapped_H0.pdf}
-  \caption{A histogram of $10{,}000$ bootstrap trials measuring the Hubble constant
-  $H_0$. Each trial samples an absolute magnitude $M \sim Norm(-19.2334,
-  0.0404)$ \citep{camarena2020} before it samples, with replacement, a
-  population of supernovae from the dataset published by \citet{abbott2024}.
-  Finally, it uses the non-parametric linear regression technique described by
-  \citet{siegel1982}. The result of the bootstrap is $H_0 \sim Norm(65.94, 1.3^2)$.
-  }
-\label{fig:H0bootstrap}
-\end{figure}
+Figure \ref{fig:expansion}.
 

### 2025-02-03 src/redshift/supernova.py
Update the distance definition

@@ -344,6 +344,7 @@ def k_corrections_for_photon_counts_graph(save=False):
 
 def k_equation_flow_graph(save=False):
     plt.clf()
+    plt.rcParams["figure.figsize"] = (WIDTH, WIDTH)
     plt.rcParams["text.usetex"] = True
     #plt.rcParams["hatch.linewidth"] = 4
 
@@ -354,7 +355,7 @@ def k_equation_flow_graph(save=False):
     xs = np.linspace(lo, hi, hi - lo)
 
     fig = plt.figure(figsize=[1.5 * WIDTH, WIDTH])
-    fig.suptitle(r"Calculating $K'_{xy}$, the ratio of rest frame to observation frame counts for $z = 0.5$")
+    fig.suptitle(r"Calculating $\frac{\mathcal{F}_x}{\mathcal{F}_y}$, the ratio of rest frame to observation frame counts for $z = 0.5$")
 
     def F():
         ax = fig.add_axes([0.1, 8/11, 0.3, 0.075])
@@ -695,7 +696,7 @@ def k_equation_flow_graph(save=False):
         ax.spines["right"].set_visible(False)
         ax.set_xticks([])
         ax.set_yticks([])
-        ax.text(0.5, 0.5, r"$K'_{xy} = \frac{\int F'(\lambda) S_x(\lambda) d\lambda}{\int R'(\lambda) S_y(\lambda) d\lambda} = \frac{" + f"{val_x:.2f}" + r"}{" + f"{val_y:.2f}" + r"} = " + f"{val_x / val_y:.2f}" + r"$", fontsize=14)
+        ax.text(0.5, 0.5, r"$\frac{\mathcal{F}_x}{\mathcal{F}_y} = \frac{\int F'(\lambda) S_x(\lambda) d\lambda}{\int R'(\lambda) S_y(\lambda) d\lambda} = \frac{" + f"{val_x:.2f}" + r"}{" + f"{val_y:.2f}" + r"} = " + f"{val_x / val_y:.2f}" + r"$", fontsize=14)
     result()
 
     if save:
@@ -791,12 +792,12 @@ def all_lum_distance_vs_redshift_graph(data, save=True):
     # )
 
     ax.set_xlabel("z")
-    ax.set_ylabel("luminosity distance (Mps)")
+    ax.set_ylabel("light travel distance (Mps)")
 
     ax.set_title("Distance vs Redshift")
[…]

### 2025-02-03 paper/dark_energy_corrections.tex

@@
-\documentclass[aps,prl,reprint,amsmath]{revtex4-2}
+\documentclass[aps,prl,reprint,amsmath,floatfix]{revtex4-2}
 
 \usepackage{graphicx}
+\usepackage{relsize}
 
@@
 errors traces back to 1930 and two new errors were introduced in 1996. We
-conclude that properly correcting apparent magnitudes for redshift resolves two
-of the preeminent mysteries in cosmology: first, dark energy is not supported
-by observations of Type Ia supernovae and second, the Hubble tension is due to
-the errors in the K-correction equation.
+conclude that correcting apparent magnitudes for time dilation resolves two of
+the preeminent mysteries in cosmology: first, dark energy is not supported by
+observations of Type Ia supernovae and second, the Hubble tension is due to the
+errors in the K-correction equation.
 \end{abstract}
@@
 
-The estimate of Type Ia supernovae (SnIa) distances is one of the primary
-sources of data for cosmological models. Performing these distance estimates
-involves taking a measurement of redshifted light in our observation frame and
-then calculating the rest frame magnitude as if no redshift had occurred. The
-equation that converts from an observation frame magnitude to a rest frame
-magnitude is called K-correction.
+Cosmic expansion redshifts light, so when we compute the light travel distance
+it is necessary to account for multiple redshift effects. We will show that
+modern cosmology does not correct observations for time dilation.
+
+Most cosmological models require an estimate of distance, so this error is far
+reaching. However, we will focus on showing that correcting observations of
+Type Ia supernovae (SNe Ia) for time dilation resolves the Hubble tension. The
+Hubble tension, as described by \citet{verde2019}, is an observation that
+independent techniques of estimating the expansion rate produce incompatible
+values.
+
+In order to use SNe Ia to estimate the expansion rate of the universe, we need to
+identify both the redshift $z$ and the light travel distance $d$. In order to
+compute the light travel distance $d$, we use the definition of the distance
+modulus \citep{weinberg2008}:
+
+\begin{equation}
+\label{eq:mu_def}
+  d = 10^{1 + (m - M)/5} \text{pc}.
+\end{equation}
+
+\noindent The quantity $m$ represents the apparent magnitude while $M$
+represents the absolute magnitude of a SN Ia. It is common to use the
+substitution $\mu = m - M$ and call $\mu$ the distance modulus.
+
+Labeling $m$ as the ``apparent magnitude'' is a bit misleading for distant
+observations because redshift will change several aspects of the observed
+light. However, we can correct the value $m$ for redshift effects by using the
+K-correction equation. This allows us to report an apparent magnitude that
+represents the brightness of an object as if none of the light-altering effects
+of redshift were present. According to
+\citet{riess1998}:
+
+\begin{quote}
+  An appropriate K-correction quantifies the difference between the supernova
+  light that falls into a standard passband (e.g., $B$) at $z_0$ and that which
+  falls into the filters we employ to observe a redshifted SN Ia.
+\end{quote}
+
+\noindent In other words, the goal of the K-correction equation is to remove
+all redshift effects from the apparent magnitude $m$ so that the distance
+modulus defined in Equation \ref{eq:mu_def} allows us to compute the light
+travel distance $d$.
 
@@
 effects of redshift. An alternative K-correction was correctly derived by
-\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy was
-briefly discussed yet dismissed. \citet{oke1968} rederived the K-correction
-equation where they accounted for spectral bandwidth stretching, but they did
-not account for time dilation, one of the other dimming effects of redshift.
-The paper by \citet{kim1996}, which is the basis for modern implementations of
-K-correction, extended the work of \citet{oke1968} to handle additional
-cross-filter comparisons and added a term that was intended to address
-zero-point corrections. This history is explored in more depth in Section
-\ref{sec:history}.
+\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy between
+the two equations was briefly discussed yet ultimately dismissed.
+\citet{oke1968} derived a K-correction equation that they noted was equivalent
+to earlier work, and while they accounted for spectral bandwidth stretching,
+they did not account for time dilation. The paper by \citet{kim1996}, which is
+the basis for modern implementations of K-correction, extended the work of
+\citet{oke1968} to handle additional cross-filter comparisons and added a term
+that was intended to address zero-point corrections.
 
-The effect of using an incorrect redshift correction for SnIa is that we think
+The effect of using an incorrect redshift correction for SNe Ia is that we think
 objects are farther away than they really are; this effect compounds for
@@
 constant $\Lambda$ and dark energy in order to explain the non-linear
-distance-redshift graph. We will show in Section \ref{sec:conclusions} that
-correcting the flaws of K-correction leads to a linear graph that does not
-need to rely on a cosmological constant.
+distance-redshift graph. We will show that correcting the flaws of K-correction
+leads to a linear graph that does not need to rely on a cosmological constant.
 
@@
 with our understanding of cosmology because this technique produces a
-significantly different value than when the constant is derived using SnIa.  As
-we will discuss in Section \ref{sec:conclusions}, fixing the errors with
-K-correction produces a measurement of the Hubble constant that is compatible
-with models based on the CMB.
+significantly different value than when the constant is derived using SNe Ia.
+Fixing the errors with K-correction produces a measurement of the Hubble
+constant that is compatible with models based on the CMB.
 
 \section{A brief history of K-correction}
-\label{sec:history}
 
-Observational data from SnIa are essential for the calibration of models that
+Observational data from SNe Ia are essential for the calibration of models that
 use redshift to estimate distance. The approximately linear relationship
-between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
-describes how quickly the universe is expanding. However, \citet{riess1998}
-and \citet{perlmutter1999} presented evidence that there is not a linear
-relationship between redshift and distance, but instead, distant objects are
-farther away than their redshift would predict (see Figure
-\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
+between redshift and light travel distance, often called the
+Hubble-Lema\^{i}tre law, describes how quickly the universe is expanding.
+However, \citet{riess1998} and \citet{perlmutter1999} presented evidence that
+there is not a linear relationship between redshift and distance, but instead,
+distant objects are farther away than their redshift would predict (see Figure
+\ref{fig:distance_vs_redshift}). This phenomenon implies that the
 acceleration of the universe is faster today than it was for old observations.
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{lum_distance_vs_redshift.pdf}
-  \caption{The relationship between luminosity distance and redshift for two
+  \includegraphics[width=\columnwidth]{distance_vs_redshift.pdf}
+  \caption{The relationship between light travel distance and redshift for two
   treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
@@
   treatment, which fixes the K-correction redshift error, appears to be linear.
-  The displayed points are roughly a third of the values in the full SnIa
+  The displayed points are roughly a third of the values in the full SNe Ia
   dataset published in \citet{abbott2024}, selected with uniform redshift
   spacing to aid visibility. }
-  \label{fig:mu_distance_vs_redshift}
+  \label{fig:distance_vs_redshift}
 \end{figure}
 
-SnIa are used to explore the relationship between distance and redshift because
-these events have a roughly constant absolute magnitude, which allows us to use
-the apparent magnitude to estimate distance. An analogy is to imagine someone
-walking in the dark and lighting matches. If we know how brightly a match burns
-at a known distance, we can estimate the distance to any match by measuring the
-apparent brightness before applying some geometry.
+SNe Ia are used to explore the relationship between distance and redshift because
+these events have a roughly constant absolute magnitude which allows us to use
+the apparent magnitude to estimate distance.
 
-However, redshifting dims the luminosity of an observation in three ways:
+However, redshifting dims the brightness of an observation in three ways:
 
@@
   redshift of $z$ means the amount of energy per photon is reduced by a factor
-  of $1 / (1+z)$.
+  of ${1 / (1+z)}$.
 
   \item The bandwidth stretches. If the rest frame observes photons in the
-  bandwidth from 400nm and 401nm, then a redshift of $z = 1$ stretches the
+  bandwidth from 400nm and 401nm, then a redshift of ${z = 1}$ stretches the
   wavelengths to the bandwidth from 800nm to 802nm. The number of photons per
-  bandwidth is reduced by a factor of $1 / (1+z)$.
+  bandwidth is reduced by a factor of ${1 / (1+z)}$.
 
   \item Cosmological time dilation reduces the rate at which photons arrive.
-  The number of photons that arive per second is reduced by a factor of $1 / (1+z)$.
+  The number of photons that arive per second is reduced by a factor of ${1 / (1+z)}$.
 \end{itemize}
 
-To complicate matters, we use the $B$ band magnitude to calculate luminosity
+To complicate matters, we use the $B$ band magnitude to calculate light travel
 distance. We want to know how bright a supernova appears for wavelengths around
@@
 measured in an observation filter $y$ and compute the magnitude in the target
-filter $x$.
+filter $x$. Even if the observation filter is the same as the target filter,
+the K-correction equation is necessary to remove redshift effects.
 
@@
 A few years later, \citet{desitter1934} discussed all three issues that reduce
-the observed magnitude of a distant observation. The correction for each of
-these issues is identical: take a measurement for luminosity and multiply it by
-the factor $1 + z$.
+the observed brightness of a distant observation. The correction for each of
+these issues is identical: take a flux measurement and multiply it by the
+factor $1 + z$.
 
-A year later, \citet{hubble1935} published a similar set of calculations where they noted:
+A year later, \citet{hubble1935} published a similar set of calculations where
+they stated:
 
@@
 
-In a paper published by \citet{oke1968}, the two factors of $(1 + z)$ were
+In a paper published by \citet{oke1968}, the two factors of ${1 + z}$ were
 attributed to the change in energy and to the spectral bandwidth elongation,
@@
 blue $B$ and visible $V$ bands. It also introduced a term that deals with the
-zero-point for the actual filters. Historically, bolometric devices would
-measure the energy flux, but modern charge-coupled device (CCD) cameras
+zero-point correction for the actual filters. Historically, bolometric devices
+would measure the energy flux, but modern charge-coupled device (CCD) cameras
 effectively measure the photon flux, so \citet{kim1996} derived a form of the
-K-correction equation that uses photon flux.
-
-Quoting \citet{kim1996}:
-
-\begin{quote}
-  Therefore, the correct K correction calculation to be used with measured
-  photometric magnitudes is the integral photon counts:
-
-  \begin{equation}
-  \begin{aligned}
-  \label{eq:kim}
-    K_{xy} =
-      &-2.5\text{log} \left(
-        \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
-             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) \\
-      &+ 2.5\text{log}(1+z) \\
-      &+ 2.5\text{log}\left(
-        \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
-             {\int \lambda F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
-  \end{aligned}
-  \end{equation}
-\end{quote}
-
-This equation has three errors that we will explore in Section
-\ref{sec:consequences}.
+K-correction equation that uses photon flux. This is the form of the
+K-correction equation that is used by modern astrophysics, but we will show
+that it contains three errors, one of which is innocuous, one of which
+introduces measurement bias, and one that produces the dark energy phenomenon.
 
 \section{Derivation of K-correction}
-\label{sec:derivation}
 
-The K-correction $K_{xy}$ uses a spectral energy density $F$ template that
-specifies the expected spectrum for a SnIa observation. It also uses the
-observed redshift $z$ and the observed photon flux magnitude $m_y$.
+The K-correction $K_{xy}$ uses a spectral energy density template $F$ that
+specifies the expected spectrum for a SN Ia observation. It also uses the
+observed redshift $z$ and the observed photon flux magnitude $m_y$ measured in
+filter $y$.
 
@@
   compute the expected ratio of photons by totalling the area under the curves
-  in the bottom two panels.
+  in the bottom two panels. Dark energy occurs when we omit the step that
+  corrects for time dilation.
   }
@@
       &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
-      &= -2.5 \text{log}(\mathcal{F}_y) \\
-         &\qquad - 2.5 \text{log}(P'_y) \\
-         &\qquad - 2.5 \text{log}(K'_{xy}) \\
-         &\qquad + 2.5 \text{log}(P'_x) \\
-      &= -2.5 \biggl(\text{log}(\mathcal{F}_y) + \text{log}(K'_{xy}) \\
-         &\qquad\qquad + \text{log}(P'_y) - \text{log}(P'_x)
-        \biggr) \\
+      &= -2.5 \text{log}(\mathcal{F}_y) - 2.5 \text{log}(P'_y) \\
+         &\qquad - 2.5 \text{log}(K'_{xy}) + 2.5 \text{log}(P'_x) \\
+      &= -2.5 \left(\text{log}(\mathcal{F}_y) + \text{log}(K'_{xy}) \right. \\
+         &\qquad\qquad + \left. \text{log}(P'_y) - \text{log}(P'_x)
+        \right) \\
       &= -2.5 \text{log}\left(
@@
               \frac{\int \left(\frac{\lambda}{hc}\right) F(\lambda) S_x(\lambda) d\lambda}
-                   {\int \left(\frac{\lambda}{(1+z)hc}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
+                   {\int \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
           &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
@@
   K_{xy} &= 2.5\text{log}(K'_{xy}) \\
-         &= 2.5\text{log}\left(
-            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
+         &= 2.5\text{log}
+  \begin{aligned}[t]
+          &\left( \vphantom{\frac{\int}{\left(\frac{\int}{1}\right)}} \right.
+              \frac{P'_x}{P'_y} \times (1 + z)^2 \\
+          &\left.\quad \times
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                 {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda}\right) \\
-         &= 2.5 \left(
+                   {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}\right)
+  \end{aligned} \\
+         &= 2.5
+  \begin{aligned}[t]
+         &\left( \vphantom{\frac{\int}{\left(\frac{\int}{1}\right)}}
             \text{log} \left( \frac{P'_x}{P'_y} \right)
-            + \text{log}( {(1 + z)^2})
-            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                                    {\int (\lambda / (1+z)) F((\lambda)/ (1+z)) S_y(\lambda) d\lambda}
-            \right) \right) \\
+            + \text{log}\left( {(1 + z)^2}\right) \right. \\
+         &\left.\quad + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
+                                    {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}
+            \right) \right)
+  \end{aligned} \\
          &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
-            + 5 \text{log} (1 + z)
-            + 2.5 \text{log} \left(
+            + 5 \text{log} (1 + z) \\
+            &\quad + 2.5 \text{log} \left(
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
          &= 5 \text{log} (1 + z)
@@
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
-            - P_x + P_y .
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
+            &\quad - P_x + P_y .
 \end{aligned}
@@
 \section{Consequences}
-\label{sec:consequences}
 
-In order to fully compare our derivation against Equation \ref{eq:kim} (from
-\citet{kim1996}) we need to use the identity
+The modern version of the K-correction equation was presented by \citet{kim1996}:
+
+\begin{equation}
+\begin{aligned}
+\label{eq:kim}
+  K_{xy} &=
+    -2.5\text{log} \left(
+      \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
+           {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) \\
+    &\quad + 2.5\text{log}(1+z) \\
+    &\quad + 2.5\text{log}\left(
+      \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
+           {\int \lambda F\left(\frac{\lambda}{1+z}\right)S_y(\lambda))d\lambda}\right) \quad \text{(incorrect)}.
+\end{aligned}
+\end{equation}
+
+In order to fully compare Equation \ref{eq:K2k} against Equation \ref{eq:kim} we need to use the identity
 
@@
 \begin{aligned}
-  K_{xy} &= 5 \text{log} (1 + z)
-            + 2.5 \text{log} \left(
+  K_{xy} &= 5 \text{log} (1 + z) \\
+         &\quad + 2.5 \text{log} \left(
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
-            - P_x + P_y \\
-         &= 5 \text{log} (1 + z)
-            + 2.5 \text{log} \left(
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
+         &\quad - P_x + P_y \\
+         &= 5 \text{log} (1 + z) \\
+         &\quad + 2.5 \text{log} \left(
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\ \ \
-            + 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
-            - 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
+         &\quad + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right) \\
+         &\quad - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
          &= 2.5 \text{log} \left(
@@
                    {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
-             \right)
-            + 5 \text{log} (1 + z)
-            + 2.5 \text{log} \left(
+             \right) \\
+         &\quad + 5 \text{log} (1 + z) \\
+         &\quad + 2.5 \text{log} \left(
               \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
-                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) .
+                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) .
 \end{aligned}
@@
 \section{Conclusions}
-\label{sec:conclusions}
 
@@
   \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
-  \caption{The relationship between expansion velocity and distance. The slope
-  of this graph demonstrates the Hubble constant. The data for these SnIa
-  observations comes from the Dark Energy Survey \citep{vincenzi2024}, but the
-  magnitudes are corrected to account for time dilation by adding
-  $-2.5 log(1 + z)$.
+  \caption{The relationship between expansion velocity and light travel
+  distance. The slope of this graph demonstrates the Hubble constant. The data
+  for these SN Ia observations comes from the Dark Energy Survey
+  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
+  dilation by adding $-2.5 \text{log}(1 + z)$.
   }
@@
 
-As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
+As shown in Figure \ref{fig:distance_vs_redshift}, when reported magnitudes
 are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
-relationship between redshift and luminosity distance. This is in accordance
+relationship between redshift and light travel distance. This is in accordance
 with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
@@
 
-The value estimated here, $H_0 = 65.94 \pm 1.3$ is highly suspicious
+The value estimated here, $H_0 = 65.94 \pm 1.3$, is highly suspicious
 because of the flipped zero-point corrections, but it is consistent with
@@
 is interesting to note that restricting the Dark Energy Survey observations of
-SnIa \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
+SN Ia \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
 small enough redshift that most of the observations will have been made with
@@
 
-\bibliography{references}{}
-\bibliographystyle{aasjournal}
+\bibliography{references}
 

### 2025-02-04 src/redshift/supernova.py
Minor tweaks

@@ -70,20 +70,20 @@ class Supernova:
     def mu(self, correction=Correction.NONE):
         return self.corrected_magnitude(correction) - self.absolute_magnitude
 
-    def lum_distance(self, correction=Correction.ONE, use_mpc=True):
+    def light_distance(self, correction=Correction.ONE, use_mpc=True):
         d = 10 ** (1 + self.mu(correction) / 5)
         if use_mpc:
             d /= 1e6
         return d
 
     def orig_distance(self, correction=Correction.ONE):
-        return self.lum_distance(correction) / math.exp(self.z)
+        return self.light_distance(correction) / math.exp(self.z)
 
     def comoving_distance(self, correction=Correction.ONE):
         return self.orig_distance() * (1 + self.z)
 
     def delta_distance(self, correction=Correction.ONE):
-        return self.lum_distance(correction) - self.orig_distance(correction)
+        return self.light_distance(correction) - self.orig_distance(correction)
 
     def energy_loss(self):
         # E = hc / l
@@ -95,7 +95,7 @@ class Supernova:
 
     @property
     def t(self):
-        return self.lum_distance(correction=Correction.ONE, use_mpc=False) * 3.26156
+        return self.light_distance(correction=Correction.ONE, use_mpc=False) * 3.26156
 
     @property
     def rate(self):
@@ -105,7 +105,7 @@ class Supernova:
     def hubble(self):
         return (
             self.rate
-            * self.lum_distance(use_mpc=False)
+            * self.light_distance(use_mpc=False)
             * 3.086e13
             / (365 * 24 * 60 * 60)
         )
@@ -724,14 +724,14 @@ def reduce_data(data, step=0.002) -> list[Supernova]:
     return new_data
 
 
-def all_lum_distance_vs_redshift_graph(data, save=True):
+def all_light_distance_vs_redshift_graph(data, save=True):
     fig = plt.figure(figsize=[WIDTH, 0.9 * WIDTH])
     ax = fig.add_axes([0, 1, 1, 1])
 
     reduced_data = reduce_data(data)
     xs = [sn.z for sn in reduced_data]
 
-    ys = [sn.lum_distance(correction=Correction.ONE) for sn in reduced_data]
[…]

### 2025-02-04 paper/dark_energy_corrections.tex

@@
 represents the brightness of an object as if none of the light-altering effects
-of redshift were present. According to
-\citet{riess1998}:
+of redshift were present. According to \citet{riess1998}:
 
 \begin{quote}
-  An appropriate K-correction quantifies the difference between the supernova
-  light that falls into a standard passband (e.g., $B$) at $z_0$ and that which
-  falls into the filters we employ to observe a redshifted SN Ia.
+  An appropriate K-correction quantifies the \emph{difference} between the supernova
+  light that falls into a standard passband (e.g., $B$) at ${z = 0}$ and that
+  which falls into the filters we employ to observe a redshifted SN Ia.
 \end{quote}
@@
   \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
-  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
-  report in the target filter divided by the number of photons we measure in
-  the observation filter. Deriving this value starts with $F(\lambda)$, the
-  spectral energy density, which we then convert to $F'(\lambda)$, the photon
-  density for the rest frame. Starting at the top right corner of the figure we
-  show three steps used to compute $R'(\lambda)$, the photon density in the
-  observation frame. We first stretch the photon density, but this step
-  inflates counts. In the second step, we correct for the inflated counts by
-  multiplying by $1/(1+z)$; at this point, the total count equals the total
-  count of $F'(\lambda)$. Finally, in the third step we finish calculating the
-  observation frame photon density $R'(\lambda)$ by accounting for time
-  dilation, which also reduces photon counts by a factor of $1/(1+z)$. We can
-  compute the expected ratio of photons by totalling the area under the curves
-  in the bottom two panels. Dark energy occurs when we omit the step that
-  corrects for time dilation.
+  \caption{The value $\mathcal{F}_x / \mathcal{F}_y$ is equal to the number of
+  photons we want to report in the target filter divided by the number of
+  photons we measure in the observation filter. Deriving this value starts with
+  $F(\lambda)$, the spectral energy density, which we then convert to
+  $F'(\lambda)$, the photon density for the rest frame. Starting at the top
+  right corner of the figure we show three steps used to compute $R'(\lambda)$,
+  the photon density in the observation frame. We first stretch the photon
+  density, but this step inflates counts. In the second step, we correct for
+  the inflated counts by multiplying by $1/(1+z)$; at this point, the total
+  count equals the total count of $F'(\lambda)$. Finally, in the third step we
+  finish calculating the observation frame photon density $R'(\lambda)$ by
+  accounting for time dilation, which also reduces photon counts by a factor of
+  $1/(1+z)$. We can compute the expected ratio of photons by totalling the area
+  under the curves in the bottom two panels. Dark energy occurs when we omit
+  the step that corrects for time dilation.
   }
@@
   \citep{vincenzi2024}, but the magnitudes are corrected to account for time
-  dilation by adding $-2.5 \text{log}(1 + z)$.
+  dilation by adding ${-2.5 \text{log}(1 + z)}$.
   }
@@
 estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
-CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap. It
-is interesting to note that restricting the Dark Energy Survey observations of
-SN Ia \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
-small enough redshift that most of the observations will have been made with
-the same filter, gives the estimate $H_0 = 67.8 \pm 1.9$.
+CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap.
 

### 2025-02-04 paper/dark_energy_corrections.tex
Move references into main tex file

@@
 
+\begin{filecontents}{references.bib}
+@article{riess1998,
+  title={Observational evidence from supernovae for an accelerating universe and a cosmological constant},
+  author={Riess, Adam G and Filippenko, Alexei V and Challis, Peter and Clocchiatti, Alejandro and Diercks, Alan and Garnavich, Peter M and Gilliland, Ron L and Hogan, Craig J and Jha, Saurabh and Kirshner, Robert P and others},
+  journal={The astronomical journal},
+  volume={116},
+  number={3},
+  pages={1009},
+  year={1998},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter1999,
+  title={Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift supernovae},
+  author={Perlmutter, Saul and Aldering, Goldhaber and Goldhaber, Gerson and Knop, Richard A and Nugent, Peter and Castro, Patricia G and Deustua, Susana and Fabbro, Sebastien and Goobar, Ariel and Groom, Donald E and others},
+  journal={The Astrophysical Journal},
+  volume={517},
+  number={2},
+  pages={565},
+  year={1999},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter2003,
+  title={Measuring cosmology with supernovae},
+  author={Perlmutter, Saul and Schmidt, Brian P},
+  journal={Supernovae and Gamma-Ray Bursters},
+  pages={195--217},
+  year={2003},
+  publisher={Springer}
+}
+
+@book{weinberg2008,
+  title={Cosmology},
+  author={Weinberg, Steven},
+  year={2008},
+  publisher={OUP Oxford}
+}
+
+@article{straumann2012,
+  title={The 2011 Nobel Prize in Physics},
+  author={Straumann, Norbert and Z{\"u}rich, Uni},
+  journal={SPG Mitteilungen},
+  number={36},
+  year={2012}
+}
+
+@article{betoule2014,
+  title={Improved cosmological constraints from a joint analysis of the SDSS-II and SNLS supernova samples},
+  author={Betoule, MEA and Kessler, R and Guy, J and Mosher, J and Hardin, D and Biswas, R and Astier, P and El-Hage, P and Konig, M and Kuhlmann, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={568},
+  pages={A22},
+  year={2014},
+  publisher={EDP Sciences}
+}
+
+@article{siegel1982,
+  title={Robust regression using repeated medians},
+  author={Siegel, Andrew F},
+  journal={Biometrika},
+  volume={69},
+  number={1},
+  pages={242--244},
+  year={1982},
+  publisher={Oxford University Press}
+}
+
+@article{verde2019,
+  title={Tensions between the early and late Universe},
+  author={Verde, Licia and Treu, Tommaso and Riess, Adam G},
+  journal={Nature Astronomy},
+  volume={3},
+  number={10},
+  pages={891--895},
+  year={2019},
+  publisher={Nature Publishing Group UK London}
+}
+
+@article{abbott2024,
+  title={The Dark Energy Survey: Cosmology Results With $\sim$1500 New High-redshift Type Ia Supernovae Using The Full 5-year Dataset},
+  author={DES-Collaboration and Abbott, TMC and Acevedo, M and Aguena, M and Alarcon, A and Allam, S and Alves, O and Amon, A and Andrade-Oliveira, F and Annis, J and Armstrong, P and others},
+  journal={arXiv preprint arXiv:2401.02929},
+  year={2024}
+}
+
+@article{perivolaropoulos2022,
+  title={Challenges for $\Lambda$CDM: An update},
+  author={Perivolaropoulos, Leandros and Skara, Foteini},
+  journal={New Astronomy Reviews},
+  volume={95},
+  pages={101659},
+  year={2022},
+  publisher={Elsevier}
+}
+
+@article{flaugher2015,
+  title={The dark energy camera},
+  author={Flaugher, Brenna and Diehl, HT and Honscheid, K and Abbott, TMC and Alvarez, O and Angstadt, R and Annis, JT and Antonik, M and Ballester, O and Beaufore, L and others},
+  journal={The Astronomical Journal},
+  volume={150},
+  number={5},
+  pages={150},
+  year={2015},
+  publisher={IOP Publishing}
+}
+
+@article{vincenzi2024,
+  title={The Dark Energy Survey Supernova Program: Cosmological Analysis and Systematic Uncertainties},
+  author={Vincenzi, M and Brout, D and Armstrong, P and Popovic, B and Taylor, G and Acevedo, M and Camilleri, R and Chen, R and Davis, TM and Lee, J and others},
+  journal={The Astrophysical Journal},
+  volume={975},
+  number={1},
+  pages={86},
+  year={2024},
+  publisher={IOP Publishing}
+}
+
+@article{shao2013,
+  title={The energy loss of photons and cosmological redshift},
+  author={Shao, Ming-Hui},
+  journal={Physics Essays},
+  volume={26},
+  number={2},
+  pages={183--190},
+  year={2013},
+  publisher={Physics Essays Publication}
+}
+
+@article{white2024,
+  title={The Dark Energy Survey Supernova Program: Slow supernovae show cosmological time dilation out to $ z \sim 1$},
+  author={White, Ryan MT and Davis, Tamara M and Lewis, Geraint F and Lidman, Christopher and Shah, Paul and Abbott, TMC and Aguena, M and Allam, S and Andrade-Oliveira, F and Asorey, J and others},
+  journal={arXiv preprint arXiv:2406.05050},
+  year={2024}
+}
+
+@article{blondin2008,
+  title={Time dilation in type Ia supernova spectra at high redshift},
+  author={Blondin, Stephanie and Davis, Tamara M and Krisciunas, Kevin and Schmidt, Brian P and Sollerman, J and Wood-Vasey, WM and Becker, AC and Challis, P and Clocchiatti, A and Damke, G and others},
+  journal={The Astrophysical Journal},
+  volume={682},
+  number={2},
+  pages={724},
+  year={2008},
+  publisher={IOP Publishing}
+}
+
+@article{zwicky1929,
+  title={On the redshift of spectral lines through interstellar space},
+  author={Zwicky, Fritz},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={15},
+  number={10},
+  pages={773--779},
+  year={1929},
+  publisher={National Acad Sciences}
+}
+
+@article{tolman1930,
+  title={On the estimation of distances in a curved universe with a non-static line element},
+  author={Tolman, Richard C},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={16},
+  number={7},
+  pages={511--520},
+  year={1930},
+  publisher={National Acad Sciences}
+}
+
+@article{desitter1934,
+  title={On distance, magnitude, and related quantities in an expanding universe},
+  author={de Sitter, Willem},
+  journal={Bulletin of the Astronomical Institutes of the Netherlands, Vol. 7, p. 205},
+  volume={7},
+  pages={205},
+  year={1934}
+}
+
+@article{hubble1935,
+  title={Two methods of investigating the nature of the nebular redshift},
+  author={Hubble, Edwin and Tolman, Richard C},
+  journal={Astrophysical Journal, vol. 82, p. 302},
+  volume={82},
+  pages={302},
+  year={1935}
+}
+
+@article{oke1968,
+  title={Energy distributions, k corrections, and the Stebbins-Whitford effect for giant elliptical galaxies},
+  author={Oke, John Beverley and Sandage, Allan},
+  journal={Astrophysical Journal, vol. 154, p. 21},
+  volume={154},
+  pages={21},
+  year={1968}
+}
+
+@article{kim1996,
+  title={A generalized K correction for type Ia supernovae: comparing R-band photometry beyond z= 0.2 with B, V, and R-band nearby photometry},
+  author={Kim, Alex and Goobar, Ariel and Perlmutter, Saul},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={108},
+  number={720},
+  pages={190},
+  year={1996},
+  publisher={IOP Publishing}
+}
+
+@article{hsiao2007,
+  title={K-corrections and spectral templates of Type Ia supernovae},
+  author={Hsiao, Eric Y and Conley, A and Howell, DA and Sullivan, M and Pritchet, CJ and Carlberg, RG and Nugent, PE and Phillips, MM},
+  journal={The Astrophysical Journal},
+  volume={663},
+  number={2},
+  pages={1187},
+  year={2007},
+  publisher={IOP Publishing}
+}
+
+@article{kessler2009,
+  title={SNANA: A public software package for supernova analysis},
+  author={Kessler, Richard and Bernstein, Joseph P and Cinabro, David and Dilday, Benjamin and Frieman, Joshua A and Jha, Saurabh and Kuhlmann, Stephen and Miknaitis, Gajus and Sako, Masao and Taylor, Matt and others},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={121},
+  number={883},
+  pages={1028},
+  year={2009},
+  publisher={IOP Publishing}
+}
+
+@article{burns2010,
+  title={The Carnegie supernova project: light-curve fitting with SNooPy},
+  author={Burns, Christopher R and Stritzinger, Maximilian and Phillips, MM and Kattner, ShiAnne and Persson, SE and Madore, Barry F and Freedman, Wendy L and Boldt, Luis and Campillay, Abdo and Contreras, Carlos and others},
+  journal={The Astronomical Journal},
+  volume={141},
+  number={1},
+  pages={19},
+  year={2010},
+  publisher={IOP Publishing}
+}
+
+@article{planck2015,
+  title={Planck 2015 results-xiii. cosmological parameters},
+  author={Planck-Collaboration and Ade, Peter AR and Aghanim, Nabila and Arnaud, M and Ashdown, Mark and Aumont, Jea and Baccigalupi, Carlo and Banday, AJ and Barreiro, RB and Bartlett, JG and Bartolo, Nicola and others},
+  journal={Astronomy \& Astrophysics},
+  volume={594},
+  pages={A13},
+  year={2016},
+  publisher={EDP sciences}
+}
+
+@article{planck2020,
+  title={Planck 2018 results-VI. Cosmological parameters},
+  author={Planck-Collaboration and Aghanim, Nabila and Akrami, Yashar and Ashdown, Mark and Aumont, Jonathan and Baccigalupi, Carlo and Ballardini, Mario and Banday, Anthony J and Barreiro, RB and Bartolo, Nicola and Basak, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={641},
+  pages={A6},
+  year={2020},
+  publisher={EDP sciences}
+}
+
+@article{camarena2020,
+  title={Local determination of the Hubble constant and the deceleration parameter},
+  author={Camarena, David and Marra, Valerio},
+  journal={Physical Review Research},
+  volume={2},
+  number={1},
+  pages={013028},
+  year={2020},
+  publisher={APS}
+}
+
+@book{peebles2020,
+  title={Cosmology’s century: An inside history of our modern understanding of the universe},
+  author={Peebles, Phillip James Edwin},
+  year={2020},
+  publisher={Princeton University Press}
+}
+
+@article{lesser2015,
+  title={A summary of charge-coupled devices for astronomy},
+  author={Lesser, Michael},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={127},
+  number={957},
+  pages={1097--1104},
+  year={2015},
+  publisher={The Astronomical Society of the Pacific}
+}
+\end{filecontents}
 \bibliography{references}

### 2025-02-04 paper/dark_energy_corrections.tex
Fix file issues for submission to PRL

@@
+\begin{filecontents}{references.bib}
+@article{riess1998,
+  title={Observational evidence from supernovae for an accelerating universe and a cosmological constant},
+  author={Riess, Adam G and Filippenko, Alexei V and Challis, Peter and Clocchiatti, Alejandro and Diercks, Alan and Garnavich, Peter M and Gilliland, Ron L and Hogan, Craig J and Jha, Saurabh and Kirshner, Robert P and others},
+  journal={The astronomical journal},
+  volume={116},
+  number={3},
+  pages={1009},
+  year={1998},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter1999,
+  title={Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift supernovae},
+  author={Perlmutter, Saul and Aldering, Goldhaber and Goldhaber, Gerson and Knop, Richard A and Nugent, Peter and Castro, Patricia G and Deustua, Susana and Fabbro, Sebastien and Goobar, Ariel and Groom, Donald E and others},
+  journal={The Astrophysical Journal},
+  volume={517},
+  number={2},
+  pages={565},
+  year={1999},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter2003,
+  title={Measuring cosmology with supernovae},
+  author={Perlmutter, Saul and Schmidt, Brian P},
+  journal={Supernovae and Gamma-Ray Bursters},
+  pages={195--217},
+  year={2003},
+  publisher={Springer}
+}
+
+@book{weinberg2008,
+  title={Cosmology},
+  author={Weinberg, Steven},
+  year={2008},
+  publisher={OUP Oxford}
+}
+
+@article{straumann2012,
+  title={The 2011 Nobel Prize in Physics},
+  author={Straumann, Norbert and Z{\"u}rich, Uni},
+  journal={SPG Mitteilungen},
+  number={36},
+  year={2012}
+}
+
+@article{betoule2014,
+  title={Improved cosmological constraints from a joint analysis of the SDSS-II and SNLS supernova samples},
+  author={Betoule, MEA and Kessler, R and Guy, J and Mosher, J and Hardin, D and Biswas, R and Astier, P and El-Hage, P and Konig, M and Kuhlmann, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={568},
+  pages={A22},
+  year={2014},
+  publisher={EDP Sciences}
+}
+
+@article{siegel1982,
+  title={Robust regression using repeated medians},
+  author={Siegel, Andrew F},
+  journal={Biometrika},
+  volume={69},
+  number={1},
+  pages={242--244},
+  year={1982},
+  publisher={Oxford University Press}
+}
+
+@article{verde2019,
+  title={Tensions between the early and late Universe},
+  author={Verde, Licia and Treu, Tommaso and Riess, Adam G},
+  journal={Nature Astronomy},
+  volume={3},
+  number={10},
+  pages={891--895},
+  year={2019},
+  publisher={Nature Publishing Group UK London}
+}
+
+@article{abbott2024,
+  title={The Dark Energy Survey: Cosmology Results With $\sim$1500 New High-redshift Type Ia Supernovae Using The Full 5-year Dataset},
+  author={DES-Collaboration and Abbott, TMC and Acevedo, M and Aguena, M and Alarcon, A and Allam, S and Alves, O and Amon, A and Andrade-Oliveira, F and Annis, J and Armstrong, P and others},
+  journal={arXiv preprint arXiv:2401.02929},
+  year={2024}
+}
+
+@article{perivolaropoulos2022,
+  title={Challenges for $\Lambda$CDM: An update},
+  author={Perivolaropoulos, Leandros and Skara, Foteini},
+  journal={New Astronomy Reviews},
+  volume={95},
+  pages={101659},
+  year={2022},
+  publisher={Elsevier}
+}
+
+@article{flaugher2015,
+  title={The dark energy camera},
+  author={Flaugher, Brenna and Diehl, HT and Honscheid, K and Abbott, TMC and Alvarez, O and Angstadt, R and Annis, JT and Antonik, M and Ballester, O and Beaufore, L and others},
+  journal={The Astronomical Journal},
+  volume={150},
+  number={5},
+  pages={150},
+  year={2015},
+  publisher={IOP Publishing}
+}
+
+@article{vincenzi2024,
+  title={The Dark Energy Survey Supernova Program: Cosmological Analysis and Systematic Uncertainties},
+  author={Vincenzi, M and Brout, D and Armstrong, P and Popovic, B and Taylor, G and Acevedo, M and Camilleri, R and Chen, R and Davis, TM and Lee, J and others},
+  journal={The Astrophysical Journal},
+  volume={975},
+  number={1},
+  pages={86},
+  year={2024},
+  publisher={IOP Publishing}
+}
+
+@article{shao2013,
+  title={The energy loss of photons and cosmological redshift},
+  author={Shao, Ming-Hui},
+  journal={Physics Essays},
+  volume={26},
+  number={2},
+  pages={183--190},
+  year={2013},
+  publisher={Physics Essays Publication}
+}
+
+@article{white2024,
+  title={The Dark Energy Survey Supernova Program: Slow supernovae show cosmological time dilation out to $ z \sim 1$},
+  author={White, Ryan MT and Davis, Tamara M and Lewis, Geraint F and Lidman, Christopher and Shah, Paul and Abbott, TMC and Aguena, M and Allam, S and Andrade-Oliveira, F and Asorey, J and others},
+  journal={arXiv preprint arXiv:2406.05050},
+  year={2024}
+}
+
+@article{blondin2008,
+  title={Time dilation in type Ia supernova spectra at high redshift},
+  author={Blondin, Stephanie and Davis, Tamara M and Krisciunas, Kevin and Schmidt, Brian P and Sollerman, J and Wood-Vasey, WM and Becker, AC and Challis, P and Clocchiatti, A and Damke, G and others},
+  journal={The Astrophysical Journal},
+  volume={682},
+  number={2},
+  pages={724},
+  year={2008},
+  publisher={IOP Publishing}
+}
+
+@article{zwicky1929,
+  title={On the redshift of spectral lines through interstellar space},
+  author={Zwicky, Fritz},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={15},
+  number={10},
+  pages={773--779},
+  year={1929},
+  publisher={National Acad Sciences}
+}
+
+@article{tolman1930,
+  title={On the estimation of distances in a curved universe with a non-static line element},
+  author={Tolman, Richard C},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={16},
+  number={7},
+  pages={511--520},
+  year={1930},
+  publisher={National Acad Sciences}
+}
+
+@article{desitter1934,
+  title={On distance, magnitude, and related quantities in an expanding universe},
+  author={de Sitter, Willem},
+  journal={Bulletin of the Astronomical Institutes of the Netherlands, Vol. 7, p. 205},
+  volume={7},
+  pages={205},
+  year={1934}
+}
+
+@article{hubble1935,
+  title={Two methods of investigating the nature of the nebular redshift},
+  author={Hubble, Edwin and Tolman, Richard C},
+  journal={Astrophysical Journal, vol. 82, p. 302},
+  volume={82},
+  pages={302},
+  year={1935}
+}
+
+@article{oke1968,
+  title={Energy distributions, k corrections, and the Stebbins-Whitford effect for giant elliptical galaxies},
+  author={Oke, John Beverley and Sandage, Allan},
+  journal={Astrophysical Journal, vol. 154, p. 21},
+  volume={154},
+  pages={21},
+  year={1968}
+}
+
+@article{kim1996,
+  title={A generalized K correction for type Ia supernovae: comparing R-band photometry beyond z= 0.2 with B, V, and R-band nearby photometry},
+  author={Kim, Alex and Goobar, Ariel and Perlmutter, Saul},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={108},
+  number={720},
+  pages={190},
+  year={1996},
+  publisher={IOP Publishing}
+}
+
+@article{hsiao2007,
+  title={K-corrections and spectral templates of Type Ia supernovae},
+  author={Hsiao, Eric Y and Conley, A and Howell, DA and Sullivan, M and Pritchet, CJ and Carlberg, RG and Nugent, PE and Phillips, MM},
+  journal={The Astrophysical Journal},
+  volume={663},
+  number={2},
+  pages={1187},
+  year={2007},
+  publisher={IOP Publishing}
+}
+
+@article{kessler2009,
+  title={SNANA: A public software package for supernova analysis},
+  author={Kessler, Richard and Bernstein, Joseph P and Cinabro, David and Dilday, Benjamin and Frieman, Joshua A and Jha, Saurabh and Kuhlmann, Stephen and Miknaitis, Gajus and Sako, Masao and Taylor, Matt and others},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={121},
+  number={883},
+  pages={1028},
+  year={2009},
+  publisher={IOP Publishing}
+}
+
+@article{burns2010,
+  title={The Carnegie supernova project: light-curve fitting with SNooPy},
+  author={Burns, Christopher R and Stritzinger, Maximilian and Phillips, MM and Kattner, ShiAnne and Persson, SE and Madore, Barry F and Freedman, Wendy L and Boldt, Luis and Campillay, Abdo and Contreras, Carlos and others},
+  journal={The Astronomical Journal},
+  volume={141},
+  number={1},
+  pages={19},
+  year={2010},
+  publisher={IOP Publishing}
+}
+
+@article{planck2015,
+  title={Planck 2015 results-xiii. cosmological parameters},
+  author={Planck-Collaboration and Ade, Peter AR and Aghanim, Nabila and Arnaud, M and Ashdown, Mark and Aumont, Jea and Baccigalupi, Carlo and Banday, AJ and Barreiro, RB and Bartlett, JG and Bartolo, Nicola and others},
+  journal={Astronomy \& Astrophysics},
+  volume={594},
+  pages={A13},
+  year={2016},
+  publisher={EDP sciences}
+}
+
+@article{planck2020,
+  title={Planck 2018 results-VI. Cosmological parameters},
+  author={Planck-Collaboration and Aghanim, Nabila and Akrami, Yashar and Ashdown, Mark and Aumont, Jonathan and Baccigalupi, Carlo and Ballardini, Mario and Banday, Anthony J and Barreiro, RB and Bartolo, Nicola and Basak, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={641},
+  pages={A6},
+  year={2020},
+  publisher={EDP sciences}
+}
+
+@article{camarena2020,
+  title={Local determination of the Hubble constant and the deceleration parameter},
+  author={Camarena, David and Marra, Valerio},
+  journal={Physical Review Research},
+  volume={2},
+  number={1},
+  pages={013028},
+  year={2020},
+  publisher={APS}
+}
+
+@book{peebles2020,
+  title={Cosmology’s century: An inside history of our modern understanding of the universe},
+  author={Peebles, Phillip James Edwin},
+  year={2020},
+  publisher={Princeton University Press}
+}
+
+@article{lesser2015,
+  title={A summary of charge-coupled devices for astronomy},
+  author={Lesser, Michael},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={127},
+  number={957},
+  pages={1097--1104},
+  year={2015},
+  publisher={The Astronomical Society of the Pacific}
+}
+\end{filecontents}
+
+\begin{filecontents}{dark_energy_corrections.bbl}
+\begin{thebibliography}{17}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Verde}\ \emph {et~al.}(2019)\citenamefont {Verde},
+  \citenamefont {Treu},\ and\ \citenamefont {Riess}}]{verde2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Verde}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Treu}},\ and\
+  \bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont {Riess}},\ }\bibfield
+  {title} {\bibinfo {title} {Tensions between the early and late universe},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Astronomy}\
+  }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {891} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Weinberg}(2008)}]{weinberg2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Weinberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Cosmology}}}\
+  (\bibinfo  {publisher} {OUP Oxford},\ \bibinfo {year} {2008})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Riess}\ \emph {et~al.}(1998)\citenamefont {Riess},
+  \citenamefont {Filippenko}, \citenamefont {Challis}, \citenamefont
+  {Clocchiatti}, \citenamefont {Diercks}, \citenamefont {Garnavich},
+  \citenamefont {Gilliland}, \citenamefont {Hogan}, \citenamefont {Jha},
+  \citenamefont {Kirshner} \emph {et~al.}}]{riess1998}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
+  {Riess}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
+  {Filippenko}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Challis}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Clocchiatti}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Diercks}}, \bibinfo {author}
+  {\bibfnamefont {P.~M.}\ \bibnamefont {Garnavich}}, \bibinfo {author}
+  {\bibfnamefont {R.~L.}\ \bibnamefont {Gilliland}}, \bibinfo {author}
+  {\bibfnamefont {C.~J.}\ \bibnamefont {Hogan}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Jha}}, \bibinfo {author} {\bibfnamefont
+  {R.~P.}\ \bibnamefont {Kirshner}}, \emph {et~al.},\ }\bibfield  {title}
+  {\bibinfo {title} {Observational evidence from supernovae for an accelerating
+  universe and a cosmological constant},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {The astronomical journal}\ }\textbf {\bibinfo {volume}
+  {116}},\ \bibinfo {pages} {1009} (\bibinfo {year} {1998})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Tolman}(1930)}]{tolman1930}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+  {Tolman}},\ }\bibfield  {title} {\bibinfo {title} {On the estimation of
+  distances in a curved universe with a non-static line element},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+  Academy of Sciences}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages}
+  {511} (\bibinfo {year} {1930})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {de~Sitter}(1934)}]{desitter1934}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {de~Sitter}},\ }\bibfield  {title} {\bibinfo {title} {On distance, magnitude,
+  and related quantities in an expanding universe},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Bulletin of the Astronomical Institutes of
+  the Netherlands, Vol. 7, p. 205}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo
+  {pages} {205} (\bibinfo {year} {1934})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hubble}\ and\ \citenamefont
+  {Tolman}(1935)}]{hubble1935}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Hubble}}\ and\ \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+  {Tolman}},\ }\bibfield  {title} {\bibinfo {title} {Two methods of
+  investigating the nature of the nebular redshift},\ }\href@noop {} {\bibfield
+   {journal} {\bibinfo  {journal} {Astrophysical Journal, vol. 82, p. 302}\
+  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {302} (\bibinfo {year}
+  {1935})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Oke}\ and\ \citenamefont {Sandage}(1968)}]{oke1968}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont
+  {Oke}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sandage}},\
+  }\bibfield  {title} {\bibinfo {title} {Energy distributions, k corrections,
+  and the stebbins-whitford effect for giant elliptical galaxies},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Astrophysical Journal, vol.
+  154, p. 21}\ }\textbf {\bibinfo {volume} {154}},\ \bibinfo {pages} {21}
+  (\bibinfo {year} {1968})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kim}\ \emph {et~al.}(1996)\citenamefont {Kim},
+  \citenamefont {Goobar},\ and\ \citenamefont {Perlmutter}}]{kim1996}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Kim}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Goobar}},\ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Perlmutter}},\ }\bibfield
+   {title} {\bibinfo {title} {A generalized k correction for type ia
+  supernovae: comparing r-band photometry beyond z= 0.2 with b, v, and r-band
+  nearby photometry},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Publications of the Astronomical Society of the Pacific}\ }\textbf
+  {\bibinfo {volume} {108}},\ \bibinfo {pages} {190} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Planck-Collaboration}\ \emph
+  {et~al.}(2016)\citenamefont {Planck-Collaboration}, \citenamefont {Ade},
+  \citenamefont {Aghanim}, \citenamefont {Arnaud}, \citenamefont {Ashdown},
+  \citenamefont {Aumont}, \citenamefont {Baccigalupi}, \citenamefont {Banday},
+  \citenamefont {Barreiro}, \citenamefont {Bartlett}, \citenamefont {Bartolo}
+  \emph {et~al.}}]{planck2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {Planck-Collaboration}},
+  \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont {Ade}}, \bibinfo
+  {author} {\bibfnamefont {N.}~\bibnamefont {Aghanim}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Arnaud}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Ashdown}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Aumont}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Baccigalupi}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Banday}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Barreiro}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Bartlett}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Bartolo}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {Planck 2015 results-xiii. cosmological parameters},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Astronomy \& Astrophysics}\
+  }\textbf {\bibinfo {volume} {594}},\ \bibinfo {pages} {A13} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Perlmutter}\ \emph {et~al.}(1999)\citenamefont
+  {Perlmutter}, \citenamefont {Aldering}, \citenamefont {Goldhaber},
+  \citenamefont {Knop}, \citenamefont {Nugent}, \citenamefont {Castro},
+  \citenamefont {Deustua}, \citenamefont {Fabbro}, \citenamefont {Goobar},
+  \citenamefont {Groom} \emph {et~al.}}]{perlmutter1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Perlmutter}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Aldering}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Goldhaber}},
+  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Knop}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Nugent}}, \bibinfo {author}
+  {\bibfnamefont {P.~G.}\ \bibnamefont {Castro}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Deustua}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Fabbro}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Goobar}}, \bibinfo {author} {\bibfnamefont {D.~E.}\
+  \bibnamefont {Groom}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title}
+  {Measurements of $\omega$ and $\lambda$ from 42 high-redshift supernovae},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
+  Journal}\ }\textbf {\bibinfo {volume} {517}},\ \bibinfo {pages} {565}
+  (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {DES-Collaboration}\ \emph {et~al.}(2024)\citenamefont
+  {DES-Collaboration}, \citenamefont {Abbott}, \citenamefont {Acevedo},
+  \citenamefont {Aguena}, \citenamefont {Alarcon}, \citenamefont {Allam},
+  \citenamefont {Alves}, \citenamefont {Amon}, \citenamefont
+  {Andrade-Oliveira}, \citenamefont {Annis}, \citenamefont {Armstrong} \emph
+  {et~al.}}]{abbott2024}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {DES-Collaboration}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Abbott}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Acevedo}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Aguena}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Alarcon}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Allam}}, \bibinfo {author} {\bibfnamefont
+  {O.}~\bibnamefont {Alves}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Amon}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Andrade-Oliveira}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Annis}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Armstrong}},
+  \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The dark energy
+  survey: Cosmology results with $\sim$1500 new high-redshift type ia
+  supernovae using the full 5-year dataset},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2401.02929}\ } (\bibinfo
+  {year} {2024})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Flaugher}\ \emph {et~al.}(2015)\citenamefont
+  {Flaugher}, \citenamefont {Diehl}, \citenamefont {Honscheid}, \citenamefont
+  {Abbott}, \citenamefont {Alvarez}, \citenamefont {Angstadt}, \citenamefont
+  {Annis}, \citenamefont {Antonik}, \citenamefont {Ballester}, \citenamefont
+  {Beaufore} \emph {et~al.}}]{flaugher2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Flaugher}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Diehl}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Honscheid}}, \bibinfo
+  {author} {\bibfnamefont {T.}~\bibnamefont {Abbott}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Alvarez}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Angstadt}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Annis}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Antonik}}, \bibinfo {author} {\bibfnamefont
+  {O.}~\bibnamefont {Ballester}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Beaufore}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
+  {title} {The dark energy camera},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Astronomical Journal}\ }\textbf {\bibinfo {volume}
+  {150}},\ \bibinfo {pages} {150} (\bibinfo {year} {2015})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Lesser}(2015)}]{lesser2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Lesser}},\ }\bibfield  {title} {\bibinfo {title} {A summary of
+  charge-coupled devices for astronomy},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Publications of the Astronomical Society of the
+  Pacific}\ }\textbf {\bibinfo {volume} {127}},\ \bibinfo {pages} {1097}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Burns}\ \emph {et~al.}(2010)\citenamefont {Burns},
+  \citenamefont {Stritzinger}, \citenamefont {Phillips}, \citenamefont
+  {Kattner}, \citenamefont {Persson}, \citenamefont {Madore}, \citenamefont
+  {Freedman}, \citenamefont {Boldt}, \citenamefont {Campillay}, \citenamefont
+  {Contreras} \emph {et~al.}}]{burns2010}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
+  {Burns}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Stritzinger}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Phillips}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Kattner}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Persson}}, \bibinfo {author} {\bibfnamefont
+  {B.~F.}\ \bibnamefont {Madore}}, \bibinfo {author} {\bibfnamefont {W.~L.}\
+  \bibnamefont {Freedman}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Boldt}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Campillay}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Contreras}}, \emph
+  {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The carnegie supernova
+  project: light-curve fitting with snoopy},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {The Astronomical Journal}\ }\textbf {\bibinfo
+  {volume} {141}},\ \bibinfo {pages} {19} (\bibinfo {year} {2010})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Kessler}\ \emph {et~al.}(2009)\citenamefont
+  {Kessler}, \citenamefont {Bernstein}, \citenamefont {Cinabro}, \citenamefont
+  {Dilday}, \citenamefont {Frieman}, \citenamefont {Jha}, \citenamefont
+  {Kuhlmann}, \citenamefont {Miknaitis}, \citenamefont {Sako}, \citenamefont
+  {Taylor} \emph {et~al.}}]{kessler2009}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Kessler}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+  {Bernstein}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cinabro}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Dilday}}, \bibinfo
+  {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Frieman}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Jha}}, \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Kuhlmann}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Miknaitis}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Sako}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Taylor}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title} {Snana: A
+  public software package for supernova analysis},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Publications of the Astronomical Society of
+  the Pacific}\ }\textbf {\bibinfo {volume} {121}},\ \bibinfo {pages} {1028}
+  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vincenzi}\ \emph {et~al.}(2024)\citenamefont
+  {Vincenzi}, \citenamefont {Brout}, \citenamefont {Armstrong}, \citenamefont
+  {Popovic}, \citenamefont {Taylor}, \citenamefont {Acevedo}, \citenamefont
+  {Camilleri}, \citenamefont {Chen}, \citenamefont {Davis}, \citenamefont {Lee}
+  \emph {et~al.}}]{vincenzi2024}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Vincenzi}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Brout}},
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Armstrong}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Popovic}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Taylor}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Acevedo}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Camilleri}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Davis}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Lee}}, \emph
+  {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The dark energy survey
+  supernova program: Cosmological analysis and systematic uncertainties},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
+  Journal}\ }\textbf {\bibinfo {volume} {975}},\ \bibinfo {pages} {86}
+  (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Planck-Collaboration}\ \emph
+  {et~al.}(2020)\citenamefont {Planck-Collaboration}, \citenamefont {Aghanim},
+  \citenamefont {Akrami}, \citenamefont {Ashdown}, \citenamefont {Aumont},
+  \citenamefont {Baccigalupi}, \citenamefont {Ballardini}, \citenamefont
+  {Banday}, \citenamefont {Barreiro}, \citenamefont {Bartolo}, \citenamefont
+  {Basak} \emph {et~al.}}]{planck2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {Planck-Collaboration}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Aghanim}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Akrami}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Ashdown}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Aumont}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Baccigalupi}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Ballardini}}, \bibinfo {author} {\bibfnamefont {A.~J.}\
+  \bibnamefont {Banday}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Barreiro}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bartolo}},
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Basak}}, \emph {et~al.},\
+  }\bibfield  {title} {\bibinfo {title} {Planck 2018 results-vi. cosmological
+  parameters},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Astronomy \& Astrophysics}\ }\textbf {\bibinfo {volume} {641}},\ \bibinfo
+  {pages} {A6} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\end{thebibliography}%
+\end{filecontents}
+
 \documentclass[aps,prl,reprint,amsmath,floatfix]{revtex4-2}
@@
 
-\begin{filecontents}{references.bib}
-@article{riess1998,
-  title={Observational evidence from supernovae for an accelerating universe and a cosmological constant},
-  author={Riess, Adam G and Filippenko, Alexei V and Challis, Peter and Clocchiatti, Alejandro and Diercks, Alan and Garnavich, Peter M and Gilliland, Ron L and Hogan, Craig J and Jha, Saurabh and Kirshner, Robert P and others},
-  journal={The astronomical journal},
-  volume={116},
-  number={3},
-  pages={1009},
-  year={1998},
-  publisher={IOP Publishing}
-}
-
-@article{perlmutter1999,
-  title={Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift supernovae},
-  author={Perlmutter, Saul and Aldering, Goldhaber and Goldhaber, Gerson and Knop, Richard A and Nugent, Peter and Castro, Patricia G and Deustua, Susana and Fabbro, Sebastien and Goobar, Ariel and Groom, Donald E and others},
-  journal={The Astrophysical Journal},
-  volume={517},
-  number={2},
-  pages={565},
-  year={1999},
-  publisher={IOP Publishing}
-}
-
-@article{perlmutter2003,
-  title={Measuring cosmology with supernovae},
-  author={Perlmutter, Saul and Schmidt, Brian P},
-  journal={Supernovae and Gamma-Ray Bursters},
-  pages={195--217},
-  year={2003},
-  publisher={Springer}
-}
-
-@book{weinberg2008,
-  title={Cosmology},
-  author={Weinberg, Steven},
-  year={2008},
-  publisher={OUP Oxford}
-}
-
-@article{straumann2012,
-  title={The 2011 Nobel Prize in Physics},
-  author={Straumann, Norbert and Z{\"u}rich, Uni},
-  journal={SPG Mitteilungen},
-  number={36},
-  year={2012}
-}
-
-@article{betoule2014,
-  title={Improved cosmological constraints from a joint analysis of the SDSS-II and SNLS supernova samples},
-  author={Betoule, MEA and Kessler, R and Guy, J and Mosher, J and Hardin, D and Biswas, R and Astier, P and El-Hage, P and Konig, M and Kuhlmann, S and others},
-  journal={Astronomy \& Astrophysics},
-  volume={568},
-  pages={A22},
-  year={2014},
-  publisher={EDP Sciences}
-}
-
-@article{siegel1982,
-  title={Robust regression using repeated medians},
-  author={Siegel, Andrew F},
-  journal={Biometrika},
-  volume={69},
-  number={1},
-  pages={242--244},
-  year={1982},
-  publisher={Oxford University Press}
-}
-
-@article{verde2019,
-  title={Tensions between the early and late Universe},
-  author={Verde, Licia and Treu, Tommaso and Riess, Adam G},
-  journal={Nature Astronomy},
-  volume={3},
-  number={10},
-  pages={891--895},
-  year={2019},
-  publisher={Nature Publishing Group UK London}
-}
-
-@article{abbott2024,
-  title={The Dark Energy Survey: Cosmology Results With $\sim$1500 New High-redshift Type Ia Supernovae Using The Full 5-year Dataset},
-  author={DES-Collaboration and Abbott, TMC and Acevedo, M and Aguena, M and Alarcon, A and Allam, S and Alves, O and Amon, A and Andrade-Oliveira, F and Annis, J and Armstrong, P and others},
-  journal={arXiv preprint arXiv:2401.02929},
-  year={2024}
-}
-
-@article{perivolaropoulos2022,
-  title={Challenges for $\Lambda$CDM: An update},
-  author={Perivolaropoulos, Leandros and Skara, Foteini},
-  journal={New Astronomy Reviews},
-  volume={95},
-  pages={101659},
-  year={2022},
-  publisher={Elsevier}
-}
-
-@article{flaugher2015,
-  title={The dark energy camera},
-  author={Flaugher, Brenna and Diehl, HT and Honscheid, K and Abbott, TMC and Alvarez, O and Angstadt, R and Annis, JT and Antonik, M and Ballester, O and Beaufore, L and others},
-  journal={The Astronomical Journal},
-  volume={150},
-  number={5},
-  pages={150},
-  year={2015},
-  publisher={IOP Publishing}
-}
-
-@article{vincenzi2024,
-  title={The Dark Energy Survey Supernova Program: Cosmological Analysis and Systematic Uncertainties},
-  author={Vincenzi, M and Brout, D and Armstrong, P and Popovic, B and Taylor, G and Acevedo, M and Camilleri, R and Chen, R and Davis, TM and Lee, J and others},
-  journal={The Astrophysical Journal},
-  volume={975},
-  number={1},
-  pages={86},
-  year={2024},
-  publisher={IOP Publishing}
-}
-
-@article{shao2013,
-  title={The energy loss of photons and cosmological redshift},
-  author={Shao, Ming-Hui},
-  journal={Physics Essays},
-  volume={26},
-  number={2},
-  pages={183--190},
-  year={2013},
-  publisher={Physics Essays Publication}
-}
-
-@article{white2024,
-  title={The Dark Energy Survey Supernova Program: Slow supernovae show cosmological time dilation out to $ z \sim 1$},
-  author={White, Ryan MT and Davis, Tamara M and Lewis, Geraint F and Lidman, Christopher and Shah, Paul and Abbott, TMC and Aguena, M and Allam, S and Andrade-Oliveira, F and Asorey, J and others},
-  journal={arXiv preprint arXiv:2406.05050},
-  year={2024}
-}
-
-@article{blondin2008,
-  title={Time dilation in type Ia supernova spectra at high redshift},
-  author={Blondin, Stephanie and Davis, Tamara M and Krisciunas, Kevin and Schmidt, Brian P and Sollerman, J and Wood-Vasey, WM and Becker, AC and Challis, P and Clocchiatti, A and Damke, G and others},
-  journal={The Astrophysical Journal},
-  volume={682},
-  number={2},
-  pages={724},
-  year={2008},
-  publisher={IOP Publishing}
-}
-
-@article{zwicky1929,
-  title={On the redshift of spectral lines through interstellar space},
-  author={Zwicky, Fritz},
-  journal={Proceedings of the National Academy of Sciences},
-  volume={15},
-  number={10},
-  pages={773--779},
-  year={1929},
-  publisher={National Acad Sciences}
-}
-
-@article{tolman1930,
-  title={On the estimation of distances in a curved universe with a non-static line element},
-  author={Tolman, Richard C},
-  journal={Proceedings of the National Academy of Sciences},
-  volume={16},
-  number={7},
-  pages={511--520},
-  year={1930},
-  publisher={National Acad Sciences}
-}
-
-@article{desitter1934,
-  title={On distance, magnitude, and related quantities in an expanding universe},
-  author={de Sitter, Willem},
-  journal={Bulletin of the Astronomical Institutes of the Netherlands, Vol. 7, p. 205},
-  volume={7},
-  pages={205},
-  year={1934}
-}
-
-@article{hubble1935,
-  title={Two methods of investigating the nature of the nebular redshift},
-  author={Hubble, Edwin and Tolman, Richard C},
-  journal={Astrophysical Journal, vol. 82, p. 302},
-  volume={82},
-  pages={302},
-  year={1935}
-}
-
-@article{oke1968,
-  title={Energy distributions, k corrections, and the Stebbins-Whitford effect for giant elliptical galaxies},
-  author={Oke, John Beverley and Sandage, Allan},
-  journal={Astrophysical Journal, vol. 154, p. 21},
-  volume={154},
-  pages={21},
-  year={1968}
-}
-
-@article{kim1996,
-  title={A generalized K correction for type Ia supernovae: comparing R-band photometry beyond z= 0.2 with B, V, and R-band nearby photometry},
-  author={Kim, Alex and Goobar, Ariel and Perlmutter, Saul},
-  journal={Publications of the Astronomical Society of the Pacific},
-  volume={108},
-  number={720},
-  pages={190},
-  year={1996},
-  publisher={IOP Publishing}
-}
-
-@article{hsiao2007,
-  title={K-corrections and spectral templates of Type Ia supernovae},
-  author={Hsiao, Eric Y and Conley, A and Howell, DA and Sullivan, M and Pritchet, CJ and Carlberg, RG and Nugent, PE and Phillips, MM},
-  journal={The Astrophysical Journal},
-  volume={663},
-  number={2},
-  pages={1187},
-  year={2007},
-  publisher={IOP Publishing}
-}
-
-@article{kessler2009,
-  title={SNANA: A public software package for supernova analysis},
-  author={Kessler, Richard and Bernstein, Joseph P and Cinabro, David and Dilday, Benjamin and Frieman, Joshua A and Jha, Saurabh and Kuhlmann, Stephen and Miknaitis, Gajus and Sako, Masao and Taylor, Matt and others},
-  journal={Publications of the Astronomical Society of the Pacific},
-  volume={121},
-  number={883},
-  pages={1028},
-  year={2009},
-  publisher={IOP Publishing}
-}
-
-@article{burns2010,
-  title={The Carnegie supernova project: light-curve fitting with SNooPy},
-  author={Burns, Christopher R and Stritzinger, Maximilian and Phillips, MM and Kattner, ShiAnne and Persson, SE and Madore, Barry F and Freedman, Wendy L and Boldt, Luis and Campillay, Abdo and Contreras, Carlos and others},
-  journal={The Astronomical Journal},
-  volume={141},
-  number={1},
-  pages={19},
-  year={2010},
-  publisher={IOP Publishing}
-}
-
-@article{planck2015,
-  title={Planck 2015 results-xiii. cosmological parameters},
-  author={Planck-Collaboration and Ade, Peter AR and Aghanim, Nabila and Arnaud, M and Ashdown, Mark and Aumont, Jea and Baccigalupi, Carlo and Banday, AJ and Barreiro, RB and Bartlett, JG and Bartolo, Nicola and others},
-  journal={Astronomy \& Astrophysics},
-  volume={594},
-  pages={A13},
-  year={2016},
-  publisher={EDP sciences}
-}
-
-@article{planck2020,
-  title={Planck 2018 results-VI. Cosmological parameters},
-  author={Planck-Collaboration and Aghanim, Nabila and Akrami, Yashar and Ashdown, Mark and Aumont, Jonathan and Baccigalupi, Carlo and Ballardini, Mario and Banday, Anthony J and Barreiro, RB and Bartolo, Nicola and Basak, S and others},
-  journal={Astronomy \& Astrophysics},
-  volume={641},
-  pages={A6},
-  year={2020},
-  publisher={EDP sciences}
-}
-
-@article{camarena2020,
-  title={Local determination of the Hubble constant and the deceleration parameter},
-  author={Camarena, David and Marra, Valerio},
-  journal={Physical Review Research},
-  volume={2},
-  number={1},
-  pages={013028},
-  year={2020},
-  publisher={APS}
-}
-
-@book{peebles2020,
-  title={Cosmology’s century: An inside history of our modern understanding of the universe},
-  author={Peebles, Phillip James Edwin},
-  year={2020},
-  publisher={Princeton University Press}
-}
-
-@article{lesser2015,
-  title={A summary of charge-coupled devices for astronomy},
-  author={Lesser, Michael},
-  journal={Publications of the Astronomical Society of the Pacific},
-  volume={127},
-  number={957},
-  pages={1097--1104},
-  year={2015},
-  publisher={The Astronomical Society of the Pacific}
-}
-\end{filecontents}
 \bibliography{references}

### 2025-02-07 paper/dark_energy_corrections.tex

--- 2025-02-04 paper/dark_energy_corrections.tex
@@
+\begin{filecontents}{references.bib}
+@article{riess1998,
+  title={Observational evidence from supernovae for an accelerating universe and a cosmological constant},
+  author={Riess, Adam G and Filippenko, Alexei V and Challis, Peter and Clocchiatti, Alejandro and Diercks, Alan and Garnavich, Peter M and Gilliland, Ron L and Hogan, Craig J and Jha, Saurabh and Kirshner, Robert P and others},
+  journal={The astronomical journal},
+  volume={116},
+  number={3},
+  pages={1009},
+  year={1998},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter1999,
+  title={Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift supernovae},
+  author={Perlmutter, Saul and Aldering, Goldhaber and Goldhaber, Gerson and Knop, Richard A and Nugent, Peter and Castro, Patricia G and Deustua, Susana and Fabbro, Sebastien and Goobar, Ariel and Groom, Donald E and others},
+  journal={The Astrophysical Journal},
+  volume={517},
+  number={2},
+  pages={565},
+  year={1999},
+  publisher={IOP Publishing}
+}
+
+@article{perlmutter2003,
+  title={Measuring cosmology with supernovae},
+  author={Perlmutter, Saul and Schmidt, Brian P},
+  journal={Supernovae and Gamma-Ray Bursters},
+  pages={195--217},
+  year={2003},
+  publisher={Springer}
+}
+
+@book{weinberg2008,
+  title={Cosmology},
+  author={Weinberg, Steven},
+  year={2008},
+  publisher={OUP Oxford}
+}
+
+@article{straumann2012,
+  title={The 2011 Nobel Prize in Physics},
+  author={Straumann, Norbert and Z{\"u}rich, Uni},
+  journal={SPG Mitteilungen},
+  number={36},
+  year={2012}
+}
+
+@article{betoule2014,
+  title={Improved cosmological constraints from a joint analysis of the SDSS-II and SNLS supernova samples},
+  author={Betoule, MEA and Kessler, R and Guy, J and Mosher, J and Hardin, D and Biswas, R and Astier, P and El-Hage, P and Konig, M and Kuhlmann, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={568},
+  pages={A22},
+  year={2014},
+  publisher={EDP Sciences}
+}
+
+@article{siegel1982,
+  title={Robust regression using repeated medians},
+  author={Siegel, Andrew F},
+  journal={Biometrika},
+  volume={69},
+  number={1},
+  pages={242--244},
+  year={1982},
+  publisher={Oxford University Press}
+}
+
+@article{verde2019,
+  title={Tensions between the early and late Universe},
+  author={Verde, Licia and Treu, Tommaso and Riess, Adam G},
+  journal={Nature Astronomy},
+  volume={3},
+  number={10},
+  pages={891--895},
+  year={2019},
+  publisher={Nature Publishing Group UK London}
+}
+
+@article{abbott2024,
+  title={The Dark Energy Survey: Cosmology Results With $\sim$1500 New High-redshift Type Ia Supernovae Using The Full 5-year Dataset},
+  author={DES-Collaboration and Abbott, TMC and Acevedo, M and Aguena, M and Alarcon, A and Allam, S and Alves, O and Amon, A and Andrade-Oliveira, F and Annis, J and Armstrong, P and others},
+  journal={arXiv preprint arXiv:2401.02929},
+  year={2024}
+}
+
+@article{perivolaropoulos2022,
+  title={Challenges for $\Lambda$CDM: An update},
+  author={Perivolaropoulos, Leandros and Skara, Foteini},
+  journal={New Astronomy Reviews},
+  volume={95},
+  pages={101659},
+  year={2022},
+  publisher={Elsevier}
+}
+
+@article{flaugher2015,
+  title={The dark energy camera},
+  author={Flaugher, Brenna and Diehl, HT and Honscheid, K and Abbott, TMC and Alvarez, O and Angstadt, R and Annis, JT and Antonik, M and Ballester, O and Beaufore, L and others},
+  journal={The Astronomical Journal},
+  volume={150},
+  number={5},
+  pages={150},
+  year={2015},
+  publisher={IOP Publishing}
+}
+
+@article{vincenzi2024,
+  title={The Dark Energy Survey Supernova Program: Cosmological Analysis and Systematic Uncertainties},
+  author={Vincenzi, M and Brout, D and Armstrong, P and Popovic, B and Taylor, G and Acevedo, M and Camilleri, R and Chen, R and Davis, TM and Lee, J and others},
+  journal={The Astrophysical Journal},
+  volume={975},
+  number={1},
+  pages={86},
+  year={2024},
+  publisher={IOP Publishing}
+}
+
+@article{shao2013,
+  title={The energy loss of photons and cosmological redshift},
+  author={Shao, Ming-Hui},
+  journal={Physics Essays},
+  volume={26},
+  number={2},
+  pages={183--190},
+  year={2013},
+  publisher={Physics Essays Publication}
+}
+
+@article{white2024,
+  title={The Dark Energy Survey Supernova Program: Slow supernovae show cosmological time dilation out to $ z \sim 1$},
+  author={White, Ryan MT and Davis, Tamara M and Lewis, Geraint F and Lidman, Christopher and Shah, Paul and Abbott, TMC and Aguena, M and Allam, S and Andrade-Oliveira, F and Asorey, J and others},
+  journal={arXiv preprint arXiv:2406.05050},
+  year={2024}
+}
+
+@article{blondin2008,
+  title={Time dilation in type Ia supernova spectra at high redshift},
+  author={Blondin, Stephanie and Davis, Tamara M and Krisciunas, Kevin and Schmidt, Brian P and Sollerman, J and Wood-Vasey, WM and Becker, AC and Challis, P and Clocchiatti, A and Damke, G and others},
+  journal={The Astrophysical Journal},
+  volume={682},
+  number={2},
+  pages={724},
+  year={2008},
+  publisher={IOP Publishing}
+}
+
+@article{zwicky1929,
+  title={On the redshift of spectral lines through interstellar space},
+  author={Zwicky, Fritz},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={15},
+  number={10},
+  pages={773--779},
+  year={1929},
+  publisher={National Acad Sciences}
+}
+
+@article{tolman1930,
+  title={On the estimation of distances in a curved universe with a non-static line element},
+  author={Tolman, Richard C},
+  journal={Proceedings of the National Academy of Sciences},
+  volume={16},
+  number={7},
+  pages={511--520},
+  year={1930},
+  publisher={National Acad Sciences}
+}
+
+@article{desitter1934,
+  title={On distance, magnitude, and related quantities in an expanding universe},
+  author={de Sitter, Willem},
+  journal={Bulletin of the Astronomical Institutes of the Netherlands, Vol. 7, p. 205},
+  volume={7},
+  pages={205},
+  year={1934}
+}
+
+@article{hubble1935,
+  title={Two methods of investigating the nature of the nebular redshift},
+  author={Hubble, Edwin and Tolman, Richard C},
+  journal={Astrophysical Journal, vol. 82, p. 302},
+  volume={82},
+  pages={302},
+  year={1935}
+}
+
+@article{oke1968,
+  title={Energy distributions, k corrections, and the Stebbins-Whitford effect for giant elliptical galaxies},
+  author={Oke, John Beverley and Sandage, Allan},
+  journal={Astrophysical Journal, vol. 154, p. 21},
+  volume={154},
+  pages={21},
+  year={1968}
+}
+
+@article{kim1996,
+  title={A generalized K correction for type Ia supernovae: comparing R-band photometry beyond z= 0.2 with B, V, and R-band nearby photometry},
+  author={Kim, Alex and Goobar, Ariel and Perlmutter, Saul},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={108},
+  number={720},
+  pages={190},
+  year={1996},
+  publisher={IOP Publishing}
+}
+
+@article{hsiao2007,
+  title={K-corrections and spectral templates of Type Ia supernovae},
+  author={Hsiao, Eric Y and Conley, A and Howell, DA and Sullivan, M and Pritchet, CJ and Carlberg, RG and Nugent, PE and Phillips, MM},
+  journal={The Astrophysical Journal},
+  volume={663},
+  number={2},
+  pages={1187},
+  year={2007},
+  publisher={IOP Publishing}
+}
+
+@article{kessler2009,
+  title={SNANA: A public software package for supernova analysis},
+  author={Kessler, Richard and Bernstein, Joseph P and Cinabro, David and Dilday, Benjamin and Frieman, Joshua A and Jha, Saurabh and Kuhlmann, Stephen and Miknaitis, Gajus and Sako, Masao and Taylor, Matt and others},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={121},
+  number={883},
+  pages={1028},
+  year={2009},
+  publisher={IOP Publishing}
+}
+
+@article{burns2010,
+  title={The Carnegie supernova project: light-curve fitting with SNooPy},
+  author={Burns, Christopher R and Stritzinger, Maximilian and Phillips, MM and Kattner, ShiAnne and Persson, SE and Madore, Barry F and Freedman, Wendy L and Boldt, Luis and Campillay, Abdo and Contreras, Carlos and others},
+  journal={The Astronomical Journal},
+  volume={141},
+  number={1},
+  pages={19},
+  year={2010},
+  publisher={IOP Publishing}
+}
+
+@article{planck2015,
+  title={Planck 2015 results-xiii. cosmological parameters},
+  author={Planck-Collaboration and Ade, Peter AR and Aghanim, Nabila and Arnaud, M and Ashdown, Mark and Aumont, Jea and Baccigalupi, Carlo and Banday, AJ and Barreiro, RB and Bartlett, JG and Bartolo, Nicola and others},
+  journal={Astronomy \& Astrophysics},
+  volume={594},
+  pages={A13},
+  year={2016},
+  publisher={EDP sciences}
+}
+
+@article{planck2020,
+  title={Planck 2018 results-VI. Cosmological parameters},
+  author={Planck-Collaboration and Aghanim, Nabila and Akrami, Yashar and Ashdown, Mark and Aumont, Jonathan and Baccigalupi, Carlo and Ballardini, Mario and Banday, Anthony J and Barreiro, RB and Bartolo, Nicola and Basak, S and others},
+  journal={Astronomy \& Astrophysics},
+  volume={641},
+  pages={A6},
+  year={2020},
+  publisher={EDP sciences}
+}
+
+@article{camarena2020,
+  title={Local determination of the Hubble constant and the deceleration parameter},
+  author={Camarena, David and Marra, Valerio},
+  journal={Physical Review Research},
+  volume={2},
+  number={1},
+  pages={013028},
+  year={2020},
+  publisher={APS}
+}
+
+@book{peebles2020,
+  title={Cosmology’s century: An inside history of our modern understanding of the universe},
+  author={Peebles, Phillip James Edwin},
+  year={2020},
+  publisher={Princeton University Press}
+}
+
+@article{lesser2015,
+  title={A summary of charge-coupled devices for astronomy},
+  author={Lesser, Michael},
+  journal={Publications of the Astronomical Society of the Pacific},
+  volume={127},
+  number={957},
+  pages={1097--1104},
+  year={2015},
+  publisher={The Astronomical Society of the Pacific}
+}
+\end{filecontents}
+
 \documentclass[aps,prl,reprint,amsmath,floatfix]{revtex4-2}
@@
 
-In order to use SNe Ia to estimate the expansion rate of the universe, we need to
-identify both the redshift $z$ and the light travel distance $d$. In order to
-compute the light travel distance $d$, we use the definition of the distance
-modulus \citep{weinberg2008}:
+In order to use SNe Ia to estimate the expansion rate of the universe, we need
+to identify both the redshift $z$ and the light travel distance $d_{LT}$. In
+order to compute the light travel distance $d_{LT}$ in parsecs (pc), we use the
+definition of the distance modulus \citep{weinberg2008}:
 
@@
 \label{eq:mu_def}
-  d = 10^{1 + (m - M)/5} \text{pc}.
+  d_{LT} = 10^{1 + (m - M)/5} \text{pc}.
 \end{equation}
@@
 substitution $\mu = m - M$ and call $\mu$ the distance modulus.
+
+Cosmology uses multiple distance measurements, but for measuring the expansion
+rate of the universe, the only one we care about is the light travel distance
+$d_{LT}$. A similar distance measurement, the luminosity distance $d_L$, is
+often discussed in conjunction of flux measurements, but $d_L$ represents an
+illusory distance. In fact, ${d_{L} = d_{LT} \times (1 + z)}$, which can be
+thought of as the distance an object would need to be to produce the same
+amount of measured energy flux if redshift did not exist. The light travel
+distance $d_{LT}$ represents a physical quantity while $d_{L}$ does not.
 
@@
 modulus defined in Equation \ref{eq:mu_def} allows us to compute the light
-travel distance $d$.
+travel distance $d_{LT}$.
 
@@
   \includegraphics[width=\columnwidth]{distance_vs_redshift.pdf}
-  \caption{The relationship between light travel distance and redshift for two
-  treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
-  the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
-  treatment, which fixes the K-correction redshift error, appears to be linear.
-  The displayed points are roughly a third of the values in the full SNe Ia
-  dataset published in \citet{abbott2024}, selected with uniform redshift
-  spacing to aid visibility. }
+  \caption {The relationship between light travel distance $d_{LT}$ and
+  redshift $z$ for two treatments of the magnitude data. The red ${k(z) = 1}$
+  treatment, which represents the uncorrected values, is clearly non-linear
+  while the blue ${k(z) = 1 + z}$ treatment, which fixes the K-correction
+  redshift error, appears to be linear.  The displayed points are roughly a
+  third of the values in the full SNe Ia dataset published in
+  \citet{abbott2024}, selected with uniform redshift spacing to aid visibility.
+  }
   \label{fig:distance_vs_redshift}

### 2025-02-08 paper/dark_energy_corrections.tex

@@
 We rederive the K-correction equation and discover that the version commonly
-used to calculate magnitudes contains multiple errors. The oldest of these
-errors traces back to 1930 and two new errors were introduced in 1996. We
-conclude that correcting apparent magnitudes for time dilation resolves two of
-the preeminent mysteries in cosmology: first, dark energy is not supported by
-observations of Type Ia supernovae and second, the Hubble tension is due to the
-errors in the K-correction equation.
+used to calculate magnitudes fails to account for time dilation. This error
+traces back to 1930. We conclude that correcting apparent magnitudes for time
+dilation resolves two of the preeminent mysteries in cosmology: first, dark
+energy is not supported by observations of Type Ia supernovae and second, the
+Hubble tension is due to the error in the K-correction equation.
 \end{abstract}
@@
 \citet{oke1968} to handle additional cross-filter comparisons and added a term
-that was intended to address zero-point corrections.
+that addresses zero-point corrections.
 
@@
 K-correction equation that is used by modern astrophysics, but we will show
-that it contains three errors, one of which is innocuous, one of which
-introduces measurement bias, and one that produces the dark energy phenomenon.
+that this equation still contains the time dilation error that produces the
+dark energy phenomenon.
 
@@
 \begin{aligned}
+\label{eq:eflux2pflux}
    F(\lambda) &= F'(\lambda) \times \frac{hc}{\lambda} \\
@@
       \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
-           {\int \lambda F\left(\frac{\lambda}{1+z}\right)S_y(\lambda))d\lambda}\right) \quad \text{(incorrect)}.
+           {\int \lambda F\left(\frac{\lambda}{1+z}\right)S_y(\lambda)d\lambda}\right) \quad \text{(incorrect)}.
 \end{aligned}
@@
 
-In order to fully compare Equation \ref{eq:K2k} against Equation \ref{eq:kim} we need to use the identity
+In order to fully compare Equation \ref{eq:K2k} against Equation \ref{eq:kim},
+we need to convert the zero-point value $P_x$ into an expression that describes
+the accumulation of flux $\mathcal{F}_x$. We start with
+Equation \ref{eq:flux2mag}, set ${m_x = 0}$, and solve for the zero-point value
+$P_x$:
 
 \begin{equation}
-  P = -2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S(\lambda) d\lambda \right)
+\begin{aligned}
+  m_x &= -2.5 \text{log}(\mathcal{F}_x) + P_x \\
+    0 &= -2.5 \text{log}(\mathcal{F}_x) + P_x \\
+  P_x &= 2.5 \text{log}(\mathcal{F}_x).
+\end{aligned}
 \end{equation}
 
-\noindent where, according to \citet{kim1996}, ``$\mathcal{Z}(\lambda)$ is an
-idealized spectral energy distribution at $z = 0$ for which
-$U = B = V = R = I = 0$ in the photometric system being used.'' Combining this
-with Equation \ref{eq:K2k}, we have
+\noindent Next, we convert the measured flux $\mathcal{F}_x$ to energy flux
+$F_x$ using Equation \ref{eq:flux_definition} before renaming
+$F(\lambda) = \mathcal{Z}(\lambda)$ to indicate that we are measuring the
+idealized zero-point flux.
+
+\begin{equation}
+\begin{aligned}
+  P_x &= 2.5 \text{log}(\mathcal{F}_x(\lambda)) \\
+      &= 2.5 \text{log}\left( \int \lambda F(\lambda) S_x(\lambda) d\lambda \right) \\
+      &= 2.5 \text{log}\left( \int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right).
+\end{aligned}
+\end{equation}
+
+\noindent Combining this with Equation \ref{eq:K2k}, we have
 
@@
                    {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
-         &\quad + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right) \\
-         &\quad - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
-         &= 2.5 \text{log} \left(
+          &\quad - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right) \\
+          &\quad + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
+         &= -2.5 \text{log} \left(
               \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
@@
 
-Three differences with Equation \ref{eq:kim} stand out:
+Two differences with Equation \ref{eq:kim} stand out:
 
 \begin{itemize}
-  \item The sign is different for the first term. This will have a subtle but
-  frustrating effect for real measurements. The zero-point values for the two
-  filters are usually, but not always, roughly equal. As we observe more
-  distant supernovae, it is useful to switch our observational filter to a
-  filter that is sensitive to longer wavelengths, but each observation filter will
-  have its own small bias.
-
   \item The second term is multiplied by $2.5$ in \citet{kim1996}, but is
@@
 
-The value estimated here, $H_0 = 65.94 \pm 1.3$, is highly suspicious
-because of the flipped zero-point corrections, but it is consistent with
+The value estimated here, $H_0 = 65.94 \pm 1.3$, is consistent with
 estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
